---
title: 'Meta-analysis: transgenerational effects of a HFD in rodents'
author: 'Hamza Anwer  '
date: "15 July 2019"
output:
  html_document:
    df_print: paged
---

## Body Weight Data Extractions - lnRR

```{r, include=FALSE, mesage = FALSE, warning = FALSE}

library(tidyverse)
library(openxlsx)  
library(knitr)
library(metafor)
library(ggplot2)
library(readxl)
library(janitor)
```

```{r} 
#Importing Data
ALL_TRAITS <- read_excel("../data/ALL_TRAITS.xlsx")
str(ALL_TRAITS)

#convert categorical variables into factors
ALL_TRAITS$Trait <- factor(ALL_TRAITS$Trait)
ALL_TRAITS$Exposure_Type <- factor(ALL_TRAITS$Exposure_Type)
ALL_TRAITS$Sex <- factor(ALL_TRAITS$Sex)
ALL_TRAITS$Generation <- factor(ALL_TRAITS$Generation)
ALL_TRAITS$Cohort_ID <- factor(ALL_TRAITS$Cohort_ID)
ALL_TRAITS$Paper_ID <- factor(ALL_TRAITS$Paper_ID)
ALL_TRAITS$Rodent_type <- factor(ALL_TRAITS$Rodent_type)
ALL_TRAITS$F2_Diet_at_measurement <- factor(ALL_TRAITS$F2_Diet_at_measurement)
ALL_TRAITS$Strain <- factor(ALL_TRAITS$Strain)
ALL_TRAITS$F0_Parent_Exposed <- factor(ALL_TRAITS$F0_Parent_Exposed)

```
```{r}
#Data checks

#Initial results section ! Showing how many effect sizes we had and the distribution of these effect sizes ! 

#Checking continuous variables
hist(ALL_TRAITS$Age_Days)
hist(ALL_TRAITS$Sample_Size_n_Control)
hist(ALL_TRAITS$Sample_Size_n_Treatment)

#checking categorical variables
tabyl(ALL_TRAITS, Trait)
tabyl(ALL_TRAITS, Exposure_Type) 
tabyl(ALL_TRAITS, Sex) 
tabyl(ALL_TRAITS, Generation) 
tabyl(ALL_TRAITS, Cohort_ID) 
tabyl(ALL_TRAITS, Paper_ID) 
tabyl(ALL_TRAITS, Rodent_type) 
tabyl(ALL_TRAITS, F2_Diet_at_measurement) 
tabyl(ALL_TRAITS, Strain) 
tabyl(ALL_TRAITS, F0_Parent_Exposed) 

#two-way tables
tabyl(ALL_TRAITS, Trait, Exposure_Type)
tabyl(ALL_TRAITS, Exposure_Type, Sex)


#three-way tables
tabyl(ALL_TRAITS, Paper_ID, Trait, Exposure_Type)
tabyl(ALL_TRAITS, Sex, Exposure_Type, Trait)
#Will have to skip some of the models because we can't exactly compare males and females for certain traits ! There just isn't enough data or balance !


#Will always need to look at whether we need to exclude data or not, for example, when using sex as a moderator, there isn't much balance and so we can exclude "Both" from the analysis.


```





## **1. What random effect structure to use ?**

Choose random effect structure by conducting LRTs (likelihood ratio tests), and for that we need ML (maximum likelihood) estimates

Possible random effects: paper ID, cohort_ID, strain, lineage, shared control. I'm adding random effects to models and then running anovas to see if the AIC is low (important) or high (not important) when compared to the model with NO random effects. After finding the lowest values, I'll put them together for the best model.

```{r}
meta1null <- rma.mv(yi, vi, data=Effect_Size, method = 'ML') 
metastudy <- rma.mv(yi, vi,random = ~1|Cohort_ID, data=Effect_Size, method = 'ML') 
anova(meta1null, metastudy)
meta0study <- rma.mv(yi, vi,random = ~1|Paper_ID, data=Effect_Size, method = 'ML') 
anova(meta1null, meta0study)
meta1study <- rma.mv(yi, vi,random = ~1|Rodent_type, data=Effect_Size, method = 'ML') 
anova(meta1null, meta1study)
meta4study <- rma.mv(yi, vi,random = ~1|Strain, data=Effect_Size, method = 'ML') 
anova(meta1null, meta4study)

metastudy_best <- rma.mv(yi, vi,random = list(~1|Paper_ID,~1|Cohort_ID), data=Effect_Size, method = 'ML') 
anova(meta0study, metastudy_best)
summary(metastudy_best)
forest(metastudy_best)
metastudy_best2 <- rma.mv(yi, vi,random = list(~1|Paper_ID,~1|Cohort_ID,~1|Rodent_type,~1|Strain), data=Effect_Size, method = 'ML') 
anova(metastudy_best, metastudy_best2)
```

Results:
I had a look at different random effects and compiled a model that I think is best. Paper ID, Cohort ID yielded the lowest AIC values when looked at independently, with rodent type, and strain producing very high values. As such, I will only incorporate Paper_ID and Cohort_ID as my random effects. 

Need to add comments for each model !

```{r}
ES_ID <- factor(1:dim(Effect_Size)[1])
Effect_Size$ES_ID <-ES_ID
model0 <- rma.mv(yi, vi,random = list(~1|Paper_ID,~1|Cohort_ID, ~1|ES_ID), data=Effect_Size)
summary(model0)

model1 <- rma.mv(yi, vi, mod = ~ Exposure_Type-1, random = list(~1|Paper_ID,~1|Strain, ~1|ES_ID), data=Effect_Size)
summary(model1)


model2 <- rma.mv(yi, vi, random = list(~1|Paper_ID, ~1|Cohort_ID, ~1|ES_ID), data=Effect_Size[Effect_Size$Exposure_Type == "One off",])
summary(model2)

model3 <- rma(yi, vi, data=Effect_Size[Effect_Size$Exposure_Type == "One off",])
summary(model3)
funnel(model3)

model4 <- rma.mv(yi, vi, mod = ~scale(Age_Days), random = list(~1|Paper_ID, ~1|Cohort_ID, ~1|ES_ID), data=Effect_Size[Effect_Size$Exposure_Type == "One off",])
summary(model4)


model5 <- rma.mv(yi, vi, mod = Age_Days, random = list(~1|Paper_ID, ~1|Cohort_ID, ~1|ES_ID), data=Effect_Size[Effect_Size$Exposure_Type != "One off",])
summary(model5)

prediction <- predict(model5, newmods = 100)
prediction
```
# Summarize models and choose which to present in main report !

# **2. Calculating the effects size (log response ratio)**
```{r}
#Body Weight
#ADD HISTOGRAMS!!!NEED TO CHECK IF THERE ARE ANY UNUSUAL EFFECT SIZES
#ADD CONSISTENT DATA FRAME NAMES
# ASSIGN TO SAME DATA FRAME INSTEAD OF CREATING NEW DATAFRAMES, THEN RENMAE YI AND VI FOR LNR AND YI AND VI FOR LNCVR
# STEP 2 IS CALCUALTING EFFECT SIZES AND STEP 3 IS THE DATA SUMMARY, AND THEN AFTER THAT RUN META-ANALYTIC MODELS !!!! FIRST MODEL ANSWERS FIRST QUESTIONS, AND THEN PROGRESS WITH ANSWERING YOUR OTHER QUESTIONS ! 
# Viualize and decide what is next
# Also do the multigenerational data
# rename models: eg. OF_lnRR_BW_MA
# Create vectors, then use dataframe("name" = *vector*)

#Body Weight One Off
lnRR_BW_MA_ES <- escalc(measure="ROM", m1i=Mean_Treatment, sd1i=SD_Treatment, n1i=Sample_Size_n_Treatment, m2i=Mean_Control, sd2i=SD_Control, n2i=Sample_Size_n_Control, data=Body_Weight)

OF_lnRR_BW_MA <- rma.mv(yi, vi,random = list(~1|Paper_ID,~1|Cohort_ID), data=lnRR_BW_MA_ES[lnRR_BW_MA_ES$Exposure_Type == "One off",], method = 'REML') 
summary(OF_lnRR_BW_MA)
forest(OF_lnRR_BW_MA)

#Body Weight MG
MG_lnRR_BW_MA <- rma.mv(yi, vi,random = list(~1|Paper_ID,~1|Cohort_ID), data=lnRR_BW_MA_ES[lnRR_BW_MA_ES$Exposure_Type == "Multigenerational",], method = 'REML') 
summary(MG_lnRR_BW_MA)
forest(MG_lnRR_BW_MA)

#Glucose one off (change data sheet for amalgamated vs not amalgamated)

Effect_Size_Glucose <- escalc(measure="ROM", m1i=Mean_Treatment, sd1i=SD_Treatment, n1i=Sample_Size_n_Treatment, m2i=Mean_Control_Orig, sd2i=SD_Control_Orig, n2i=Sample_Size_n_Control, data=Glucose_Amalgamated) 
hist(Effect_Size_Glucose$yi)

OF_lnRR_Glucose_MA <- rma.mv(yi, vi,random = list(~1|Paper_ID,~1|Cohort_ID), data=Effect_Size_Glucose[Effect_Size_Glucose$Exposure_Type == "One off",], method = 'REML') 
summary(OF_lnRR_Glucose_MA)

#Glucose MG
MG_lnRR_Glucose_MA <- rma.mv(yi, vi,random = list(~1|Paper_ID,~1|Cohort_ID), data=Effect_Size_Glucose[Effect_Size_Glucose$Exposure_Type == "Multigenerational",], method = 'REML') 
summary(MG_lnRR_Glucose_MA)

#Insulin one off
Effect_Size_Insulin <- escalc(measure="ROM", m1i=New_Mean__1, sd1i=New_SD__1, n1i=Sample_Size_n_Treatment, m2i=New_Mean, sd2i=New_SD, n2i=Sample_Size_n_Control, data=Insulin_AUC)

OF_lnRR_Insulin_MA <- rma.mv(yi, vi,random = list(~1|Paper_ID,~1|Cohort_ID), data=Effect_Size_Insulin[Effect_Size_Insulin$Exposure_Type == "One off",], method = 'REML') 
summary(OF_lnRR_Insulin_MA)

#Insulin MG
MG_lnRR_Insulin_MA <- rma.mv(yi, vi,random = list(~1|Paper_ID,~1|Cohort_ID), data=Effect_Size_Insulin[Effect_Size_Insulin$Exposure_Type == "Multigenerational",], method = 'REML') 
summary(MG_lnRR_Insulin_MA)

#Triglycerides One off
Effect_Size_TG <- escalc(measure="ROM", m1i=Mean_Treatment, sd1i=SD_Treatment, n1i=Sample_Size_n_Treatment, m2i=Mean_Control_Orig, sd2i=SD_Control_Orig, n2i=Sample_Size_n_Control, data=Triglycerides)

OF_lnRR_TG_MA <- rma.mv(yi, vi,random = list(~1|Paper_ID,~1|Cohort_ID), data=Effect_Size_TG[Effect_Size_TG$Exposure_Type == "One off",], method = 'REML') 
summary(OF_lnRR_TG_MA)

#Triglycerides MG
MG_lnRR_TG_MA <- rma.mv(yi, vi,random = list(~1|Paper_ID,~1|Cohort_ID), data=Effect_Size_TG[Effect_Size_TG$Exposure_Type == "Multigenerational",], method = 'REML') 
summary(MG_lnRR_TG_MA)

#Adiposity one off
Effect_Size_Adiposity <- escalc(measure="ROM", m1i=Mean_Treatment, sd1i=SD_Treatment, n1i=Sample_Size_n_Treatment, m2i=Mean_Control_Orig, sd2i=SD_Control_Orig, n2i=Sample_Size_n_Control, data=Adiposity)

OF_lnRR_Adiposity_MA <- rma.mv(yi, vi,random = list(~1|Paper_ID,~1|Cohort_ID), data=Effect_Size_Adiposity[Effect_Size_Adiposity$Exposure_Type == "One off",], method = 'REML') 
summary(OF_lnRR_Adiposity_MA)

#Adiposity MG
MG_lnRR_Adiposity_MA <- rma.mv(yi, vi,random = list(~1|Paper_ID,~1|Cohort_ID), data=Effect_Size_Adiposity[Effect_Size_Adiposity$Exposure_Type == "Multigenerational",], method = 'REML') 
summary(MG_lnRR_Adiposity_MA)

#Leptin
Effect_Size_Leptin <- escalc(measure="ROM", m1i=Mean_Treatment, sd1i=SD_Treatment, n1i=Sample_Size_n_Treatment, m2i=Mean_Control_Orig, sd2i=SD_Control_Orig, n2i=Sample_Size_n_Control, data=Leptin)

OF_lnRR_Leptin_MA <- rma.mv(yi, vi,random = list(~1|Paper_ID,~1|Cohort_ID), data=Effect_Size_Leptin[Effect_Size_Leptin$Exposure_Type == "One off",], method = 'REML') 
summary(OF_lnRR_Leptin_MA)

#Leptin MG
MG_lnRR_Leptin_MA <- rma.mv(yi, vi,random = list(~1|Paper_ID,~1|Cohort_ID), data=Effect_Size_Leptin[Effect_Size_Leptin$Exposure_Type == "Multigenerational",], method = 'REML') 
summary(MG_lnRR_Leptin_MA)


```

# **2. Summary table and figure**
```{r}
# Making a table of meta-analytic results for ln_RR

experiment_type <- c(rep("OF", 6), rep("MG", 6))

trait_type <- rep(c("Body_Weight", "Glucose", "Triglycerides", "Insulin", "Adiposity", "Leptin"), 2)  

lnRR_MA_means <- c(OF_lnRR_BW_MA$b, OF_lnRR_Glucose_MA$b, OF_lnRR_TG_MA$b, OF_lnRR_Insulin_MA$b, OF_lnRR_Adiposity_MA$b, OF_lnRR_Leptin_MA$b, MG_lnRR_BW_MA$b, MG_lnRR_Glucose_MA$b, MG_lnRR_TG_MA$b, MG_lnRR_Insulin_MA$b, MG_lnRR_Adiposity_MA$b, MG_lnRR_Leptin_MA$b)

lnRR_MA_means

lnRR_MA_cilb <- c(OF_lnRR_BW_MA$ci.lb, OF_lnRR_Glucose_MA$ci.lb, OF_lnRR_TG_MA$ci.lb, OF_lnRR_Insulin_MA$ci.lb, OF_lnRR_Adiposity_MA$ci.lb, OF_lnRR_Leptin_MA$ci.lb, MG_lnRR_BW_MA$ci.lb, MG_lnRR_Glucose_MA$ci.lb, MG_lnRR_TG_MA$ci.lb, MG_lnRR_Insulin_MA$ci.lb, MG_lnRR_Adiposity_MA$ci.lb, MG_lnRR_Leptin_MA$ci.lb)

lnRR_MA_cilb

lnRR_MA_ciub <- c(OF_lnRR_BW_MA$ci.ub, OF_lnRR_Glucose_MA$ci.ub, OF_lnRR_TG_MA$ci.ub, OF_lnRR_Insulin_MA$ci.ub, OF_lnRR_Adiposity_MA$ci.ub, OF_lnRR_Leptin_MA$ci.ub, MG_lnRR_BW_MA$ci.ub, MG_lnRR_Glucose_MA$ci.ub, MG_lnRR_TG_MA$ci.ub, MG_lnRR_Insulin_MA$ci.ub, MG_lnRR_Adiposity_MA$ci.ub, MG_lnRR_Leptin_MA$ci.ub)

lnRR_MA_ciub

lnRR_MA_k <- c(OF_lnRR_BW_MA$k, OF_lnRR_Glucose_MA$k, OF_lnRR_TG_MA$k, OF_lnRR_Insulin_MA$k, OF_lnRR_Adiposity_MA$k, OF_lnRR_Leptin_MA$k, MG_lnRR_BW_MA$k, MG_lnRR_Glucose_MA$k, MG_lnRR_TG_MA$k, MG_lnRR_Insulin_MA$k, MG_lnRR_Adiposity_MA$k, MG_lnRR_Leptin_MA$k)

lnRR_MA_k

length(OF_lnRR_BW_MA$s.levels[1][[1]])

lnRR_MA_Npapers <- c(length(OF_lnRR_BW_MA$s.levels[1][[1]]), 
                     length(OF_lnRR_Glucose_MA$s.levels[1][[1]]),
                     length(OF_lnRR_TG_MA$s.levels[1][[1]]),
                     length(OF_lnRR_Insulin_MA$s.levels[1][[1]]),
                     length(OF_lnRR_Adiposity_MA$s.levels[1][[1]]),
                     length(OF_lnRR_Leptin_MA$s.levels[1][[1]]),
                     length(MG_lnRR_BW_MA$s.levels[1][[1]]),
                     length(MG_lnRR_Glucose_MA$s.levels[1][[1]]),
                     length(MG_lnRR_TG_MA$s.levels[1][[1]]),
                     length(MG_lnRR_Insulin_MA$s.levels[1][[1]]),
                     length(MG_lnRR_Adiposity_MA$s.levels[1][[1]]),
                     length(MG_lnRR_Leptin_MA$s.levels[1][[1]])
                     )
                     
lnRR_MA_Npapers

lnRR_MA_Ncohorts <- c(length(OF_lnRR_BW_MA$s.levels[2][[1]]), 
                     length(OF_lnRR_Glucose_MA$s.levels[2][[1]]),
                     length(OF_lnRR_TG_MA$s.levels[2][[1]]),
                     length(OF_lnRR_Insulin_MA$s.levels[2][[1]]),
                     length(OF_lnRR_Adiposity_MA$s.levels[2][[1]]),
                     length(OF_lnRR_Leptin_MA$s.levels[2][[1]]),
                     length(MG_lnRR_BW_MA$s.levels[2][[1]]),
                     length(MG_lnRR_Glucose_MA$s.levels[2][[1]]),
                     length(MG_lnRR_TG_MA$s.levels[2][[1]]),
                     length(MG_lnRR_Insulin_MA$s.levels[2][[1]]),
                     length(MG_lnRR_Adiposity_MA$s.levels[2][[1]]),
                     length(MG_lnRR_Leptin_MA$s.levels[2][[1]])
                     )
                     
lnRR_MA_Ncohorts  

#create data fame
lnRR_MA_results <- data.frame(Experiment_type = experiment_type, trait = trait_type, mean = lnRR_MA_means, ci.lb= lnRR_MA_cilb, ci.ub= lnRR_MA_ciub, k= lnRR_MA_k, N_papers = lnRR_MA_Npapers, N_cohorts=lnRR_MA_Ncohorts)

lnRR_MA_results

lnRR_MA_results <- unite(lnRR_MA_results, "labels", c("Experiment_type", "trait"), sep = " - ", remove = FALSE)

lnRR_MA_results

#Plotting

plot_lnRR <- ggplot(lnRR_MA_results, aes(x=trait, y=mean, colour=Experiment_type)) + 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3)) +
  geom_point(aes(x = trait, y = mean), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(title ="Difference between treatment and control in means", x = "Traits", y = "lnRR") +
  coord_flip()
 
plot_lnRR

ggsave("../figs/plot_lnRR.png")

```


```{r}
#ALL TRAITS ANALYSIS

Effect_Size_All_Traits <- escalc(measure="ROM", m1i=Mean_Treatment, sd1i=SD_Treatment, n1i=Sample_Size_n_Treatment, m2i=Mean_Control, sd2i=SD_Control, n2i=Sample_Size_n_Control, data=ALL_TRAITS)

hist(Effect_Size_All_Traits$yi)
hist(log(Effect_Size_All_Traits$vi))
```

```{r}
#Modelling all traits exposure type

All_Traits_Analysis <- rma.mv(yi, vi, mods = ~relevel(Exposure_Type, ref="One off"), random = list(~1|Trait, ~1|Paper_ID,~1|Cohort_ID), data=Effect_Size_All_Traits, method = 'REML')

summary(All_Traits_Analysis)

#Intercept only model
All_Traits_Analysis <- rma.mv(yi, vi, mods = ~relevel(Exposure_Type, ref="One off")-1, random = list(~1|Trait, ~1|Paper_ID,~1|Cohort_ID), data=Effect_Size_All_Traits, method = 'REML')

summary(All_Traits_Analysis)
```


```{r}
# Sex as a moderator
All_Traits_Analysis_Sex <- rma.mv(yi, vi, mods = ~relevel(Sex, ref = "Female")-1, random = list(~1|Trait, ~1|Paper_ID,~1|Cohort_ID), data=Effect_Size_All_Traits, method = 'REML')

summary(All_Traits_Analysis_Sex)

#subsetted
All_Traits_Analysis_Sex <- rma.mv(yi, vi, mods = ~relevel(Sex, ref = "Female"), random = list(~1|Trait, ~1|Paper_ID,~1|Cohort_ID), data=Effect_Size_All_Traits, method = 'REML', subset = (Sex!="Both"))

summary(All_Traits_Analysis_Sex)

#Generation 
All_Traits_Analysis <- rma.mv(yi, vi, mods = ~relevel(Generation, ref="F2")-1, random = list(~1|Trait, ~1|Paper_ID,~1|Cohort_ID), data=Effect_Size_All_Traits, method = 'REML')

summary(All_Traits_Analysis)

#Generation interaction with exposure type 
All_Traits_Analysis <- rma.mv(yi, vi, mods = ~relevel(Generation, ref="F2") * Exposure_Type, random = list(~1|Trait, ~1|Paper_ID,~1|Cohort_ID), data=Effect_Size_All_Traits, method = 'REML')

summary(All_Traits_Analysis)
```




```{r}
#Notes

#Converting to factors is crucial when attempting to run models with categorical variables ! To do so, we need to use the function: "as.factor" 
#I also need to make sure to do exploratory analysis BEFORE meeting with Shinichi, the data should be clean and ready to analyse! I need to do histograms to be able to identify any issues with the effect sizes !
```


```{r}
#Meta-regression
str(lnRR_BW_MA_ES) #is it a factor
is.factor(lnRR_BW_MA_ES$Sex)

levels(lnRR_BW_MA_ES$Sex)
table(lnRR_BW_MA_ES$Sex)
lnRR_BW_MA_ES$Sex <- gsub(" ", "", lnRR_BW_MA_ES$Sex) #cleaning spaces

Body_Weight_Sex <- rma.mv(yi, vi,mods = ~ relevel(as.factor(Sex), ref="Male"), random = list(~1|Paper_ID,~1|Cohort_ID), data=lnRR_BW_MA_ES[lnRR_BW_MA_ES$Exposure_Type == "One off",], method = 'REML') 

Body_Weight_Sex <- rma.mv(yi, vi,mods = ~ Sex -1, random = list(~1|Paper_ID,~1|Cohort_ID), data=lnRR_BW_MA_ES[lnRR_BW_MA_ES$Exposure_Type == "One off",], method = 'REML') 

summary(Body_Weight_Sex)

#Glucose, tolerance test vs. fbg

Glucose_Test_Type <- rma.mv(yi, vi,mods = ~ Tolerance_test, random = list(~1|Paper_ID,~1|Cohort_ID), data=Effect_Size_Glucose[Effect_Size_Glucose$Exposure_Type == "One off",], method = 'REML') 

summary(Glucose_Test_Type)
```




