---
title: "Adiposity and TG"
author: "Hamza"
date: "6 October 2019"
output:
  pdf_document: default
  html_document: default
---

```{r load packages, include=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(openxlsx)  
library(knitr)
library(metafor)
library(ggplot2)
library(readxl)
```

```{r}
load(file="Effect_Size_All_Traits.RData")
load(file="Effect_Size_All_Traits_lnCVR.RData")

Adiposity_lnRR <- subset(Effect_Size_All_Traits, Effect_Size_All_Traits$Trait == "Adiposity")

Adiposity_lnRR_MG <- subset(Adiposity_lnRR, Adiposity_lnRR$Exposure_Type == "Multigenerational")
Adiposity_lnRR_OF <- subset(Adiposity_lnRR, Adiposity_lnRR$Exposure_Type == "One off")
```
#Adiposity
```{r}

#Overall analysis, not split

Adiposity_overall_lnRR_0mods <- rma.mv(yi, vi,random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Adiposity_lnRR, method = 'REML')

summary(Adiposity_overall_lnRR_0mods)
funnel(Adiposity_overall_lnRR_0mods)

#Tibble of overall results

Adiposity_overall_lnRR <- tibble(
  ID = "Overall", 
  lnRR = 0.7172,
  ci.lb = 0.1899,
  ci.ub = 1.2445
)

plot_adiposity_overall <- ggplot(Adiposity_overall_lnRR, aes(x=ID, y=lnRR)) + 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3)) +
  geom_point(aes(x = ID, y = lnRR), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(title ="Adiposity differences, overall", x = "ID", y = "lnRR") +
  coord_flip()
plot_adiposity_overall

```

#Splitting by exposure type
```{r}
Adiposity_overall_lnRR_MG <- rma.mv(yi, vi,random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Adiposity_lnRR_MG, method = 'REML')

summary(Adiposity_overall_lnRR_MG)
funnel (Adiposity_overall_lnRR_MG)

Adiposity_overall_lnRR_OF <- rma.mv(yi, vi,random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Adiposity_lnRR_OF, method = 'REML')

summary(Adiposity_overall_lnRR_OF)
funnel (Adiposity_overall_lnRR_OF)

Adiposity_Exp_lnRR <- tibble(
  Exposure_Type = c("Multigenerational", "One off"),
  lnRR = c(1.2407,0.1194),
  ci.lb = c(0.5792,-0.0079),
  ci.ub = c(1.9022,0.2466)
)

Adiposity_Exp_lnRR



#Plotting when split by exp type

plot_Adiposity_exp_type <- ggplot(Adiposity_Exp_lnRR, aes(x=Exposure_Type, y=lnRR, colour = Exposure_Type)) + 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3)) +
  geom_point(aes(x = Exposure_Type, y = lnRR), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(x = "Exp_Type", y = "lnRR") +
  coord_flip()
plot_Adiposity_exp_type

```
#Adiposity analysis with moderators (split by exposure type)
```{r}
Adiposity_MG_F0 <- rma.mv(yi, vi, mods = ~F0_Parent_Exposed-1, random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Adiposity_lnRR_MG, method = 'REML')

Adiposity_MG_F0

Adiposity_OF_F0 <- rma.mv(yi, vi, mods = ~F0_Parent_Exposed-1, random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Adiposity_lnRR_OF, method = 'REML')

Adiposity_OF_F0


Adiposity_MG_Sex <- rma.mv(yi, vi, mods = ~Sex-1, random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Adiposity_lnRR_MG, method = 'REML')

Adiposity_MG_Sex

Adiposity_OF_Sex <- rma.mv(yi, vi, mods = ~Sex-1, random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Adiposity_lnRR_OF, method = 'REML')

Adiposity_OF_Sex

Adiposity_Exp_mods_lnRR <- tibble(
  Exposure_Type = c("Multigenerational","Multigenerational", "One off", "One off", "Multigenerational", "Multigenerational", "One off","One off"),
  mod = c("F0 Female","F0 Male", "F0 Female", "F0 Male","Female Offspring", "Male Offspring","Female Offspring", "Male Offspring"),
  lnRR = c(1.3709,0.6531,0.1384,-0.0011,1.1890,1.2919,0.0423,0.1976),
  ci.lb = c(0.6043,-0.9971,-0.0080,-0.4012,0.5005,0.6033,-0.1069,0.0513),
  ci.ub = c(2.1375,2.3034,0.2849,0.3990,1.8774,1.9805,0.1914,0.3438)
)

plot_Adiposity_lnRR_mods_exp <- ggplot(Adiposity_Exp_mods_lnRR, aes(x=mod, y=lnRR, colour=Exposure_Type))+ 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3)) +
  geom_point(aes(x = mod, y = lnRR), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(x = "mod", y = "lnRR") +
  coord_flip()
 
plot_Adiposity_lnRR_mods_exp
```

#ADiposity lnCVR
```{r}

#Subset Adiposity lnCVR Data
Adiposity_lnCVR <- subset(Effect_Size_All_Traits_lnCVR, Effect_Size_All_Traits_lnCVR$Trait == "Adiposity")

Adiposity_lnCVR_MG <- subset(Adiposity_lnCVR, Adiposity_lnCVR$Exposure_Type == "Multigenerational")
Adiposity_lnCVR_OF <- subset(Adiposity_lnCVR, Adiposity_lnCVR$Exposure_Type == "One off")



Adiposity_overall_lnCVR_0mods <- rma.mv(yi, vi, random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Adiposity_lnCVR, method = 'REML')

summary(Adiposity_overall_lnCVR_0mods)

#Tibble of overall results

Insulin_overall_lnCVR <- tibble(
  ID = "Overall", 
  lnCVR = -0.0529,
  ci.lb = -0.2818,
  ci.ub = 0.175
)

```
#Adiposity lnCVR (split by exposure type)
```{r}
Adiposity_overall_lnCVR_MG <- rma.mv(yi, vi,random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Adiposity_lnCVR_MG, method = 'REML')

summary(Adiposity_overall_lnCVR_MG)
funnel (Adiposity_overall_lnCVR_MG)

Adiposity_overall_lnCVR_OF <- rma.mv(yi, vi,random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Adiposity_lnCVR_OF, method = 'REML')

summary(Adiposity_overall_lnCVR_OF)
funnel (Adiposity_overall_lnCVR_OF)

Adiposity_Exp_lnCVR <- tibble(
  Exposure_Type = c("Multigenerational", "One off"),
  lnCVR = c(0.0018,-0.0857),
  ci.lb = c(-0.3380,-0.3660),
  ci.ub = c(0.3415,0.1946)
)

Adiposity_Exp_lnCVR



#Plotting when split by exp type

plot_Adiposity_exp_type_lnCVR <- ggplot(Adiposity_Exp_lnCVR, aes(x=Exposure_Type, y=lnCVR, colour = Exposure_Type)) + 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3)) +
  geom_point(aes(x = Exposure_Type, y = lnCVR), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(x = "Exp_Type", y = "lnCVR") +
  coord_flip()
plot_Adiposity_exp_type_lnCVR
```

#Adiposity analysis with moderators (split by exposure type)
```{r}
Adiposity_MG_F0_lnCVR <- rma.mv(yi, vi, mods = ~F0_Parent_Exposed-1, random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Adiposity_lnCVR_MG, method = 'REML')

Adiposity_MG_F0_lnCVR

Adiposity_OF_F0_lnCVR <- rma.mv(yi, vi, mods = ~F0_Parent_Exposed-1, random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Adiposity_lnCVR_OF, method = 'REML')

Adiposity_OF_F0_lnCVR


Adiposity_MG_Sex_lnCVR <- rma.mv(yi, vi, mods = ~Sex-1, random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Adiposity_lnCVR_MG, method = 'REML')

Adiposity_MG_Sex_lnCVR

Adiposity_OF_Sex_lnCVR <- rma.mv(yi, vi, mods = ~Sex-1, random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Adiposity_lnCVR_OF, method = 'REML')

Adiposity_OF_Sex_lnCVR

Adiposity_Exp_mods_lnCVR <- tibble(
  Exposure_Type = c("Multigenerational","Multigenerational", "One off", "One off", "Multigenerational", "Multigenerational", "One off","One off"),
  mod = c("F0 Female","F0 Male", "F0 Female", "F0 Male","Female Offspring", "Male Offspring","Female Offspring", "Male Offspring"),
  lnCVR = c(0.0503,-0.0858,-0.1104,0.0600,0.0267,-0.0252,0.0154,-0.1752),
  ci.lb = c(-0.3711,-0.9736,-0.4445,-0.6657,-0.4326,-0.4377,-0.3060,-0.4899),
  ci.ub = c(0.4717,0.8020,0.2237,0.7857,0.4860,0.3873,0.3368,0.1394)
)

plot_Adiposity_lnCVR_mods_exp <- ggplot(Adiposity_Exp_mods_lnCVR, aes(x=mod, y=lnCVR, colour=Exposure_Type))+ 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3)) +
  geom_point(aes(x = mod, y = lnCVR), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(x = "mod", y = "lnCVR") +
  coord_flip()
 
plot_Adiposity_lnCVR_mods_exp





```
#Triglycerides lnRR
```{r}
#Subsetting Data for lnRR
Triglycerides_lnRR <- subset(Effect_Size_All_Traits, Effect_Size_All_Traits$Trait == "Triglycerides")

Triglycerides_lnRR_MG <- subset(Triglycerides_lnRR, Triglycerides_lnRR$Exposure_Type == "Multigenerational")
Triglycerides_lnRR_OF <- subset(Triglycerides_lnRR, Triglycerides_lnRR$Exposure_Type == "One off")

#Subsetting Data for lmCVR
Triglycerides_lnCVR <- subset(Effect_Size_All_Traits_lnCVR, Effect_Size_All_Traits_lnCVR$Trait == "Triglycerides")

Triglycerides_lnCVR_MG <- subset(Triglycerides_lnCVR, Triglycerides_lnCVR$Exposure_Type == "Multigenerational")
Triglycerides_lnCVR_OF <- subset(Triglycerides_lnCVR, Triglycerides_lnCVR$Exposure_Type == "One off")
```


#Overall Triglycerides analysis
```{r}




TG_overall_lnRR_0mods <- rma.mv(yi, vi,random = list(~1|Cohort_ID,~1|ES_ID), data=Triglycerides_lnRR, method = 'REML')

summary(TG_overall_lnRR_0mods)

TG_overall_lnRR <- tibble(
  ID = "Overall", 
  lnRR = 0.1894,
  ci.lb = 0.0168,
  ci.ub = 0.3621
)



plot_tg_overall <- ggplot(TG_overall_lnRR, aes(x=ID, y=lnRR)) + 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3)) +
  geom_point(aes(x = ID, y = lnRR), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(title ="TG differences, overall", x = "ID", y = "lnRR") +
  coord_flip()
plot_tg_overall
```
#Triglycerides analysis (split by exposure type)
```{r}
Triglycerides_overall_lnRR_MG <- rma.mv(yi, vi,random = list(~1|Cohort_ID,~1|ES_ID), data=Triglycerides_lnRR_MG, method = 'REML')

summary(Triglycerides_overall_lnRR_MG)
funnel (Triglycerides_overall_lnRR_MG)

Triglycerides_overall_lnRR_OF <- rma.mv(yi, vi,random = list(~1|Cohort_ID,~1|ES_ID), data=Triglycerides_lnRR_OF, method = 'REML')

summary(Triglycerides_overall_lnRR_OF)
funnel (Triglycerides_overall_lnRR_OF)

Triglycerides_Exp_lnRR <- tibble(
  Exposure_Type = c("Multigenerational", "One off"),
  lnRR = c(0.4658,0.1077),
  ci.lb = c(-0.2411,-0.0109),
  ci.ub = c(1.1727,0.2262)
)

Triglycerides_Exp_lnRR



#Plotting when split by exp type

plot_Triglycerides_exp_type <- ggplot(Triglycerides_Exp_lnRR, aes(x=Exposure_Type, y=lnRR, colour = Exposure_Type)) + 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3)) +
  geom_point(aes(x = Exposure_Type, y = lnRR), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(x = "Exp_Type", y = "lnRR") +
  coord_flip()
plot_Triglycerides_exp_type
```

#Triglycerides lnCVR

#Overall Triglycerides analysis
```{r}




TG_overall_lnCVR_0mods <- rma.mv(yi, vi,random = list(~1|Cohort_ID,~1|ES_ID), data=Triglycerides_lnCVR, method = 'REML')

summary(TG_overall_lnCVR_0mods)

TG_overall_lnCVR <- tibble(
  ID = "Overall", 
  lnCVR = -0.1844,
  ci.lb = -0.3993,
  ci.ub =0.0305 
)



plot_tg_overall_lnCVR <- ggplot(TG_overall_lnCVR, aes(x=ID, y=lnCVR)) + 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3)) +
  geom_point(aes(x = ID, y = lnCVR), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(title ="TG differences, overall", x = "ID", y = "lnCVR") +
  coord_flip()
plot_tg_overall_lnCVR
```
#Triglycerides analysis (split by exposure type)
```{r}
Triglycerides_overall_lnCVR_MG <- rma.mv(yi, vi,random = list(~1|Cohort_ID,~1|ES_ID), data=Triglycerides_lnCVR_MG, method = 'REML')

summary(Triglycerides_overall_lnCVR_MG)
funnel (Triglycerides_overall_lnCVR_MG)

Triglycerides_overall_lnCVR_OF <- rma.mv(yi, vi,random = list(~1|Cohort_ID,~1|ES_ID), data=Triglycerides_lnCVR_OF, method = 'REML')

summary(Triglycerides_overall_lnCVR_OF)
funnel (Triglycerides_overall_lnCVR_OF)

Triglycerides_Exp_lnCVR <- tibble(
  Exposure_Type = c("Multigenerational", "One off"),
  lnCVR = c(-0.5575,-0.0900),
  ci.lb = c(-1.2913,-0.2972),
  ci.ub = c(0.1763,0.1171)
)

Triglycerides_Exp_lnCVR



#Plotting when split by exp type

plot_Triglycerides_exp_type <- ggplot(Triglycerides_Exp_lnCVR, aes(x=Exposure_Type, y=lnCVR, colour = Exposure_Type)) + 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3)) +
  geom_point(aes(x = Exposure_Type, y = lnCVR), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(x = "Exp_Type", y = "lnCVR") +
  coord_flip()
plot_Triglycerides_exp_type
```







