---
title: "Body Weight"
author: "Hamza"
date: "1 October 2019"
output:
  pdf_document: default
  html_document: default
---
```{r load packages, include=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(openxlsx)  
library(knitr)
library(metafor)
library(ggplot2)
library(readxl)
```


## Meta-analysis Body Weight

```{r}
load(file="Effect_Size_All_Traits.RData")
load(file="Effect_Size_All_Traits_lnCVR.RData")

Body_Weight_lnRR <- subset(Effect_Size_All_Traits, Effect_Size_All_Traits$Trait == "Body_Weight")
```
```{r}

#Subetting (removing BOTH)

Body_Weight_lnRR_MG <- subset(Body_Weight_lnRR, Body_Weight_lnRR$Exposure_Type == "Multigenerational")

Body_Weight_lnRR_OF <- subset(Body_Weight_lnRR, Body_Weight_lnRR$Exposure_Type == "One off")
```
#Overall analysis, not split
```{r}



Body_Weight_overall <- rma.mv(yi, vi, random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Body_Weight_lnRR, method = 'REML')

summary(Body_Weight_overall)
funnel(Body_Weight_overall)

#Tibble of overall results

Body_Weight_overall_lnRR <- tibble(
  ID = "Overall", 
  lnRR = 0.1018,
  ci.lb = 0.0128,
  ci.ub = 0.1909
)

plot_BW_overall <- ggplot(Body_Weight_overall_lnRR, aes(x=ID, y=lnRR)) + 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3)) +
  geom_point(aes(x = ID, y = lnRR), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(title ="Body Weight differences, overall", x = "ID", y = "lnRR") +
  coord_flip()
plot_BW_overall
```

#Overall analysis when split by exposure type
```{r}



Body_Weight_MG <- rma.mv(yi, vi, random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Body_Weight_lnRR_MG, method = 'REML')

summary(Body_Weight_MG)
funnel(Body_Weight_MG)

Body_Weight_OF <- rma.mv(yi, vi, random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Body_Weight_lnRR_OF, method = 'REML')

summary(Body_Weight_OF)
funnel(Body_Weight_OF)

#Tibble of results

Body_Weight_Exp_lnRR <- tibble(
  Exposure_Type = c("Multigenerational", "One off"),
  k = c(52,94),
  lnRR = c(0.1952, 0.0245),
  ci.lb = c(0.0337, 0.0018),
  ci.ub = c(0.3566, 0.0471)
)

Body_Weight_Exp_lnRR



#Plotting when split by exp type

plot_BW_exp_type <- ggplot(Body_Weight_Exp_lnRR, aes(x=Exposure_Type, y=lnRR, colour = Exposure_Type)) + 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3)) +
  geom_point(aes(x = Exposure_Type, y = lnRR), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(title ="Body Weight differences, exp type", x = "Exp_Type", y = "lnRR") +
  coord_flip()
plot_BW_exp_type
```
#### Running meta-analysis (Overall with moderators, and then overall split by exposure type with moderators)

```{r, echo=FALSE}
#Adding moderators
BW_Exp_Type <- rma.mv(yi, vi, mods = ~Exposure_Type-1, random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Body_Weight_lnRR, method = 'REML')

BW_Exp_Type
funnel(BW_Exp_Type)

BW_F0 <- rma.mv(yi, vi, mods = ~F0_Parent_Exposed-1, random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Body_Weight_lnRR, method = 'REML')

summary(BW_F0)
funnel(BW_F0)

BW_Sex <- rma.mv(yi, vi, mods = ~Sex-1, random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Body_Weight_lnRR, method = 'REML')

summary(BW_Sex)
funnel(BW_Sex)

#Tibble of results

Body_Weight_Mods_lnRR <- tibble(
  ID = c("Multigenerational", "One off", "Both F0", "F0 Female", "F0 Male", "Both Sexes Grand Offspring", "Female Grand Offspring", "Male Grand Offspring"),
  lnRR = c(BW_Exp_Type$b[1],BW_Exp_Type$b[2],BW_F0$b[1],BW_F0$b[2],BW_F0$b[3],BW_Sex$b[1],BW_Sex$b[2],BW_Sex$b[3]),
  ci.lb = c(BW_Exp_Type$ci.lb[1],BW_Exp_Type$ci.lb[2],BW_F0$ci.lb[1],BW_F0$ci.lb[2],BW_F0$ci.lb[3],BW_Sex$ci.lb[1],BW_Sex$ci.lb[2],BW_Sex$ci.lb[3]),
  ci.ub = c(BW_Exp_Type$ci.ub[1],BW_Exp_Type$ci.ub[2],BW_F0$ci.ub[1],BW_F0$ci.ub[2],BW_F0$ci.ub[3],BW_Sex$ci.ub[1],BW_Sex$ci.ub[2],BW_Sex$ci.ub[3])
)

Body_Weight_Mods_lnRR

plot_BW_mods <- ggplot(Body_Weight_Mods_lnRR, aes(x=ID, y=lnRR)) + 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3)) +
  geom_point(aes(x = ID, y = lnRR), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(x = "Exp_Type", y = "lnRR") +
  coord_flip()
plot_BW_mods

```
```{r}
#splitting by exposure type

Body_Weight_MG_F0 <- rma.mv(yi, vi, mods = ~F0_Parent_Exposed-1, random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Body_Weight_lnRR_MG, method = 'REML')

Body_Weight_MG_F0

Body_Weight_OF_F0 <- rma.mv(yi, vi, mods = ~F0_Parent_Exposed-1, random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Body_Weight_lnRR_OF, method = 'REML')

Body_Weight_OF_F0


Body_Weight_MG_Sex <- rma.mv(yi, vi, mods = ~Sex-1, random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Body_Weight_lnRR_MG, method = 'REML')

Body_Weight_MG_Sex

Body_Weight_OF_Sex <- rma.mv(yi, vi, mods = ~Sex-1, random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Body_Weight_lnRR_OF, method = 'REML')

Body_Weight_OF_Sex

Overall_Exp_mods_lnRR <- tibble(
  Exposure_Type = c("Multigenerational","Multigenerational", "One off", "One off", "One off", "Multigenerational", "Multigenerational","Multigenerational", "One off","One off","One off" ),
  mod = c("F0 Female","F0 Male", "F0 Both", "F0 Female", "F0 Male","Both Offspring Sex","Female Offspring", "Male Offspring", "Both Offspring Sex","Female Offspring", "Male Offspring"),
  lnRR = c(0.2197,0.0723,0.1409,0.0296,0.0025,-0.0353,0.2799,0.2805,-0.1987,0.0242,0.0252),
  ci.lb = c(0.0378,-0.3345,0.0592,0.0039,-0.0367,-0.3238,0.1021,0.1008,-0.9166,-0.0012,0.0002),
  ci.ub = c(0.4015,0.4791,0.2226,0.0553,0.0417,0.2532,0.4576,0.4602,0.5192,0.0496,0.0502)
)

plot_lnRR_overall_mods_exp <- ggplot(Overall_Exp_mods_lnRR, aes(x=mod, y=lnRR, colour=Exposure_Type))+ 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3)) +
  geom_point(aes(x = mod, y = lnRR), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(x = "mod", y = "lnRR") +
  coord_flip()
 
plot_lnRR_overall_mods_exp

```

## Meta-analysis overall results (lnCVR)

### 4. Calculating effect sizes (Done)

We calculated our effect sizes (lnCVR) for our complete data set (all traits).
```{r, include = FALSE}

#Subetting

Body_Weight_lnCVR <- subset(Effect_Size_All_Traits_lnCVR, Effect_Size_All_Traits_lnCVR$Trait == "Body_Weight")

Body_Weight_lnCVR_MG <- subset(Body_Weight_lnCVR, Body_Weight_lnCVR$Exposure_Type == "Multigenerational")

Body_Weight_lnCVR_OF <- subset(Body_Weight_lnCVR, Body_Weight_lnCVR$Exposure_Type == "One off")

```

#### 5. Running meta-analysis for body weight lnCVR 

#All Data (lnCVR)
```{r, include = FALSE}


Body_Weight_lnCVR_0mods <- rma.mv(yi, vi, random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Body_Weight_lnCVR, method = 'REML')

summary(Body_Weight_lnCVR_0mods)

#Tibble of overall results

Body_Weight_overall_lnCVR <- tibble(
  ID = "Overall", 
  lnCVR = 0.0744,
  ci.lb = -0.0430,
  ci.ub = 0.1917
)

plot_BW_overall_lnCVR <- ggplot(Body_Weight_overall_lnCVR, aes(x=ID, y=lnCVR, colour=ID)) + 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3)) +
  geom_point(aes(x = ID, y = lnCVR), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(title ="Body Weight differences, overall lnCVR", x = "ID", y = "lnCVR") +
  coord_flip()
plot_BW_overall_lnCVR

```


```{r}

# Modelling all traits with no mods MG (lnCVR)
Body_Weight_lnCVR_0mods_MG <- rma.mv(yi, vi, random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Body_Weight_lnCVR_MG, method = 'REML')


summary(Body_Weight_lnCVR_0mods_MG)



# Modelling all traits with no mods OF (lnCVR)
Body_Weight_lnCVR_0mods_OF <- rma.mv(yi, vi, random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Body_Weight_lnCVR_OF, method = 'REML')

summary(Body_Weight_lnCVR_0mods_OF)

#Tibble of results

Body_Weight_Exp_lnCVR <- tibble(
  Exposure_Type = c("Multigenerational", "One off"),
  lnCVR = c(0.1757,0.0044),
  ci.lb = c(0.0476,-0.1448),
  ci.ub = c(0.3038,0.1537)
)

Body_Weight_Exp_lnCVR



#Plotting when split by exp type

plot_BW_exp_type_lnCVR <- ggplot(Body_Weight_Exp_lnCVR, aes(x=Exposure_Type, y=lnCVR, colour = Exposure_Type)) + 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3)) +
  geom_point(aes(x = Exposure_Type, y = lnCVR), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(title ="Body Weight differences, exp type_lnCVR", x = "Exp_Type", y = "lnCVR") +
  coord_flip()
plot_BW_exp_type_lnCVR


```
#### Running meta-analysis (Overall with moderators)

```{r, echo=FALSE}
#Adding moderators
BW_Exp_lnCVR <- rma.mv(yi, vi, mods = ~Exposure_Type-1, random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Body_Weight_lnCVR, method = 'REML')

summary(BW_Exp_lnCVR)

BW_F0_lnCVR <- rma.mv(yi, vi, mods = ~F0_Parent_Exposed-1, random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Body_Weight_lnCVR, method = 'REML')

summary(BW_F0_lnCVR)

BW_Sex_lnCVR <- rma.mv(yi, vi, mods = ~Sex-1, random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Body_Weight_lnCVR, method = 'REML')

summary(BW_Sex_lnCVR)

#Tibble of results

Body_Weight_Mods_lnCVR <- tibble(
  ID = c("Multigenerational", "One off", "Both F0", "F0 Female", "F0 Male", "Both Sexes Grand Offspring", "Female Grand Offspring", "Male Grand Offspring"),
  lnCVR = c(BW_Exp_lnCVR$b[1], BW_Exp_lnCVR$b[2], BW_F0_lnCVR$b[1], BW_F0_lnCVR$b[2],BW_F0_lnCVR$b[3],BW_Sex_lnCVR$b[1],BW_Sex_lnCVR$b[2],BW_Sex_lnCVR$b[3]),
  ci.lb = c(BW_Exp_lnCVR$ci.lb[1], BW_Exp_lnCVR$ci.lb[2],BW_F0_lnCVR$ci.lb[1], BW_F0_lnCVR$ci.lb[2],BW_F0_lnCVR$ci.lb[3],BW_Sex_lnCVR$ci.lb[1],BW_Sex_lnCVR$ci.lb[2],BW_Sex_lnCVR$ci.lb[3]),
  ci.ub = c(BW_Exp_lnCVR$ci.ub[1], BW_Exp_lnCVR$ci.ub[2],BW_F0_lnCVR$ci.ub[1], BW_F0_lnCVR$ci.ub[2],BW_F0_lnCVR$ci.ub[3],BW_Sex_lnCVR$ci.ub[1],BW_Sex_lnCVR$ci.ub[2],BW_Sex_lnCVR$ci.ub[3])
)

Body_Weight_Mods_lnCVR

plot_BW_mods_lnCVR <- ggplot(Body_Weight_Mods_lnCVR, aes(x=ID, y=lnCVR )) + 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3), colour = "red") +
  geom_point(aes(x = ID, y = lnCVR), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(x = "ID", y = "lnCVR") +
  coord_flip()
plot_BW_mods_lnCVR
```
# Meta-regression when split by exposure type
```{r}
Body_Weight_MG_F0_lnCVR <- rma.mv(yi, vi, mods = ~F0_Parent_Exposed-1, random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Body_Weight_lnCVR_MG, method = 'REML')

Body_Weight_MG_F0_lnCVR

Body_Weight_OF_F0_lnCVR <- rma.mv(yi, vi, mods = ~F0_Parent_Exposed-1, random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Body_Weight_lnCVR_OF, method = 'REML')

Body_Weight_OF_F0_lnCVR


Body_Weight_MG_Sex_lnCVR <- rma.mv(yi, vi, mods = ~Sex-1, random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Body_Weight_lnCVR_MG, method = 'REML')

Body_Weight_MG_Sex_lnCVR

Body_Weight_OF_Sex_lnCVR <- rma.mv(yi, vi, mods = ~Sex-1, random = list(~1|Paper_ID,~1|Cohort_ID,~1|ES_ID), data=Body_Weight_lnCVR_OF, method = 'REML')

Body_Weight_OF_Sex_lnCVR

Overall_Exp_mods_lnCVR <- tibble(
  Exposure_Type = c("Multigenerational","Multigenerational", "One off", "One off", "One off", "Multigenerational", "Multigenerational","Multigenerational", "One off","One off","One off" ),
  mod = c("F0 Female","F0 Male", "F0 Both", "F0 Female", "F0 Male","Both Offspring Sex","Female Offspring", "Male Offspring", "Both Offspring Sex","Female Offspring", "Male Offspring"),
  lnCVR = c(0.1930,0.1122,-0.1228,-0.0000,0.0387,0.2032,0.2676,0.0518,-0.2760,-0.0174,0.0364),
  ci.lb = c(0.0477,-0.1682,-0.8491,-0.1743,-0.2637,-0.0966,0.0769,-0.1570,-1.5441,-0.1997,-0.1468),
  ci.ub = c(0.3383,0.3925,0.6035,0.1742,0.3410,0.5029,0.4583,0.2607,0.9920,0.1648,0.2195)
)

plot_lnCVR_overall_mods_exp <- ggplot(Overall_Exp_mods_lnCVR, aes(x=mod, y=lnCVR, colour=Exposure_Type))+ 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3)) +
  geom_point(aes(x = mod, y = lnCVR), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(x = "mod", y = "lnCVR") +
  coord_flip()
 
plot_lnCVR_overall_mods_exp
```


