---
title: "Body Weight"
author: "Hamza"
date: "1 October 2019"
output: html_document
---
```{r load packages, include=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(openxlsx)  
library(knitr)
library(metafor)
library(ggplot2)
library(readxl)
```


## Meta-regression Body Weight

```{r}
Body_Weight_lnRR <- read.csv("../data/Body_Weight_lnRR.csv")

ALL_TRAITS <- read.xlsx("../data/ALL_TRAITS.xlsx")
```
```{r}

#Subetting (removing BOTH)

Body_Weight_lnRR_MG <- subset(Body_Weight_lnRR, Body_Weight_lnRR$Exposure_Type == "Multigenerational")

Body_Weight_lnRR_OF <- subset(Body_Weight_lnRR, Body_Weight_lnRR$Exposure_Type == "One off")
```

```{r}

#Overall analysis, not split

Body_Weight_overall <- rma.mv(yi, vi, random = list(~1|Paper_ID,~1|Cohort_ID), data=Body_Weight_lnRR, method = 'REML')

summary(Body_Weight_overall)

#Tibble of overall results

Body_Weight_overall_lnRR <- tibble(
  ID = "Overall", 
  lnRR = 0.1028,
  ci.lb = 0.0103,
  ci.ub = 0.1953
)

plot_BW_overall <- ggplot(Body_Weight_overall_lnRR, aes(x=ID, y=lnRR)) + 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3)) +
  geom_point(aes(x = ID, y = lnRR), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(title ="Body Weight differences, overall", x = "ID", y = "lnRR") +
  coord_flip()
plot_BW_overall

W <- diag(1/Body_Weight_lnRR$vi)
X <- model.matrix(Body_Weight_overall)
P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
I2_overall_BW <- 100 * sum(Body_Weight_overall$sigma2) / (sum(Body_Weight_overall$sigma2) + (Body_Weight_overall$k-Body_Weight_overall$p)/sum(diag(P)))
I2_overall_BW
```


```{r}

#MG then OF

Body_Weight_MG <- rma.mv(yi, vi, random = list(~1|Paper_ID,~1|Cohort_ID), data=Body_Weight_lnRR_MG, method = 'REML')

summary(Body_Weight_MG)

Body_Weight_OF <- rma.mv(yi, vi, random = list(~1|Paper_ID,~1|Cohort_ID), data=Body_Weight_lnRR_OF, method = 'REML')

summary(Body_Weight_OF)


#Tibble of results

Body_Weight_Exp_lnRR <- tibble(
  Exposure_Type = c("Multigenerational", "One off"),
  k = c(52,94),
  lnRR = c(0.2042, 0.0246),
  ci.lb = c(0.0307, 0.0015),
  ci.ub = c(0.3777, 0.0477)
)

Body_Weight_Exp_lnRR



#Plotting when split by exp type

plot_BW_exp_type <- ggplot(Body_Weight_Exp_lnRR, aes(x=Exposure_Type, y=lnRR, colour = Exposure_Type)) + 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3)) +
  geom_point(aes(x = Exposure_Type, y = lnRR), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(title ="Body Weight differences, exp type", x = "Exp_Type", y = "lnRR") +
  coord_flip()
plot_BW_exp_type
```
#### Running meta-analysis (Overall with moderators, and then overall split by exposure type with moderators)

```{r, echo=FALSE}
#Adding moderators
BW_Exp_Type <- rma.mv(yi, vi, mods = ~Exposure_Type-1, random = list(~1|Paper_ID,~1|Cohort_ID), data=Body_Weight_lnRR, method = 'REML')

BW_Exp_Type

BW_F0 <- rma.mv(yi, vi, mods = ~F0_Parent_Exposed-1, random = list(~1|Paper_ID,~1|Cohort_ID), data=Body_Weight_lnRR, method = 'REML')

summary(BW_F0)

vars <- names(Body_Weight_lnRR) %in% c("v1", "v2", "v3")

BW_Sex <- rma.mv(yi, vi, mods = ~Sex-1, random = list(~1|Paper_ID,~1|Cohort_ID), data=Body_Weight_lnRR, method = 'REML')

summary(BW_Sex)

BW_Sex_Exp <- rma.mv(yi, vi, mods = ~Sex*Exposure_Type-1, random = list(~1|Paper_ID,~1|Cohort_ID), data=Body_Weight_lnRR, method = 'REML')

summary(BW_Sex_Exp)

#Tibble of results

Body_Weight_Mods_lnRR <- tibble(
  ID = c("Multigenerational", "One off", "Both F0", "F0 Female", "F0 Male", "Both Sexes Grand Offspring", "Female Grand Offspring", "Male Grand Offspring"),
  lnRR = c(BW_Exp_Type$b[1],BW_Exp_Type$b[2],BW_F0$b[1],BW_F0$b[2],BW_F0$b[3],BW_Sex$b[1],BW_Sex$b[2],BW_Sex$b[3]),
  ci.lb = c(BW_Exp_Type$ci.lb[1],BW_Exp_Type$ci.lb[2],BW_F0$ci.lb[1],BW_F0$ci.lb[2],BW_F0$ci.lb[3],BW_Sex$ci.lb[1],BW_Sex$ci.lb[2],BW_Sex$ci.lb[3]),
  ci.ub = c(BW_Exp_Type$ci.ub[1],BW_Exp_Type$ci.ub[2],BW_F0$ci.ub[1],BW_F0$ci.ub[2],BW_F0$ci.ub[3],BW_Sex$ci.ub[1],BW_Sex$ci.ub[2],BW_Sex$ci.ub[3])
)

Body_Weight_Mods_lnRR

plot_BW_mods <- ggplot(Body_Weight_Mods_lnRR, aes(x=ID, y=lnRR)) + 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3)) +
  geom_point(aes(x = ID, y = lnRR), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(x = "Exp_Type", y = "lnRR") +
  coord_flip()
plot_BW_mods

```
```{r}
#splitting by exposure type

Body_Weight_MG_F0 <- rma.mv(yi, vi, mods = ~F0_Parent_Exposed-1, random = list(~1|Paper_ID,~1|Cohort_ID), data=Body_Weight_lnRR_MG, method = 'REML')

Body_Weight_MG_F0

Body_Weight_OF_F0 <- rma.mv(yi, vi, mods = ~F0_Parent_Exposed-1, random = list(~1|Paper_ID,~1|Cohort_ID), data=Body_Weight_lnRR_OF, method = 'REML')

Body_Weight_OF_F0


Body_Weight_MG_Sex <- rma.mv(yi, vi, mods = ~Sex-1, random = list(~1|Paper_ID,~1|Cohort_ID), data=Body_Weight_lnRR_MG, method = 'REML')

Body_Weight_MG_Sex

Body_Weight_OF_Sex <- rma.mv(yi, vi, mods = ~Sex-1, random = list(~1|Paper_ID,~1|Cohort_ID), data=Body_Weight_lnRR_OF, method = 'REML')

Body_Weight_OF_Sex

```

## Meta-analysis overall results (lnCVR)

### 4. Calculating effect sizes (Done)

We calculated our effect sizes (lnCVR) for our complete data set (all traits).
```{r, include = FALSE}

Effect_Size_All_Traits_lnCVR <- escalc(measure="CVR", m1i=Mean_Treatment, sd1i=SD_Treatment, n1i=Sample_Size_n_Treatment, m2i=Mean_Control, sd2i=SD_Control, n2i=Sample_Size_n_Control, data=ALL_TRAITS)

#Converting into factors

Effect_Size_All_Traits_lnCVR$Trait <- factor(Effect_Size_All_Traits_lnCVR$Trait)
Effect_Size_All_Traits_lnCVR$Exposure_Type <- factor(Effect_Size_All_Traits_lnCVR$Exposure_Type)
Effect_Size_All_Traits_lnCVR$Sex <- factor(Effect_Size_All_Traits_lnCVR$Sex)
Effect_Size_All_Traits_lnCVR$Generation <- factor(Effect_Size_All_Traits_lnCVR$Generation)
Effect_Size_All_Traits_lnCVR$Cohort_ID <- factor(Effect_Size_All_Traits_lnCVR$Cohort_ID)
Effect_Size_All_Traits_lnCVR$Paper_ID <- factor(Effect_Size_All_Traits_lnCVR$Paper_ID)
Effect_Size_All_Traits_lnCVR$Rodent_type <- factor(Effect_Size_All_Traits_lnCVR$Rodent_type)
Effect_Size_All_Traits_lnCVR$F2_Diet_at_measurement <- factor(Effect_Size_All_Traits_lnCVR$F2_Diet_at_measurement)
Effect_Size_All_Traits_lnCVR$Strain <- factor(Effect_Size_All_Traits_lnCVR$Strain)
Effect_Size_All_Traits_lnCVR$F0_Parent_Exposed <- factor(Effect_Size_All_Traits_lnCVR$F0_Parent_Exposed)

#Subset into Body Weight

#Subetting

Body_Weight_lnCVR <- subset(Effect_Size_All_Traits_lnCVR, Effect_Size_All_Traits_lnCVR$Trait == "Body_Weight")

Body_Weight_lnCVR_MG <- subset(Body_Weight_lnCVR, Body_Weight_lnCVR$Exposure_Type == "Multigenerational")

Body_Weight_lnCVR_OF <- subset(Body_Weight_lnCVR, Body_Weight_lnCVR$Exposure_Type == "One off")

```

#### 5. Running meta-analysis for body weight lnCVR (overall, and then overall split by exposure type)
I conducted meta-analysis using lnCVR, first on the complete BW dataset, and then on subsetted data (split by one off and multigenerational exposure)

```{r, include = FALSE}
#ALL OF and MG

Body_Weight_lnCVR_0mods <- rma.mv(yi, vi, random = list(~1|Paper_ID,~1|Cohort_ID), data=Body_Weight_lnCVR, method = 'REML')

summary(Body_Weight_lnCVR_0mods)

#Tibble of overall results

Body_Weight_overall_lnCVR <- tibble(
  ID = "Overall", 
  lnCVR = 0.0817,
  ci.lb = -0.0331,
  ci.ub = 0.1964
)

plot_BW_overall_lnCVR <- ggplot(Body_Weight_overall_lnCVR, aes(x=ID, y=lnCVR, colour=ID)) + 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3)) +
  geom_point(aes(x = ID, y = lnCVR), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(title ="Body Weight differences, overall lnCVR", x = "ID", y = "lnCVR") +
  coord_flip()
plot_BW_overall_lnCVR

W <- diag(1/Body_Weight_overall_lnCVR$vi)
X <- model.matrix(Body_Weight_lnCVR_0mods)
P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
I2_BW <- 100 * sum(Body_Weight_lnCVR_0mods$sigma2) / (sum(Body_Weight_lnCVR_0mods$sigma2) + (Body_Weight_lnCVR_0mods$k-Body_Weight_lnCVR_0mods$p)/sum(diag(P)))
I2_BW

```


```{r}

# Modelling all traits with no mods MG (lnCVR)
Body_Weight_lnCVR_0mods_MG <- rma.mv(yi, vi, random = list(~1|Paper_ID,~1|Cohort_ID), data=Body_Weight_lnCVR_MG, method = 'REML')


summary(Body_Weight_lnCVR_0mods_MG)

#Heterogeneity I2 (adapt for all models)
W <- diag(1/Body_Weight_lnCVR_MG$vi)
X <- model.matrix(Body_Weight_lnCVR_0mods_MG)
P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
I2_MG_lnCVR_BW <- 100 * sum(Body_Weight_lnCVR_0mods_MG$sigma2) / (sum(Body_Weight_lnCVR_0mods_MG$sigma2) + (Body_Weight_lnCVR_0mods_MG$k-Body_Weight_lnCVR_0mods_MG$p)/sum(diag(P)))
I2_MG_lnCVR_BW

# Modelling all traits with no mods OF (lnCVR)
Body_Weight_lnCVR_0mods_OF <- rma.mv(yi, vi, random = list(~1|Paper_ID,~1|Cohort_ID), data=Body_Weight_lnCVR_OF, method = 'REML')

summary(Body_Weight_lnCVR_0mods_OF)

#Tibble of results

Body_Weight_Exp_lnCVR <- tibble(
  Exposure_Type = c("Multigenerational", "One off"),
  lnCVR = c(0.1642,0.0175 ),
  ci.lb = c(0.0292,-0.1256 ),
  ci.ub = c(0.2993,0.1605 )
)

Body_Weight_Exp_lnCVR



#Plotting when split by exp type

plot_BW_exp_type_lnCVR <- ggplot(Body_Weight_Exp_lnCVR, aes(x=Exposure_Type, y=lnCVR, colour = Exposure_Type)) + 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3)) +
  geom_point(aes(x = Exposure_Type, y = lnCVR), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(title ="Body Weight differences, exp type_lnCVR", x = "Exp_Type", y = "lnCVR") +
  coord_flip()
plot_BW_exp_type_lnCVR


```
#### Running meta-analysis (Overall with moderators)

```{r, echo=FALSE}
#Adding moderators
BW_Exp_lnCVR <- rma.mv(yi, vi, mods = ~Exposure_Type-1, random = list(~1|Paper_ID,~1|Cohort_ID), data=Body_Weight_lnCVR, method = 'REML')

summary(BW_Exp_lnCVR)

BW_F0_lnCVR <- rma.mv(yi, vi, mods = ~F0_Parent_Exposed-1, random = list(~1|Paper_ID,~1|Cohort_ID), data=Body_Weight_lnCVR, method = 'REML')

summary(BW_F0_lnCVR)

BW_Sex_lnCVR <- rma.mv(yi, vi, mods = ~Sex-1, random = list(~1|Paper_ID,~1|Cohort_ID), data=Body_Weight_lnCVR, method = 'REML')

summary(BW_Sex_lnCVR)

#Tibble of results

Body_Weight_Mods_lnCVR <- tibble(
  ID = c("Multigenerational", "One off", "Both F0", "F0 Female", "F0 Male", "Both Sexes Grand Offspring", "Female Grand Offspring", "Male Grand Offspring"),
  lnCVR = c(BW_Exp_lnCVR$b[1], BW_Exp_lnCVR$b[2], BW_F0_lnCVR$b[1], BW_F0_lnCVR$b[2],BW_F0_lnCVR$b[3],BW_Sex_lnCVR$b[1],BW_Sex_lnCVR$b[2],BW_Sex_lnCVR$b[3]),
  ci.lb = c(BW_Exp_lnCVR$ci.lb[1], BW_Exp_lnCVR$ci.lb[2],BW_F0_lnCVR$ci.lb[1], BW_F0_lnCVR$ci.lb[2],BW_F0_lnCVR$ci.lb[3],BW_Sex_lnCVR$ci.lb[1],BW_Sex_lnCVR$ci.lb[2],BW_Sex_lnCVR$ci.lb[3]),
  ci.ub = c(BW_Exp_lnCVR$ci.ub[1], BW_Exp_lnCVR$ci.ub[2],BW_F0_lnCVR$ci.ub[1], BW_F0_lnCVR$ci.ub[2],BW_F0_lnCVR$ci.ub[3],BW_Sex_lnCVR$ci.ub[1],BW_Sex_lnCVR$ci.ub[2],BW_Sex_lnCVR$ci.ub[3])
)

Body_Weight_Mods_lnCVR

plot_BW_mods_lnCVR <- ggplot(Body_Weight_Mods_lnCVR, aes(x=ID, y=lnCVR )) + 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3), colour = "red") +
  geom_point(aes(x = ID, y = lnCVR), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(x = "ID", y = "lnCVR") +
  coord_flip()
plot_BW_mods_lnCVR
```

