---
title: "Glucose_Analysis"
author: "Hamza"
date: "2 October 2019"
output: html_document
---

## Meta-regression Glucose

```{r load packages, include=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(openxlsx)  
library(knitr)
library(metafor)
library(ggplot2)
library(readxl)
```

```{r}
Glucose_lnRR <- read.csv("../data/Glucose_lnRR.csv")

ALL_TRAITS <- read.xlsx("../data/ALL_TRAITS.xlsx") 

 
```


```{r}

#Subetting

Glucose_MG <- subset(Glucose_lnRR, Glucose_lnRR$Exposure_Type == "Multigenerational")

Glucose_OF <- subset(Glucose_lnRR, Glucose_lnRR$Exposure_Type == "One off")
```

```{r}

#Overall analysis, not split

Glucose_overall_lnRR <- rma.mv(yi, vi, random = list(~1|Paper_ID,~1|Cohort_ID), data=Glucose_lnRR, method = 'REML')

summary(Glucose_overall_lnRR)

#Tibble of overall results

Glucose_overall_lnRR <- tibble(
  ID = "Overall", 
  lnRR = 0.1025,
  ci.lb = 0.0138,
  ci.ub = 0.1911
)
```


```{r}

plot_Glucose_overall <- ggplot(Glucose_overall_lnRR, aes(x=ID, y=lnRR)) + 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3)) +
  geom_point(aes(x = ID, y = lnRR), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(title ="Glucose differences, overall", x = "ID", y = "lnRR") +
  coord_flip()
plot_Glucose_overall
```

```{r}

#MG then OF

Glucose_overall_MG <- rma.mv(yi, vi, random = list(~1|Paper_ID,~1|Cohort_ID), data=Glucose_MG, method = 'REML')

summary(Glucose_overall_MG)

Glucose_overall_OF <- rma.mv(yi, vi, random = list(~1|Paper_ID,~1|Cohort_ID), data=Glucose_OF, method = 'REML')

summary(Glucose_overall_OF)


#Tibble of results

Glucose_Exp_lnRR <- tibble(
  Exposure_Type = c("Multigenerational", "One off"),
  lnRR = c(0.2351, 0.0259),
  ci.lb = c(0.0738, -0.0440),
  ci.ub = c(0.3965, 0.0958)
)

Glucose_Exp_lnRR



#Plotting when split by exp type

plot_glucose_exp_type <- ggplot(Glucose_Exp_lnRR, aes(x=Exposure_Type, y=lnRR, colour = Exposure_Type)) + 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3)) +
  geom_point(aes(x = Exposure_Type, y = lnRR), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(title ="Glucose differences, exp type", x = "Exp_Type", y = "lnRR") +
  coord_flip()
plot_glucose_exp_type
```

#### Running meta-analysis (Overall with moderators, and then overall split by exposure type with moderators)

```{r, echo=FALSE}
#Adding moderators
Glucose_Exp_Type <- rma.mv(yi, vi, mods = ~Exposure_Type-1, random = list(~1|Paper_ID,~1|Cohort_ID), data=Glucose_lnRR, method = 'REML')

summary(Glucose_Exp_Type)

Glucose_F0 <- rma.mv(yi, vi, mods = ~F0_Parent_Exposed-1, random = list(~1|Paper_ID,~1|Cohort_ID), data=Glucose_lnRR, method = 'REML')

summary(Glucose_F0)

Glucose_Sex <- rma.mv(yi, vi, mods = ~Sex-1, random = list(~1|Paper_ID,~1|Cohort_ID), data=Glucose_lnRR, method = 'REML')

summary(Glucose_Sex)

Glucose_Test_Type <- rma.mv(yi, vi, mods = ~Trait_Info-1, random = list(~1|Paper_ID,~1|Cohort_ID), data=Glucose_lnRR, method = 'REML')

Glucose_Test_Type

#Tibble of results

Glucose_Mods_lnRR <- tibble(
  ID = c("Multigenerational", "One off", "F0 Female", "F0 Male", "Both Sexes Grand Offspring", "Female Grand Offspring", "Male Grand Offspring", "FBG", "GTT"),
  lnRR = c(Glucose_Exp_Type$b[1],Glucose_Exp_Type$b[2],Glucose_F0$b[1],Glucose_F0$b[2],Glucose_Sex$b[1],Glucose_Sex$b[2],Glucose_Sex$b[3],Glucose_Test_Type$b[1],Glucose_Test_Type$b[2]),
  ci.lb = c(Glucose_Exp_Type$ci.lb[1],Glucose_Exp_Type$ci.lb[2],Glucose_F0$ci.lb[1],Glucose_F0$ci.lb[2],Glucose_Sex$ci.lb[1],Glucose_Sex$ci.lb[2],Glucose_Sex$ci.lb[3],Glucose_Test_Type$ci.lb[1],Glucose_Test_Type$ci.lb[2]),
  ci.ub = c(Glucose_Exp_Type$ci.ub[1],Glucose_Exp_Type$ci.ub[2],Glucose_F0$ci.ub[1],Glucose_F0$ci.ub[2],Glucose_Sex$ci.ub[1],Glucose_Sex$ci.ub[2],Glucose_Sex$ci.ub[3],Glucose_Test_Type$ci.ub[1],Glucose_Test_Type$ci.ub[2])
)

plot_glucose_mods <- ggplot(Glucose_Mods_lnRR, aes(x=ID, y=lnRR)) + 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3)) +
  geom_point(aes(x = ID, y = lnRR), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(title ="Glucose differences, mods", x = "ID", y = "lnRR") +
  coord_flip()
plot_glucose_mods

```



## Meta-analysis overall results (lnCVR)

### 4. Calculating effect sizes (Done)

We calculated our effect sizes (lnCVR) for our complete data set (all traits).
```{r, include = FALSE}

Effect_Size_All_Traits_lnCVR <- escalc(measure="CVR", m1i=Mean_Treatment, sd1i=SD_Treatment, n1i=Sample_Size_n_Treatment, m2i=Mean_Control, sd2i=SD_Control, n2i=Sample_Size_n_Control, data=ALL_TRAITS)

#Converting into factors

Effect_Size_All_Traits_lnCVR$Trait <- factor(Effect_Size_All_Traits_lnCVR$Trait)
Effect_Size_All_Traits_lnCVR$Exposure_Type <- factor(Effect_Size_All_Traits_lnCVR$Exposure_Type)
Effect_Size_All_Traits_lnCVR$Sex <- factor(Effect_Size_All_Traits_lnCVR$Sex)
Effect_Size_All_Traits_lnCVR$Generation <- factor(Effect_Size_All_Traits_lnCVR$Generation)
Effect_Size_All_Traits_lnCVR$Cohort_ID <- factor(Effect_Size_All_Traits_lnCVR$Cohort_ID)
Effect_Size_All_Traits_lnCVR$Paper_ID <- factor(Effect_Size_All_Traits_lnCVR$Paper_ID)
Effect_Size_All_Traits_lnCVR$Rodent_type <- factor(Effect_Size_All_Traits_lnCVR$Rodent_type)
Effect_Size_All_Traits_lnCVR$F2_Diet_at_measurement <- factor(Effect_Size_All_Traits_lnCVR$F2_Diet_at_measurement)
Effect_Size_All_Traits_lnCVR$Strain <- factor(Effect_Size_All_Traits_lnCVR$Strain)
Effect_Size_All_Traits_lnCVR$F0_Parent_Exposed <- factor(Effect_Size_All_Traits_lnCVR$F0_Parent_Exposed)

#Subset Glucose Data
Glucose_lnCVR <- subset(Effect_Size_All_Traits_lnCVR, Effect_Size_All_Traits_lnCVR$Trait == "Glucose")



#Errors with spaces and converting back to factor
Glucose_lnCVR$Sex <- gsub("Both ", "Both", Glucose_lnCVR$Sex) 
Glucose_lnCVR$Sex <- as.factor(Glucose_lnCVR$Sex)



#Subetting into MG and OF



Glucose_lnCVR_MG <- subset(Glucose_lnCVR, Glucose_lnCVR$Exposure_Type == "Multigenerational")

Glucose_lnCVR_OF <- subset(Glucose_lnCVR, Glucose_lnCVR$Exposure_Type == "One off")

```

#### 5. Running meta-analysis for glucose lnCVR (overall, and then overall split by exposure type)
I conducted meta-analysis using lnCVR, first on the complete BW dataset, and then on subsetted data (split by one off and multigenerational exposure)

```{r, echo = FALSE}
#ALL OF and MG

Glucose_lnCVR_0mods <- rma.mv(yi, vi, random = list(~1|Paper_ID,~1|Cohort_ID), data=Glucose_lnCVR, method = 'REML')

summary(Glucose_lnCVR_0mods)

#Tibble of overall results

Glucose_overall_lnCVR <- tibble(
  ID = "Overall", 
  lnCVR = -0.0064,
  ci.lb = -0.1732,
  ci.ub = 0.1604
)

plot_glucose_overall_lnCVR <- ggplot(Glucose_overall_lnCVR, aes(x=ID, y=lnCVR)) + 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3)) +
  geom_point(aes(x = ID, y = lnCVR), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(title ="Glucose variance, overall lnCVR", x = "ID", y = "lnCVR") +
  coord_flip()
plot_glucose_overall_lnCVR

```


```{r}

# Modelling all traits with no mods MG (lnCVR)
Glucose_lnCVR_0mods_MG <- rma.mv(yi, vi, random = list(~1|Paper_ID,~1|Cohort_ID), data=Glucose_lnCVR_MG, method = 'REML')


summary(Glucose_lnCVR_0mods_MG)

# Modelling all traits with no mods OF (lnCVR)
Glucose_lnCVR_0mods_OF <- rma.mv(yi, vi, random = list(~1|Paper_ID,~1|Cohort_ID), data=Glucose_lnCVR_OF, method = 'REML')

summary(Glucose_lnCVR_0mods_OF)

#Tibble of results

Glucose_Exp_lnCVR <- tibble(
  Exposure_Type = c("Multigenerational", "One off"),
  lnCVR = c(-0.1799,0.1658 ),
  ci.lb = c(-0.3465,-0.0024 ),
  ci.ub = c(-0.0134,0.3340 )
)

Glucose_Exp_lnCVR



#Plotting when split by exp type

plot_glucose_exp_type_lnCVR <- ggplot(Glucose_Exp_lnCVR, aes(x=Exposure_Type, y=lnCVR, colour = Exposure_Type)) + 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3)) +
  geom_point(aes(x = Exposure_Type, y = lnCVR), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(title ="glucose variance, exp type", x = "Exp_Type", y = "lnCVR") +
  coord_flip()
plot_glucose_exp_type_lnCVR


```
#### Running meta-analysis (Overall with moderators)
```{r, echo=FALSE}
#Adding moderators
Glucose_Exp_lnCVR <- rma.mv(yi, vi, mods = ~Exposure_Type-1, random = list(~1|Paper_ID,~1|Cohort_ID), data=Glucose_lnCVR, method = 'REML')

summary(Glucose_Exp_lnCVR)

Glucose_F0_lnCVR <- rma.mv(yi, vi, mods = ~F0_Parent_Exposed-1, random = list(~1|Paper_ID,~1|Cohort_ID), data=Glucose_lnCVR, method = 'REML')

summary(Glucose_F0_lnCVR)

Glucose_Sex_lnCVR <- rma.mv(yi, vi, mods = ~Sex-1, random = list(~1|Paper_ID,~1|Cohort_ID), data=Glucose_lnCVR, method = 'REML')

summary(Glucose_Sex_lnCVR)

Glucose_Test_Type_lnCVR <- rma.mv(yi, vi, mods = ~Trait_Info-1, random = list(~1|Paper_ID,~1|Cohort_ID), data=Glucose_lnCVR, method = 'REML')

Glucose_Test_Type_lnCVR

#Tibble of results

Glucose_Mods_lnCVR <- tibble(
  ID = c("Multigenerational", "One off", "F0 Female", "F0 Male", "Both Sexes Grand Offspring", "Female Grand Offspring", "Male Grand Offspring", "FBG", "GTT"),
  lnCVR = c(Glucose_Exp_lnCVR$b[1],Glucose_Exp_lnCVR$b[2],Glucose_F0_lnCVR$b[1],Glucose_F0_lnCVR$b[2],Glucose_Sex_lnCVR$b[1],Glucose_Sex_lnCVR$b[2],Glucose_Sex_lnCVR$b[3],Glucose_Test_Type_lnCVR$b[1],Glucose_Test_Type_lnCVR$b[2]),
  ci.lb = c(Glucose_Exp_lnCVR$ci.lb[1],Glucose_Exp_lnCVR$ci.lb[2],Glucose_F0_lnCVR$ci.lb[1],Glucose_F0_lnCVR$ci.lb[2],Glucose_Sex_lnCVR$ci.lb[1],Glucose_Sex_lnCVR$ci.lb[2],Glucose_Sex_lnCVR$ci.lb[3],Glucose_Test_Type_lnCVR$ci.lb[1],Glucose_Test_Type_lnCVR$ci.lb[2]),
  ci.ub = c(Glucose_Exp_lnCVR$ci.ub[1],Glucose_Exp_lnCVR$ci.ub[2],Glucose_F0_lnCVR$ci.ub[1],Glucose_F0_lnCVR$ci.ub[2],Glucose_Sex_lnCVR$ci.ub[1],Glucose_Sex_lnCVR$ci.ub[2],Glucose_Sex_lnCVR$ci.ub[3],Glucose_Test_Type_lnCVR$ci.ub[1],Glucose_Test_Type_lnCVR$ci.ub[2])
)

plot_glucose_mods_lnCVR <- ggplot(Glucose_Mods_lnCVR, aes(x=ID, y=lnCVR)) + 
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3)) +
  geom_point(aes(x = ID, y = lnCVR), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(title ="Glucose differences, mods", x = "ID", y = "lnCVR") +
  coord_flip()
plot_glucose_mods_lnCVR

```
