---
title: "STEP2_MAIN_MODELS"
subtitle: "MA of transgenerational effects of obesogenic diets on rodents"
author: "ML"
date: "01/05/2020"
output: html_document
knit: (function(inputFile, encoding) {rmarkdown::render(inputFile, encoding = encoding, output_dir = "Knitted") })
---

Main analysis models     
[Note: run by chunks, do not knit]     

### Setup    
```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(scipen=100)

# Load packages
# devtools::install_github("thomasp85/patchwork")
pacman::p_load(tidyverse, # tidy family and related pacakges below
               metafor, # calculating effect sizes
               magrittr, # extending piping
               ggplot2,  # nice plots
               patchwork,  # arranging plots
               bbmle, # for AICtab
               here, # help loading and saving
)

#Load environment

#load(here('myEnvironment.RData'))

# Load custom functions
source("../Scripts/custom_functions.R") #load custom functions
```

### Load data     
Processed data for analyses is stored in data_all_ES.csv and data_all_ES.RData fils.    
It needs to be split into One-off and Multigenerational data.      

```{r load and subset data, include = FALSE}
# Load preprocessed data with effect sizes
data_all <- read.csv(file =here("Data", "data_all_ES.csv"))
#load(data_all, file = "./Rdata/data_all_ES.RData") #alternative
#str(data_all)

# Subset by One off and Multigenerational
data_MG <- filter(data_all, Exposure_Type == "Multigenerational")
data_OF <- filter(data_all, Exposure_Type == "One-off")
dim(data_MG)
dim(data_OF)
data_MG <- droplevels(data_MG) #adjust factor levels
data_OF <- droplevels(data_OF) #adjust factor levels
```

Make VCV (variance-covariance matices    

```{r make VCV matrices, include = FALSE}
## all data
Vmat_lnRR_all <- make_VCV_matrix(data = data_all, V = "VlnRR", cluster = "Cohort_ID_Control", obs = "ES_ID")
Vmat_lnCVR_all <- make_VCV_matrix(data = data_all, V = "VlnCVR", cluster = "Cohort_ID_Control", obs = "ES_ID")

## OF data
Vmat_lnRR_OF <- make_VCV_matrix(data = data_OF, V = "VlnRR", cluster = "Cohort_ID_Control", obs = "ES_ID")
Vmat_lnCVR_OF <- make_VCV_matrix(data = data_OF, V = "VlnCVR", cluster = "Cohort_ID_Control", obs = "ES_ID")

## MG data
Vmat_lnRR_MG <- make_VCV_matrix(data = data_MG, V = "VlnRR", cluster = "Cohort_ID_Control", obs = "ES_ID")
Vmat_lnCVR_MG <- make_VCV_matrix(data = data_MG, V = "VlnCVR", cluster = "Cohort_ID_Control", obs = "ES_ID")

#Vmat_lnRR_all #visual check
```


```{r select random factors, include = FALSE}

## OF dataset

MA_0 <- rma.mv(lnRR, VlnRR, data = data_OF, method = 'ML') 
MA_1 <- rma.mv(lnRR, VlnRR, random = list(~1|Paper_ID, ~1|ES_ID), data = data_OF, method = 'ML') 
anova(MA_0, MA_1) #simple comparison of two  models
MA_2 <- rma.mv(lnRR, VlnRR, random = list(~1|Paper_ID, ~1|Cohort_ID, ~1|ES_ID), data = data_OF, method = 'ML') 
MA_3 <- rma.mv(lnRR, VlnRR, random = list(~1|Paper_ID, ~1|Cohort_ID, ~1|Trait, ~1|ES_ID), data = data_OF, method = 'ML') 
MA_4 <- rma.mv(lnRR, VlnRR, random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_OF, method = 'ML') 
MA_4_Vmat <- rma.mv(lnRR, Vmat_lnRR_OF, random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_OF, method = 'ML') #with VCV matrix
MA_5_Vmat <- rma.mv(lnRR, Vmat_lnRR_OF, random = list(~1|Rodent_Strain, ~1|Study_ID, ~1|Cohort_ID, ~1|Trait, ~1|ES_ID), data = data_OF, method = 'ML') #with VCV matrix and Rodent_Strain
MA_6_Vmat <- rma.mv(lnRR, Vmat_lnRR_OF, random = list(~1|Rodent_Type, ~1|Study_ID, ~1|Cohort_ID, ~1|Trait, ~1|ES_ID), data = data_OF, method = 'ML') #with VCV matrix and Rodent_Type
MA_7_Vmat <- rma.mv(lnRR, Vmat_lnRR_OF, random = list(~1|Rodent_Type, ~1|Rodent_Strain, ~1|Study_ID, ~1|Cohort_ID, ~1|Trait, ~1|ES_ID), data = data_OF, method = 'ML') #with VCV matrix and Rodent_Type and Rodent_Strain
MA_8_Vmat <- rma.mv(lnRR, Vmat_lnRR_OF, random = list(~1|Rodent_Type, ~1|Rodent_Strain, ~1|Study_ID, ~1|Trait, ~1|ES_ID), data = data_OF, method = 'ML') #with VCV matrix and Rodent_Type and Rodent_Strain, without Cohort_ID
MA_9_Vmat <- rma.mv(lnRR, Vmat_lnRR_OF, random = list(~1|Rodent_Strain, ~1|Study_ID, ~1|Trait, ~1|ES_ID), data = data_OF, method = 'ML') #with VCV matrix and Rodent_Strain, without Cohort_ID and Rodent_Type 
MA_10_Vmat <- rma.mv(lnRR, Vmat_lnRR_OF, random = list(~1|Rodent_Type, ~1|Study_ID, ~1|Trait, ~1|ES_ID), data = data_OF, method = 'ML') #with VCV matrix and Rodent_Strain, without Cohort_ID and Rodent_Strain

#compare models using AIC:
AICtab(MA_0, MA_1, MA_2, MA_3, MA_4, MA_4_Vmat, MA_5_Vmat, MA_6_Vmat, MA_7_Vmat, MA_8_Vmat, MA_9_Vmat, MA_10_Vmat) #MA_9_Vmat best, MA_5_Vmat and MA_8_Vmat very similar


## MG dataset

MA_0 <- rma.mv(lnRR, VlnRR, data = data_MG, method = 'ML') 
MA_1 <- rma.mv(lnRR, VlnRR, random = list(~1|Paper_ID, ~1|ES_ID), data = data_MG, method = 'ML') 
anova(MA_0, MA_1) #simple comparison of two  models
MA_2 <- rma.mv(lnRR, VlnRR, random = list(~1|Paper_ID, ~1|Cohort_ID, ~1|ES_ID), data = data_MG, method = 'ML') 
MA_3 <- rma.mv(lnRR, VlnRR, random = list(~1|Paper_ID, ~1|Cohort_ID, ~1|Trait, ~1|ES_ID), data = data_MG, method = 'ML') 
MA_4 <- rma.mv(lnRR, VlnRR, random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_MG, method = 'ML') 
MA_4_Vmat <- rma.mv(lnRR, Vmat_lnRR_MG, random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_MG, method = 'ML')#with VCV matrix
MA_5_Vmat <- rma.mv(lnRR, Vmat_lnRR_MG, random = list(~1|Rodent_Strain, ~1|Study_ID, ~1|Cohort_ID, ~1|Trait, ~1|ES_ID), data = data_MG, method = 'ML') #with VCV matrix and Rodent_Strain
MA_6_Vmat <- rma.mv(lnRR, Vmat_lnRR_MG, random = list(~1|Rodent_Type, ~1|Study_ID, ~1|Cohort_ID, ~1|Trait, ~1|ES_ID), data = data_MG, method = 'ML') #with VCV matrix and Rodent_Type
MA_7_Vmat <- rma.mv(lnRR, Vmat_lnRR_MG, random = list(~1|Rodent_Type, ~1|Rodent_Strain, ~1|Study_ID, ~1|Cohort_ID, ~1|Trait, ~1|ES_ID), data = data_MG, method = 'ML') #with VCV matrix and Rodent_Type and Rodent_Strain
MA_8_Vmat <- rma.mv(lnRR, Vmat_lnRR_MG, random = list(~1|Rodent_Type, ~1|Rodent_Strain, ~1|Study_ID, ~1|Trait, ~1|ES_ID), data = data_MG, method = 'ML') #with VCV matrix and Rodent_Type and Rodent_Strain, without Cohort_ID
MA_9_Vmat <- rma.mv(lnRR, Vmat_lnRR_MG, random = list(~1|Rodent_Strain, ~1|Study_ID, ~1|Trait, ~1|ES_ID), data = data_MG, method = 'ML') #with VCV matrix and Rodent_Strain, without Cohort_ID and Rodent_Type 
MA_10_Vmat <- rma.mv(lnRR, Vmat_lnRR_MG, random = list(~1|Rodent_Type, ~1|Study_ID, ~1|Trait, ~1|ES_ID), data = data_MG, method = 'ML') #with VCV matrix and Rodent_Strain, without Cohort_ID and Rodent_Strain
#compare models using AIC:
AICtab(MA_0, MA_1, MA_2, MA_3, MA_4, MA_4_Vmat, MA_5_Vmat, MA_6_Vmat, MA_7_Vmat, MA_8_Vmat, MA_9_Vmat, MA_10_Vmat) #MA_9_Vmat and MA_10_Vmat and MA_4_Vmat best, but MA_5_Vmat and MA_6_Vmat and MA_8_Vmat very similar




#use: random = list(~1|Rodent_Strain, ~1|Study_ID, ~1|Trait, ~1|ES_ID) #MA_9_Vmat
```


## Main analyses     

### Meta-analytic models (intercept-only)    

Moedels run for lnRR and lnCVR effect sizes for OF and MG datasets separately      

```{r MA main, include = TRUE}
## OF data - lnRR random-effect model with VCV
MA_OF_lnRR <- rma.mv(lnRR, Vmat_lnRR_OF, random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_OF, method = "REML") 
summary(MA_OF_lnRR)    
I2(MA_OF_lnRR, method = "S")
save(MA_OF_lnRR, file = here("Rdata/MA_OF_lnRR.Rdata"))

## OF data - lnCVR random-effect model with VCV
MA_OF_lnCVR <- rma.mv(lnCVR, Vmat_lnCVR_OF, random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_OF, method = "REML") 
summary(MA_OF_lnCVR)    
I2(MA_OF_lnCVR, method = "S")
save(MA_OF_lnCVR, file = here("Rdata/MA_OF_lnCVR.Rdata"))

## MG data - lnRR random-effect model with VCV
MA_MG_lnRR <- rma.mv(lnRR, Vmat_lnRR_MG, random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_MG, method = "REML") 
summary(MA_MG_lnRR)    
I2(MA_MG_lnRR, method = "S")
save(MA_MG_lnRR, file = here("Rdata/MA_MG_lnRR.Rdata"))

## MG data - lnCvR random-effect model with VCV
MA_MG_lnCVR <- rma.mv(lnCVR, Vmat_lnCVR_MG, random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_MG, method = "REML") 
summary(MA_MG_lnCVR)    
I2(MA_MG_lnCVR, method = "S")
save(MA_MG_lnCVR, file = here("Rdata/MA_MG_lnCVR.Rdata"))
```


### Meta-regression model on all data with Exposure_type (comapere MA intercepts)  

```{r MR exposre type all data, include = TRUE, warning = FALSE}
## lnRR
MR_all_ExpT_lnRR <- rma.mv(lnRR, Vmat_lnRR_all, mods= ~Exposure_Type, random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_all, method = "REML") 
summary(MR_all_ExpT_lnRR)    
save(MR_all_ExpT_lnRR, file = "../Rdata/MR_all_ExpT_lnRR.Rdata")

## lnRR - intercepts
MR_all_ExpT_lnRRi <- rma.mv(lnRR, Vmat_lnRR_all, mods= ~Exposure_Type - 1, random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_all, method = "REML") 
summary(MR_all_ExpT_lnRRi)    
save(MR_all_ExpT_lnRRi, file = "../Rdata/MR_all_ExpT_lnRRi.Rdata")

R2(MR_all_ExpT_lnRR)

## lnCVR
MR_all_ExpT_lnCVR <- rma.mv(lnCVR, Vmat_lnCVR_all, mods= ~Exposure_Type, random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_all, method = "REML") 
summary(MR_all_ExpT_lnCVR)    
save(MR_all_ExpT_lnCVR, file = "../Rdata/MR_all_ExpT_lnCVR.Rdata")

## lnCVR - intercepts
MR_all_ExpT_lnCVRi <- rma.mv(lnCVR, Vmat_lnCVR_all, mods= ~Exposure_Type - 1, random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_all, method = "REML") 
summary(MR_all_ExpT_lnCVRi)    
save(MR_all_ExpT_lnCVRi, file = "../Rdata/MR_all_ExpT_lnCVRi.Rdata")

R2(MR_all_ExpT_lnCVR)

#funnel(MR_all_ExpT_lnRR, yaxis="seinv")
#funnel(MR_all_ExpT_lnCVR, yaxis="seinv")
#data_all %>% group_by(Exposure_Type) %>% count()
```

### Meta-regression model on OF and MG data with rodent type as moderator
```{r}
## OF lnRR - intercepts (both, rat and mouse)
MR_OF_Rodent_lnRRi <- rma.mv(lnRR, Vmat_lnRR_OF, mods= ~Rodent_Type - 1, random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_OF, method = "REML") 
summary(MR_OF_Rodent_lnRRi)    
save(MR_OF_Rodent_lnRRi, file = here("Rdata/MR_OF_Rodent_lnRRi.Rdata"))

## OF lnRR - ref mouse
MR_OF_Rodent_lnRRm <- rma.mv(lnRR, Vmat_lnRR_OF, mods= ~Rodent_Type, random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_OF, method = "REML") 
summary(MR_OF_Rodent_lnRRm)  

save(MR_OF_Rodent_lnRRm, file = here("Rdata/MR_OF_Rodent_lnRRm.Rdata"))

R2(MR_OF_Rodent_lnRRi)

## OF lnCVR - intercepts (both, rat and mouse)
MR_OF_Rodent_lnCVRi <- rma.mv(lnCVR, Vmat_lnCVR_OF, mods= ~Rodent_Type - 1, random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_OF, method = "REML") 
summary(MR_OF_Rodent_lnCVRi)    
save(MR_OF_Rodent_lnCVRi, file = here("Rdata/MR_OF_Rodent_lnCVRi.Rdata"))

## OF lnCVR - ref mouse
MR_OF_Rodent_lnCVRm <- rma.mv(lnCVR, Vmat_lnCVR_OF, mods= ~Rodent_Type, random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_OF, method = "REML") 
summary(MR_OF_Rodent_lnCVRm)    
save(MR_OF_Rodent_lnCVRm, file = here("Rdata/MR_OF_Rodent_lnCVRm.Rdata"))

R2(MR_OF_Rodent_lnCVRi)

## MG lnRR - intercepts (Rat, Mouse)
MR_MG_Rodent_lnRRi <- rma.mv(lnRR, Vmat_lnRR_MG, mods= ~Rodent_Type - 1, random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_MG, method = "REML") 
summary(MR_MG_Rodent_lnRRi)    
save(MR_MG_Rodent_lnRRi, file = here("Rdata/MR_MG_Rodent_lnRRi.Rdata"))

## MG lnRR - ref mouse
MR_MG_Rodent_lnRRm <- rma.mv(lnRR, Vmat_lnRR_MG, mods= ~Rodent_Type, random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_MG, method = "REML") 
summary(MR_MG_Rodent_lnRRm)    
save(MR_MG_Rodent_lnRRm, file = here("Rdata/MR_MG_Rodent_lnRRm.Rdata"))

R2(MR_MG_Rodent_lnRRi)


## MG lnCVR - intercepts (Rat, Mouse)
MR_MG_Rodent_lnCVRi <- rma.mv(lnCVR, Vmat_lnCVR_MG, mods= ~Rodent_Type - 1, random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_MG, method = "REML") 
summary(MR_MG_Rodent_lnCVRi)    
save(MR_MG_Rodent_lnCVRi, file = here("Rdata/MR_MG_Rodent_lnCVRi.Rdata"))

## MG lnCVR - ref mouse
MR_MG_Rodent_lnCVRm <- rma.mv(lnCVR, Vmat_lnCVR_MG, mods= ~Rodent_Type, random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_MG, method = "REML") 
summary(MR_MG_Rodent_lnCVRm)    
save(MR_MG_Rodent_lnCVRm, file = here("Rdata/MR_MG_Rodent_lnCVRm.Rdata"))

R2(MR_MG_Rodent_lnCVRi)
```

### Meta-regression model on OF and MG data with exposed F0 sex as moderator

#CHANGE relevel function add factor() in front ! Se below

```{r MR F0_Parent_Exposed, include = TRUE, warning = FALSE}

## OF lnRR - intercepts (both, female, male)
MR_OF_ExpSex_lnRRi <- rma.mv(lnRR, Vmat_lnRR_OF, mods= ~F0_Parent_Exposed - 1, random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_OF, method = "REML") 
summary(MR_OF_ExpSex_lnRRi)    
save(MR_OF_ExpSex_lnRRi, file = "../Rdata/MR_OF_ExpSex_lnRRi.Rdata")

## OF lnRR - ref female
MR_OF_ExpSex_lnRRf <- rma.mv(lnRR, Vmat_lnRR_OF, mods= ~relevel(factor(data_OF$F0_Parent_Exposed), ref="Female"), random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_OF, method = "REML") #Adding factor() !!!
summary(MR_OF_ExpSex_lnRRf)    
save(MR_OF_ExpSex_lnRRf, file = "../Rdata/MR_OF_ExpSex_lnRRf.Rdata")

## OF lnRR - ref male
MR_OF_ExpSex_lnRRm <- rma.mv(lnRR, Vmat_lnRR_OF, mods= ~relevel(data_OF$F0_Parent_Exposed, ref="Male"), random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_OF, method = "REML") 
summary(MR_OF_ExpSex_lnRRm)    
save(MR_OF_ExpSex_lnRRm, file = "../Rdata/MR_OF_ExpSex_lnRRm.Rdata")

R2(MR_OF_ExpSex_lnRRi)


## OF lnCVR - intercepts (both, female, male)
MR_OF_ExpSex_lnCVRi <- rma.mv(lnCVR, Vmat_lnCVR_OF, mods= ~F0_Parent_Exposed - 1, random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_OF, method = "REML") 
summary(MR_OF_ExpSex_lnCVRi)    
save(MR_OF_ExpSex_lnCVRi, file = "../Rdata/MR_OF_ExpSex_lnCVRi.Rdata")

## OF lnCVR - ref female
MR_OF_ExpSex_lnCVRf <- rma.mv(lnCVR, Vmat_lnCVR_OF, mods= ~relevel(data_OF$F0_Parent_Exposed, ref="Female"), random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_OF, method = "REML") 
summary(MR_OF_ExpSex_lnCVRf)    
save(MR_OF_ExpSex_lnCVRf, file = "../Rdata/MR_OF_ExpSex_lnCVRf.Rdata")

## OF lnCVR - ref male
MR_OF_ExpSex_lnCVRm <- rma.mv(lnCVR, Vmat_lnCVR_OF, mods= ~relevel(data_OF$F0_Parent_Exposed, ref="Male"), random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_OF, method = "REML") 
summary(MR_OF_ExpSex_lnCVRm)    
save(MR_OF_ExpSex_lnCVRm, file = "../Rdata/MR_OF_ExpSex_lnCVRm.Rdata")

R2(MR_OF_ExpSex_lnCVRi)


## MG lnRR - intercepts (female, male)
MR_MG_ExpSex_lnRRi <- rma.mv(lnRR, Vmat_lnRR_MG, mods= ~F0_Parent_Exposed - 1, random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_MG, method = "REML") 
summary(MR_MG_ExpSex_lnRRi)    
save(MR_MG_ExpSex_lnRRi, file = "../Rdata/MR_MG_ExpSex_lnRRi.Rdata")

## MG lnRR - ref female
MR_MG_ExpSex_lnRRf <- rma.mv(lnRR, Vmat_lnRR_MG, mods= ~relevel(data_MG$F0_Parent_Exposed, ref="Female"), random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_MG, method = "REML") 
summary(MR_MG_ExpSex_lnRRf)    
save(MR_MG_ExpSex_lnRRf, file = "../Rdata/MR_MG_ExpSex_lnRRf.Rdata")

R2(MR_MG_ExpSex_lnRRi)


## MG lnCVR - intercepts (female, male)
MR_MG_ExpSex_lnCVRi <- rma.mv(lnCVR, Vmat_lnCVR_MG, mods= ~F0_Parent_Exposed - 1, random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_MG, method = "REML") 
summary(MR_MG_ExpSex_lnCVRi)    
save(MR_MG_ExpSex_lnCVRi, file = "../Rdata/MR_MG_ExpSex_lnCVRi.Rdata")

## MG lnCVR - ref female
MR_MG_ExpSex_lnCVRf <- rma.mv(lnCVR, Vmat_lnCVR_MG, mods= ~relevel(data_MG$F0_Parent_Exposed, ref="Female"), random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_MG, method = "REML") 
summary(MR_MG_ExpSex_lnCVRf)    
save(MR_MG_ExpSex_lnCVRf, file = "../Rdata/MR_MG_ExpSex_lnCVRf.Rdata")

R2(MR_MG_ExpSex_lnCVRi)
```


### Meta-regression model on OF and MG data with offspring sex (F2, F3) as moderator

```{r MR Offspring_Sex, include = TRUE, warning = FALSE}

## OF lnRR - intercepts (both, female, male)
MR_OF_OffSex_lnRRi <- rma.mv(lnRR, Vmat_lnRR_OF, mods= ~Offspring_Sex - 1, random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_OF, method = "REML") 
summary(MR_OF_OffSex_lnRRi)    
save(MR_OF_OffSex_lnRRi, file = "../Rdata/MR_OF_OffSex_lnRRi.Rdata")

## OF lnRR - ref female
MR_OF_OffSex_lnRRf <- rma.mv(lnRR, Vmat_lnRR_OF, mods= ~relevel(data_OF$Offspring_Sex, ref="Female"), random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_OF, method = "REML") 
summary(MR_OF_OffSex_lnRRf)    
save(MR_OF_OffSex_lnRRf, file = "../Rdata/MR_OF_OffSex_lnRRf.Rdata")

## OF lnRR - ref male
MR_OF_OffSex_lnRRm <- rma.mv(lnRR, Vmat_lnRR_OF, mods= ~relevel(data_OF$Offspring_Sex, ref="Male"), random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_OF, method = "REML") 
summary(MR_OF_OffSex_lnRRm)    
save(MR_OF_OffSex_lnRRm, file = "../Rdata/MR_OF_OffSex_lnRRm.Rdata")

R2(MR_OF_OffSex_lnRRi)


## OF lnCVR - intercepts (both, female, male)
MR_OF_OffSex_lnCVRi <- rma.mv(lnCVR, Vmat_lnCVR_OF, mods= ~Offspring_Sex - 1, random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_OF, method = "REML") 
summary(MR_OF_OffSex_lnCVRi)    
save(MR_OF_OffSex_lnCVRi, file = "../Rdata/MR_OF_OffSex_lnCVRi.Rdata")

## OF lnCVR - ref female
MR_OF_OffSex_lnCVRf <- rma.mv(lnCVR, Vmat_lnCVR_OF, mods= ~relevel(data_OF$Offspring_Sex, ref="Female"), random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_OF, method = "REML") 
summary(MR_OF_OffSex_lnCVRf)    
save(MR_OF_OffSex_lnCVRf, file = "../Rdata/MR_OF_OffSex_lnCVRf.Rdata")

## OF lnCVR - ref male
MR_OF_OffSex_lnCVRm <- rma.mv(lnCVR, Vmat_lnCVR_OF, mods= ~relevel(data_OF$Offspring_Sex, ref="Male"), random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_OF, method = "REML") 
summary(MR_OF_OffSex_lnCVRm)    
save(MR_OF_OffSex_lnCVRm, file = "../Rdata/MR_OF_OffSex_lnCVRm.Rdata")

R2(MR_OF_OffSex_lnCVRi)


## MG lnRR - intercepts (both, female, male)
MR_MG_OffSex_lnRRi <- rma.mv(lnRR, Vmat_lnRR_MG, mods= ~Offspring_Sex - 1, random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_MG, method = "REML") 
summary(MR_MG_OffSex_lnRRi)    
save(MR_MG_OffSex_lnRRi, file = "../Rdata/MR_MG_OffSex_lnRRi.Rdata")

## MG lnRR - ref female
MR_MG_OffSex_lnRRf <- rma.mv(lnRR, Vmat_lnRR_MG, mods= ~relevel(data_MG$Offspring_Sex, ref="Female"), random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_MG, method = "REML") 
summary(MR_MG_OffSex_lnRRf)    
save(MR_MG_OffSex_lnRRf, file = "../Rdata/MR_MG_OffSex_lnRRf.Rdata")

## MG lnRR - ref male
MR_MG_OffSex_lnRRm <- rma.mv(lnRR, Vmat_lnRR_MG, mods= ~relevel(data_MG$Offspring_Sex, ref="Male"), random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_MG, method = "REML") 
summary(MR_MG_OffSex_lnRRm)    
save(MR_MG_OffSex_lnRRm, file = "../Rdata/MR_MG_OffSex_lnRRm.Rdata")

R2(MR_MG_OffSex_lnRRi)


## MG lnCVR - intercepts (female, male)
MR_MG_OffSex_lnCVRi <- rma.mv(lnCVR, Vmat_lnCVR_MG, mods= ~Offspring_Sex - 1, random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_MG, method = "REML") 
summary(MR_MG_OffSex_lnCVRi)    
save(MR_MG_OffSex_lnCVRi, file = "../Rdata/MR_MG_OffSex_lnCVRi.Rdata")

## MG lnCVR - ref female
MR_MG_OffSex_lnCVRf <- rma.mv(lnCVR, Vmat_lnCVR_MG, mods= ~relevel(data_MG$Offspring_Sex, ref="Female"), random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_MG, method = "REML") 
summary(MR_MG_OffSex_lnCVRf)    
save(MR_MG_OffSex_lnCVRf, file = "../Rdata/MR_MG_OffSex_lnCVRf.Rdata")

## MG lnCVR - ref male
MR_MG_OffSex_lnCVRm <- rma.mv(lnCVR, Vmat_lnCVR_MG, mods= ~relevel(data_MG$Offspring_Sex, ref="Male"), random = list(~1|Rodent_Strain, ~1|Study_ID,  ~1|Trait, ~1|ES_ID), data = data_MG, method = "REML") 
summary(MR_MG_OffSex_lnCVRm)    
save(MR_MG_OffSex_lnCVRm, file = "../Rdata/MR_MG_OffSex_lnCVRm.Rdata")

R2(MR_MG_OffSex_lnCVRi)
```


### Meta-regression model on OF and MG data with offspring Trait category as moderator

```{r MR Trait, include = TRUE, warning = FALSE}

## OF lnRR - intercepts (Adiposity, Body_Weight, Glucose_FBG, Glucose_TT, Insulin_FI, Insulin_TT, Leptin, Triglycerides)
MR_OF_Trait_lnRRi <- rma.mv(lnRR, Vmat_lnRR_OF, mods= ~Trait - 1, random = list(~1|Rodent_Strain, ~1|Study_ID, ~1|ES_ID), data = data_OF, method = "REML") 
summary(MR_OF_Trait_lnRRi)    
R2(MR_OF_Trait_lnRRi)
save(MR_OF_Trait_lnRRi, file = "../Rdata/MR_OF_Trait_lnRRi.Rdata")

#use a custom function compare_levels to relevel factor (Trait), update model and collect results:
MR_OF_Trait_lnRR_releveled <- compare_levels(MR_OF_Trait_lnRRi, data_OF$Trait)
save(MR_OF_Trait_lnRR_releveled, file = "../Rdata/MR_OF_Trait_lnRR_releveled.Rdata")
#str(MR_OF_Trait_lnRR_releveled)
#MR_OF_Trait_lnRR_releveled[["Leptin"]]
#filter(MR_OF_Trait_lnRR_releveled[["Leptin"]],names=="intrcpt")


# manual re-leveling example:
# ## OF lnRR - ref Adiposity
# MR_OF_Trait_lnRRa <- rma.mv(lnRR, Vmat_lnRR_OF, mods= ~relevel(data_OF$Trait, ref="Adiposity"), random = list(~1|Rodent_Strain, ~1|Study_ID, ~1|ES_ID), data = data_OF, method = "REML") 
# summary(MR_OF_Trait_lnRRa)    
# save(MR_OF_Trait_lnRRa, file = "./Rdata/MR_OF_Trait_lnRRa.Rdata")
# 
# ## OF lnRR - ref Body_Weight
# MR_OF_Trait_lnRRb <- rma.mv(lnRR, Vmat_lnRR_OF, mods= ~relevel(data_OF$Trait, ref="Body_Weight"), random = list(~1|Rodent_Strain, ~1|Study_ID, ~1|ES_ID), data = data_OF, method = "REML") 
# summary(MR_OF_Trait_lnRRb)    
# save(MR_OF_Trait_lnRRb, file = "./Rdata/MR_OF_Trait_lnRRb.Rdata")
# 
# ## OF lnRR - ref Glucose_FBG
# MR_OF_Trait_lnRRgf <- rma.mv(lnRR, Vmat_lnRR_OF, mods= ~relevel(data_OF$Trait, ref="Glucose_FBG"), random = list(~1|Rodent_Strain, ~1|Study_ID, ~1|ES_ID), data = data_OF, method = "REML") 
# summary(MR_OF_Trait_lnRRgf)    
# save(MR_OF_Trait_lnRRgf, file = "./Rdata/MR_OF_Trait_lnRRgf.Rdata")
# 
# ## OF lnRR - ref Glucose_TT
# MR_OF_Trait_lnRRgt <- rma.mv(lnRR, Vmat_lnRR_OF, mods= ~relevel(data_OF$Trait, ref="Glucose_TT"), random = list(~1|Rodent_Strain, ~1|Study_ID, ~1|ES_ID), data = data_OF, method = "REML") 
# summary(MR_OF_Trait_lnRRgt)    
# save(MR_OF_Trait_lnRRgt, file = "./Rdata/MR_OF_Trait_lnRRgt.Rdata")
# 
# ## OF lnRR - ref Insulin_FI
# MR_OF_Trait_lnRRif <- rma.mv(lnRR, Vmat_lnRR_OF, mods= ~relevel(data_OF$Trait, ref="Insulin_FI"), random = list(~1|Rodent_Strain, ~1|Study_ID, ~1|ES_ID), data = data_OF, method = "REML") 
# summary(MR_OF_Trait_lnRRif)    
# save(MR_OF_Trait_lnRRif, file = "./Rdata/MR_OF_Trait_lnRRif.Rdata")
# 
# ## OF lnRR - ref Insulin_TT
# MR_OF_Trait_lnRRit <- rma.mv(lnRR, Vmat_lnRR_OF, mods= ~relevel(data_OF$Trait, ref="Insulin_TT"), random = list(~1|Rodent_Strain, ~1|Study_ID, ~1|ES_ID), data = data_OF, method = "REML") 
# summary(MR_OF_Trait_lnRRit)    
# save(MR_OF_Trait_lnRRit, file = "./Rdata/MR_OF_Trait_lnRRit.Rdata")
# 
# ## OF lnRR - ref Leptin
# MR_OF_Trait_lnRRl <- rma.mv(lnRR, Vmat_lnRR_OF, mods= ~relevel(data_OF$Trait, ref="Leptin"), random = list(~1|Rodent_Strain, ~1|Study_ID, ~1|ES_ID), data = data_OF, method = "REML") 
# summary(MR_OF_Trait_lnRRl)    
# save(MR_OF_Trait_lnRRl, file = "./Rdata/MR_OF_Trait_lnRRl.Rdata")
 



## OF lnCVR - intercepts (Adiposity, Body_Weight, Glucose_FBG, Glucose_TT, Insulin_FI, Insulin_TT, Leptin, Triglycerides)
MR_OF_Trait_lnCVRi <- rma.mv(lnCVR, Vmat_lnCVR_OF, mods= ~Trait - 1, random = list(~1|Rodent_Strain, ~1|Study_ID, ~1|ES_ID), data = data_OF, method = "REML") 
summary(MR_OF_Trait_lnCVRi)    
R2(MR_OF_Trait_lnCVRi)
save(MR_OF_Trait_lnCVRi, file = "../Rdata/MR_OF_Trait_lnCVRi.Rdata")

#use a custom function compare_levels to relevel factor (Trait), update model and collect results:
MR_OF_Trait_lnCVR_releveled <- compare_levels(MR_OF_Trait_lnCVRi, data_OF$Trait)
save(MR_OF_Trait_lnCVR_releveled, file = "../Rdata/MR_OF_Trait_lnCVR_releveled.Rdata")



## MG lnRR - intercepts (Adiposity, Body_Weight, Glucose_FBG, Glucose_TT, Insulin_FI, Insulin_TT, Leptin, Triglycerides)
MR_MG_Trait_lnRRi <- rma.mv(lnRR, Vmat_lnRR_MG, mods= ~Trait - 1, random = list(~1|Rodent_Strain, ~1|Study_ID, ~1|ES_ID), data = data_MG, method = "REML") 
summary(MR_MG_Trait_lnRRi)    
R2(MR_MG_Trait_lnRRi)
save(MR_MG_Trait_lnRRi, file = "../Rdata/MR_MG_Trait_lnRRi.Rdata")

#use a custom function compare_levels to relevel factor (Trait), update model and collect results:
MR_MG_Trait_lnRR_releveled <- compare_levels(MR_MG_Trait_lnRRi, data_MG$Trait)
save(MR_MG_Trait_lnRR_releveled, file = "../Rdata/MR_MG_Trait_lnRR_releveled.Rdata")


## MG lnCVR - intercepts (Adiposity, Body_Weight, Glucose_FBG, Glucose_TT, Insulin_FI, Insulin_TT, Leptin, Triglycerides)
MR_MG_Trait_lnCVRi <- rma.mv(lnCVR, Vmat_lnCVR_MG, mods= ~Trait - 1, random = list(~1|Rodent_Strain, ~1|Study_ID, ~1|ES_ID), data = data_MG, method = "REML") 
summary(MR_MG_Trait_lnCVRi)    
R2(MR_MG_Trait_lnCVRi)
save(MR_MG_Trait_lnCVRi, file = "../Rdata/MR_MG_Trait_lnCVRi.Rdata")

#use a custom function compare_levels to relevel factor (Trait), update model and collect results:
MR_MG_Trait_lnCVR_releveled <- compare_levels(MR_MG_Trait_lnCVRi, data_MG$Trait)
save(MR_MG_Trait_lnCVR_releveled, file = "../Rdata/MR_MG_Trait_lnCVR_releveled.Rdata")
```




*NEXT: run main MA and MR using STEP3_EXTRA_MODELS.Rmd script* 
