---
title: "STEP5_TABLES"
subtitle: "MA of transgenerational effects of obesogenic diets on rodents"
author: "ML"
date: "01/05/2020"
output: html_document
knit: (function(inputFile, encoding) {rmarkdown::render(inputFile, encoding = encoding, output_dir = "Knitted") })
---

Create tables presenting results of statistical analyses in SI.
[Do not knit. New formatted tables are saved as .csv files in /Tables folder (.xlsx file is just a format template)]

```{r setup, include=FALSE}

options(scipen=100)

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE, # no warnings
  cache = TRUE,# Cacheing to save time when kniting
  tidy = TRUE
  #fig.width = 9
  )

#options(knitr.table.format = "latex") 
#fancy table on landscape page, etc: https://www.rdocumentation.org/packages/kableExtra/versions/0.5.2/vignettes/awesome_table_in_pdf.Rmd

# loading packages
# devtools::install_github("thomasp85/patchwork")
pacman::p_load(tidyverse, # tidy family and related pacakges below
               kableExtra, 
               grid,        # graphic layout manipulation
               #gridExtra, # may not use this
               purrr,
               magrittr, # extending piping
               pander,   # nice tables
               metafor,  # package for meta-analysis
               #MCMCglmm,  # Bayeisan mixed model package
               ggbeeswarm, # making bee-swarm plots possible
               #plotly,     # interactive plots using ggplot2
               #MuMIn,  # multi-model inference
               #lme4,   # lmm & glmm (models)
               #broom.mixed, # getting estimates from lmer + glmer objects
               #performance, # getting R2 from lmer + glmer objects
               png,         # reading png files
               patchwork,    # putting ggplots together - you need to install via devtool
               formatR, # provides a function tidy_source() to format R source automatically
               #lmerTest   # more functions for lme4
               #mi,      # missing data analysis
               #betareg   # dependance of the above
               metafor, 
               readxl
)

# Load custom functions
#source("./Scripts/custom_functions.R") #load custom functions
```

<!-- ### Load data     -->
<!-- Processed data for analyses is stored in data_all_ES.csv and data_all_ES.RData fils.  -->
<!-- It needs to be split into One-off and Multigenerational data.       -->

<!-- ```{r load and subset data, include = FALSE} -->

<!-- # Load preprocessed data with effect sizes -->
<!-- data_all <- read.csv(file ="../Data/data_all_ES.csv") -->
<!-- #load(data_all, file = "../Rdata/data_all_ES.RData") #alternative -->
<!-- #str(data_all) -->

<!-- # Subset by One off and Multigenerational -->
<!-- data_MG <- filter(data_all, Exposure_Type == "Multigenerational") -->
<!-- data_OF <- filter(data_all, Exposure_Type == "One-off") -->
<!-- dim(data_MG) -->
<!-- dim(data_OF) -->
<!-- data_MG <- droplevels(data_MG) #adjust factor levels -->
<!-- data_OF <- droplevels(data_OF) #adjust factor levels -->
<!-- ``` -->


## Supplementary Tables  

### Table S1        
Search keywords strings for the main database searches.    
[insert manually in Word - this is painfult o include in Rmarkdown due to multiple quatations and bracket symbols...]    

### Table S2      
List of excluded studies with main reasons for exclusion.   
[will be also inserted manually in Word ufter updating the search / otherwise first update csv file]  

UPDATE: TABLE HAS BEEN FORMATTED MANUALLY IN WORD, NO NEED TO RUN THIS CHUNK
```{r TableS2, include = FALSE, warnings = FALSE}
#for html use:
#read_csv("../Data/Excluded_fulltext_papers_list.csv", na = "NA", col_names = c("Ref_short",	"Title",	"Main_reason")) %>%  mutate_if(is.character, as.factor) %>%  kable("html") %>% kable_styling("striped", position = "left")
#%>% kable_as_image() #use for Word documents?

#for Word try:
# pander(read_csv("../Tables/Excluded_fulltext_papers_list.csv", na = "NA", col_names = c("Ref_short",	"Title",	 "Main_reason")), split.cells = c(10, 30, 10), justify = 'left')
```

### Table S3    
List of the main variables extracted from included studies, with descriptions.    
[insert manually in Word from existing file]     


### Table S4     
lnRR and lnCVR MA models for OF and MG datasets, with I2 values.

```{r Table MA}
#list.files("./Rdata/")

# # for TableS
# load(file = "./Rdata/MA_OF_lnRR.Rdata")
# load(file = "./Rdata/MA_OF_lnCVR.Rdata")
# load(file = "./Rdata/MA_MG_lnRR.Rdata")
# load(file = "./Rdata/MA_MG_lnCVR.Rdata")

# calculate I2 values for each MA:
MA_OF_lnRR_I2 <- I2(MA_OF_lnRR, method = "S")
MA_OF_lnCVR_I2 <- I2(MA_OF_lnCVR, method = "S")
MA_MG_lnRR_I2 <- I2(MA_MG_lnRR, method = "S")
MA_MG_lnCVR_I2 <- I2(MA_MG_lnCVR, method = "S")

t4 <- read_excel("../Tables/Results_Tables_templates.xlsx", sheet = "TableS4") # loading table template for updating MA results

pos <- c(3,9,15,21) # saving initial row position for each model

# adding results from the models to the table
t4$`Fixed effects`[pos] <- round(c(MA_OF_lnRR$b,
                                   MA_OF_lnCVR$b,
                                   MA_MG_lnRR$b,
                                   MA_MG_lnCVR$b), 3)

t4$...4[pos] <- round(c(MA_OF_lnRR$ci.lb,
                                   MA_OF_lnCVR$ci.lb,
                                   MA_MG_lnRR$ci.lb,
                                   MA_MG_lnCVR$ci.lb), 3)

t4$...5[pos] <- round(c(MA_OF_lnRR$ci.ub,
                                   MA_OF_lnCVR$ci.ub,
                                   MA_MG_lnRR$ci.ub,
                                   MA_MG_lnCVR$ci.ub), 3)

t4$...6[pos] <- round(c(MA_OF_lnRR$pval,
                                   MA_OF_lnCVR$pval,
                                   MA_MG_lnRR$pval,
                                   MA_MG_lnCVR$pval), 3)

t4$`Random effects`[pos] <- round(c(MA_OF_lnRR_I2[1]*100,
                                   MA_OF_lnCVR_I2[1]*100,
                                   MA_MG_lnRR_I2[1]*100,
                                   MA_MG_lnCVR_I2[1]*100), 1)

t4$`Random effects`[pos + 1] <- round(c(MA_OF_lnRR_I2[2]*100,
                                   MA_OF_lnCVR_I2[2]*100,
                                   MA_MG_lnRR_I2[2]*100,
                                   MA_MG_lnCVR_I2[2]*100), 1)

t4$`Random effects`[pos + 2] <- round(c(MA_OF_lnRR_I2[3]*100,
                                   MA_OF_lnCVR_I2[3]*100,
                                   MA_MG_lnRR_I2[3]*100,
                                   MA_MG_lnCVR_I2[3]*100), 1)

t4$`Random effects`[pos + 3] <- round(c(MA_OF_lnRR_I2[4]*100,
                                   MA_OF_lnCVR_I2[4]*100,
                                   MA_MG_lnRR_I2[4]*100,
                                   MA_MG_lnCVR_I2[4]*100), 1)

t4$`Random effects`[pos + 4] <- round(c(MA_OF_lnRR_I2[5]*100,
                                   MA_OF_lnCVR_I2[5]*100,
                                   MA_MG_lnRR_I2[5]*100,
                                   MA_MG_lnCVR_I2[5]*100), 1)

t4$`Random effects`[pos + 5] <- round(c(MA_OF_lnRR_I2[6]*100,
                                   MA_OF_lnCVR_I2[6]*100,
                                   MA_MG_lnRR_I2[6]*100,
                                   MA_MG_lnCVR_I2[6]*100), 1)

t4$...9[pos] <- round(c(MA_OF_lnRR$k.all,
                                   MA_OF_lnCVR$k.all,
                                   MA_MG_lnRR$k.all,
                                   MA_MG_lnCVR$k.all), 3)

t4$...9[pos+1] <- round(c(MA_OF_lnRR$s.nlevels[1],
                                   MA_OF_lnCVR$s.nlevels[1],
                                   MA_MG_lnRR$s.nlevels[1],
                                   MA_MG_lnCVR$s.nlevels[1]), 3)

t4$...9[pos+2] <- round(c(MA_OF_lnRR$s.nlevels[2],
                                   MA_OF_lnCVR$s.nlevels[2],
                                   MA_MG_lnRR$s.nlevels[2],
                                   MA_MG_lnCVR$s.nlevels[2]), 3)

t4$...9[pos+3] <- round(c(MA_OF_lnRR$s.nlevels[3],
                                   MA_OF_lnCVR$s.nlevels[3],
                                   MA_MG_lnRR$s.nlevels[3],
                                   MA_MG_lnCVR$s.nlevels[3]), 3)

t4$...9[pos+4] <- round(c(MA_OF_lnRR$s.nlevels[4],
                                   MA_OF_lnCVR$s.nlevels[4],
                                   MA_MG_lnRR$s.nlevels[4],
                                   MA_MG_lnCVR$s.nlevels[4]), 3)

write.csv(t4, file = "../Tables/Table_S4_MA.csv", row.names = F, na = "")
```


### Table S5    
lnRR and lnCVR MR models for OF and MG datasets merged, with exposure type as a moderator.   

```{r Table MR univ Exposure Type}
# #list.files("./Rdata/")
# load(file = "./Rdata/MR_all_ExpT_lnRRi.Rdata")
# load(file = "./Rdata/MR_all_ExpT_lnCVRi.Rdata")
# load(file = "./Rdata/MR_all_ExpT_lnRR.Rdata")
# load(file = "./Rdata/MR_all_ExpT_lnCVR.Rdata")

# loading empty table
t5 <- read_excel("../Tables/Results_Tables_templates.xlsx", sheet = 2)

# saving row position for estimates
pos <- c(2:4, 6:8)

t5$`Mean`[pos] <- round(c(
  MR_all_ExpT_lnRRi$b[2:1], 
  MR_all_ExpT_lnRR$b[2],
  MR_all_ExpT_lnCVRi$b[2:1], 
  MR_all_ExpT_lnCVR$b[2]), 3) 
  
t5$CI.lb[pos] <- round(c(
  MR_all_ExpT_lnRRi$ci.lb[2:1], 
  MR_all_ExpT_lnRR$ci.lb[2],
  MR_all_ExpT_lnCVRi$ci.lb[2:1], 
  MR_all_ExpT_lnCVR$ci.lb[2]), 3) 

t5$CI.ub[pos] <- round(c(
  MR_all_ExpT_lnRRi$ci.ub[2:1], 
  MR_all_ExpT_lnRR$ci.ub[2],
  MR_all_ExpT_lnCVRi$ci.ub[2:1], 
  MR_all_ExpT_lnCVR$ci.ub[2]), 3) 

t5$k[pos] <- c(
  rev(table(data_all$Exposure_Type)), 
  rep(NA, 1),
  rev(table(data_all$Exposure_Type)), 
  rep(NA, 1)
  ) 

# adding model R2 estimates to the table
posR2 <- c(1,5) #row positions
t5$`R2`[posR2] <- round(c(R2(MR_all_ExpT_lnRR)[1], R2(MR_all_ExpT_lnCVR)[1]),3)

write.csv(t5, file = "../Tables/Table_S5.csv", row.names = F, na = "")    
```


### Table S6    
lnRR and lnCVR MR models for OF and MG datasets, with sex of exposed F0 grandparents as a moderator.   

```{r Table MR univ F0 Sex}
#list.files("./Rdata/")
# load(file = "./Rdata/MR_OF_ExpSex_lnRRi.Rdata")
# load(file = "./Rdata/MR_OF_ExpSex_lnRRf.Rdata")
# load(file = "./Rdata/MR_OF_ExpSex_lnRRm.Rdata")
# load(file = "./Rdata/MR_OF_ExpSex_lnCVRi.Rdata")
# load(file = "./Rdata/MR_OF_ExpSex_lnCVRf.Rdata")
# load(file = "./Rdata/MR_OF_ExpSex_lnCVRm.Rdata")
# load(file = "./Rdata/MR_MG_ExpSex_lnRRi.Rdata")
# load(file = "./Rdata/MR_MG_ExpSex_lnRRf.Rdata")
# load(file = "./Rdata/MR_MG_ExpSex_lnCVRi.Rdata")
# load(file = "./Rdata/MR_MG_ExpSex_lnCVRf.Rdata")


# loading empty table
t6 <- read_excel("../Tables/Results_Tables_templates.xlsx", sheet = 3)

# saving row position for estimates
pos <- c(2:7, 9:14, 16:18, 20:22)

t6$`Mean`[pos] <- round(c(
  MR_OF_ExpSex_lnRRi$b[2:3], 
  MR_OF_ExpSex_lnRRi$b[1],
  MR_OF_ExpSex_lnRRf$b[3:2], 
  MR_OF_ExpSex_lnRRm$b[2],
  MR_OF_ExpSex_lnCVRi$b[2:3], 
  MR_OF_ExpSex_lnCVRi$b[1],
  MR_OF_ExpSex_lnCVRf$b[3:2], 
  MR_OF_ExpSex_lnCVRm$b[2],
  MR_MG_ExpSex_lnRRi$b[1:2], 
  MR_MG_ExpSex_lnRRf$b[2],
  MR_MG_ExpSex_lnCVRi$b[1:2], 
  MR_MG_ExpSex_lnCVRf$b[2]), 3) 
  
t6$CI.lb[pos] <- round(c(
  MR_OF_ExpSex_lnRRi$ci.lb[2:3], 
  MR_OF_ExpSex_lnRRi$ci.lb[1],
  MR_OF_ExpSex_lnRRf$ci.lb[3:2], 
  MR_OF_ExpSex_lnRRm$ci.lb[2],
  MR_OF_ExpSex_lnCVRi$ci.lb[2:3], 
  MR_OF_ExpSex_lnCVRi$ci.lb[1],
  MR_OF_ExpSex_lnCVRf$ci.lb[3:2], 
  MR_OF_ExpSex_lnCVRm$ci.lb[2],
  MR_MG_ExpSex_lnRRi$ci.lb[1:2], 
  MR_MG_ExpSex_lnRRf$ci.lb[2],
  MR_MG_ExpSex_lnCVRi$ci.lb[1:2], 
  MR_MG_ExpSex_lnCVRf$ci.lb[2]), 3) 

t6$CI.ub[pos] <- round(c(
  MR_OF_ExpSex_lnRRi$ci.ub[2:3], 
  MR_OF_ExpSex_lnRRi$ci.ub[1],
  MR_OF_ExpSex_lnRRf$ci.ub[3:2], 
  MR_OF_ExpSex_lnRRm$ci.ub[2],
  MR_OF_ExpSex_lnCVRi$ci.ub[2:3], 
  MR_OF_ExpSex_lnCVRi$ci.ub[1],
  MR_OF_ExpSex_lnCVRf$ci.ub[3:2], 
  MR_OF_ExpSex_lnCVRm$ci.ub[2],
  MR_MG_ExpSex_lnRRi$ci.ub[1:2], 
  MR_MG_ExpSex_lnRRf$ci.ub[2],
  MR_MG_ExpSex_lnCVRi$ci.ub[1:2], 
  MR_MG_ExpSex_lnCVRf$ci.ub[2]), 3) 

t6$k[pos] <- c(
  table(data_OF$F0_Parent_Exposed)[c(2,3,1)], 
  rep(NA, 3),
  table(data_OF$F0_Parent_Exposed)[c(2,3,1)], 
  rep(NA, 3),
  table(data_MG$F0_Parent_Exposed)[c(1,2)], 
  rep(NA, 1),
  table(data_MG$F0_Parent_Exposed)[c(1,2)], 
  rep(NA, 1)) 

# adding model R2 estimates to the table
posR2 <- c(1,8,15,19) #row positions
t6$`R2`[posR2] <- round(c(R2(MR_OF_ExpSex_lnRRi)[1], R2(MR_OF_ExpSex_lnCVRi)[1], R2(MR_MG_ExpSex_lnRRi)[1], R2(MR_MG_ExpSex_lnCVRi)[1]),3)

write.csv(t6, file = "../Tables/Table_S6.csv", row.names = F, na = "")    
```


## Table S7    
lnRR and lnCVR MR models for OF and MG datasets, with sex of measured grand-offspring as a moderator.   

```{r Table MR univ Offspr Sex}
# #list.files("./Rdata/")
# load(file = "./Rdata/MR_OF_OffSex_lnRRi.Rdata")
# load(file = "./Rdata/MR_OF_OffSex_lnRRf.Rdata")
# load(file = "./Rdata/MR_OF_OffSex_lnRRm.Rdata")
# load(file = "./Rdata/MR_OF_OffSex_lnCVRi.Rdata")
# load(file = "./Rdata/MR_OF_OffSex_lnCVRf.Rdata")
# load(file = "./Rdata/MR_OF_OffSex_lnCVRm.Rdata")
# load(file = "./Rdata/MR_MG_OffSex_lnRRi.Rdata")
# load(file = "./Rdata/MR_MG_OffSex_lnRRf.Rdata")
# load(file = "./Rdata/MR_MG_OffSex_lnRRm.Rdata")
# load(file = "./Rdata/MR_MG_OffSex_lnCVRi.Rdata")
# load(file = "./Rdata/MR_MG_OffSex_lnCVRf.Rdata")
# load(file = "./Rdata/MR_MG_OffSex_lnCVRm.Rdata")

# loading empty table
t7 <- read_excel("../Tables/Results_Tables_templates.xlsx", sheet = 4)

# saving row position for estimates
pos <- c(2:7, 9:14, 16:21, 23:28)

t7$`Mean`[pos] <- round(c(
  MR_OF_OffSex_lnRRi$b[2:3], 
  MR_OF_OffSex_lnRRi$b[1],
  MR_OF_OffSex_lnRRf$b[3:2], 
  MR_OF_OffSex_lnRRm$b[2],
  MR_OF_OffSex_lnCVRi$b[2:3], 
  MR_OF_OffSex_lnCVRi$b[1],
  MR_OF_OffSex_lnCVRf$b[3:2], 
  MR_OF_OffSex_lnCVRm$b[2],
  MR_MG_OffSex_lnRRi$b[2:3], 
  MR_MG_OffSex_lnRRi$b[1],
  MR_MG_OffSex_lnRRf$b[3:2], 
  MR_MG_OffSex_lnRRm$b[2],
  MR_MG_OffSex_lnCVRi$b[2:3], 
  MR_MG_OffSex_lnCVRi$b[1],
  MR_MG_OffSex_lnCVRf$b[3:2], 
  MR_MG_OffSex_lnCVRm$b[2]),3) 
  
t7$CI.lb[pos] <- round(c(
  MR_OF_OffSex_lnRRi$ci.lb[2:3], 
  MR_OF_OffSex_lnRRi$ci.lb[1],
  MR_OF_OffSex_lnRRf$ci.lb[3:2], 
  MR_OF_OffSex_lnRRm$ci.lb[2],
  MR_OF_OffSex_lnCVRi$ci.lb[2:3], 
  MR_OF_OffSex_lnCVRi$ci.lb[1],
  MR_OF_OffSex_lnCVRf$ci.lb[3:2], 
  MR_OF_OffSex_lnCVRm$ci.lb[2],
  MR_MG_OffSex_lnRRi$ci.lb[2:3], 
  MR_MG_OffSex_lnRRi$ci.lb[1],
  MR_MG_OffSex_lnRRf$ci.lb[3:2], 
  MR_MG_OffSex_lnRRm$ci.lb[2],
  MR_MG_OffSex_lnCVRi$ci.lb[2:3], 
  MR_MG_OffSex_lnCVRi$ci.lb[1],
  MR_MG_OffSex_lnCVRf$ci.lb[3:2], 
  MR_MG_OffSex_lnCVRm$ci.lb[2]),3) 

t7$CI.ub[pos] <- round(c(
  MR_OF_OffSex_lnRRi$ci.ub[2:3], 
  MR_OF_OffSex_lnRRi$ci.ub[1],
  MR_OF_OffSex_lnRRf$ci.ub[3:2], 
  MR_OF_OffSex_lnRRm$ci.ub[2],
  MR_OF_OffSex_lnCVRi$ci.ub[2:3], 
  MR_OF_OffSex_lnCVRi$ci.ub[1],
  MR_OF_OffSex_lnCVRf$ci.ub[3:2], 
  MR_OF_OffSex_lnCVRm$ci.ub[2],
  MR_MG_OffSex_lnRRi$ci.ub[2:3], 
  MR_MG_OffSex_lnRRi$ci.ub[1],
  MR_MG_OffSex_lnRRf$ci.ub[3:2], 
  MR_MG_OffSex_lnRRm$ci.ub[2],
  MR_MG_OffSex_lnCVRi$ci.ub[2:3], 
  MR_MG_OffSex_lnCVRi$ci.ub[1],
  MR_MG_OffSex_lnCVRf$ci.ub[3:2], 
  MR_MG_OffSex_lnCVRm$ci.ub[2]),3) 

t7$k[pos] <- c(
  table(data_OF$Offspring_Sex)[c(2,3,1)], 
  rep(NA, 3),
  table(data_OF$Offspring_Sex)[c(2,3,1)], 
  rep(NA, 3),
  table(data_MG$Offspring_Sex)[c(2,3,1)], 
  rep(NA, 3),
  table(data_MG$Offspring_Sex)[c(2,3,1)], 
  rep(NA, 3)) 

# adding model R2 estimates to the table
posR2 <- c(1,8,15,22) #row positions
t7$`R2`[posR2] <- round(c(R2(MR_OF_OffSex_lnRRi)[1], R2(MR_OF_OffSex_lnCVRi)[1], R2(MR_MG_OffSex_lnRRi)[1], R2(MR_MG_OffSex_lnCVRi)[1]),3)

write.csv(t7, file = "../Tables/Table_S7.csv", row.names = F, na = "")    
```


### Table S8    
lnRR and lnCVR MR models for OF and MG datasets, with trait type of measured grand-offspring as a moderator.   

```{r Table MR univ Trait Type}
#list.files("./Rdata/")
# load(file = "./Rdata/MR_OF_Trait_lnRRi.Rdata")
# load(file = "./Rdata/MR_OF_Trait_lnCVRi.Rdata")
# load(file = "./Rdata/MR_MG_Trait_lnRRi.Rdata")
# load(file = "./Rdata/MR_MG_Trait_lnCVRi.Rdata")
# 
# load(file = "./Rdata/MR_OF_Trait_lnRR_releveled.Rdata")
# load(file = "./Rdata/MR_OF_Trait_lnCVR_releveled.Rdata")
# load(file = "./Rdata/MR_MG_Trait_lnRR_releveled.Rdata")
# load(file = "./Rdata/MR_MG_Trait_lnCVR_releveled.Rdata")

#cont_gen(levels(data_OF$Trait)) #list of potential contrasts
#write.csv(cont_gen(levels(data_OF$Trait)), file = "./Tables/Trait_contrasts.csv", row.names = F, na = "")  

# loading empty table
t8 <- read_excel("../Tables/Results_Tables_templates.xlsx", sheet = 5)

# saving row position for estimates
pos <- c(2:37, 39:74, 76:111, 113:148)

t8$`Mean`[pos] <- round(c(
  MR_OF_Trait_lnRRi$b, 
  MR_OF_Trait_lnRR_releveled[[1]]$estimate[2:8],
  MR_OF_Trait_lnRR_releveled[[2]]$estimate[3:8], 
  MR_OF_Trait_lnRR_releveled[[3]]$estimate[4:8], 
  MR_OF_Trait_lnRR_releveled[[4]]$estimate[5:8], 
  MR_OF_Trait_lnRR_releveled[[5]]$estimate[6:8], 
  MR_OF_Trait_lnRR_releveled[[6]]$estimate[7:8], 
  MR_OF_Trait_lnRR_releveled[[7]]$estimate[8],
    MR_OF_Trait_lnCVRi$b, 
  MR_OF_Trait_lnCVR_releveled[[1]]$estimate[2:8],
  MR_OF_Trait_lnCVR_releveled[[2]]$estimate[3:8], 
  MR_OF_Trait_lnCVR_releveled[[3]]$estimate[4:8], 
  MR_OF_Trait_lnCVR_releveled[[4]]$estimate[5:8], 
  MR_OF_Trait_lnCVR_releveled[[5]]$estimate[6:8], 
  MR_OF_Trait_lnCVR_releveled[[6]]$estimate[7:8], 
  MR_OF_Trait_lnCVR_releveled[[7]]$estimate[8],
    MR_MG_Trait_lnRRi$b, 
  MR_MG_Trait_lnRR_releveled[[1]]$estimate[2:8],
  MR_MG_Trait_lnRR_releveled[[2]]$estimate[3:8], 
  MR_MG_Trait_lnRR_releveled[[3]]$estimate[4:8], 
  MR_MG_Trait_lnRR_releveled[[4]]$estimate[5:8], 
  MR_MG_Trait_lnRR_releveled[[5]]$estimate[6:8], 
  MR_MG_Trait_lnRR_releveled[[6]]$estimate[7:8], 
  MR_MG_Trait_lnRR_releveled[[7]]$estimate[8],
    MR_MG_Trait_lnCVRi$b, 
  MR_MG_Trait_lnCVR_releveled[[1]]$estimate[2:8],
  MR_MG_Trait_lnCVR_releveled[[2]]$estimate[3:8], 
  MR_MG_Trait_lnCVR_releveled[[3]]$estimate[4:8], 
  MR_MG_Trait_lnCVR_releveled[[4]]$estimate[5:8], 
  MR_MG_Trait_lnCVR_releveled[[5]]$estimate[6:8], 
  MR_MG_Trait_lnCVR_releveled[[6]]$estimate[7:8], 
  MR_MG_Trait_lnCVR_releveled[[7]]$estimate[8] ),3) 

t8$CI.lb[pos] <- round(c(
  MR_OF_Trait_lnRRi$ci.lb, 
  MR_OF_Trait_lnRR_releveled[[1]]$ci.lb[2:8],
  MR_OF_Trait_lnRR_releveled[[2]]$ci.lb[3:8], 
  MR_OF_Trait_lnRR_releveled[[3]]$ci.lb[4:8], 
  MR_OF_Trait_lnRR_releveled[[4]]$ci.lb[5:8], 
  MR_OF_Trait_lnRR_releveled[[5]]$ci.lb[6:8], 
  MR_OF_Trait_lnRR_releveled[[6]]$ci.lb[7:8], 
  MR_OF_Trait_lnRR_releveled[[7]]$ci.lb[8],
    MR_OF_Trait_lnCVRi$ci.lb, 
  MR_OF_Trait_lnCVR_releveled[[1]]$ci.lb[2:8],
  MR_OF_Trait_lnCVR_releveled[[2]]$ci.lb[3:8], 
  MR_OF_Trait_lnCVR_releveled[[3]]$ci.lb[4:8], 
  MR_OF_Trait_lnCVR_releveled[[4]]$ci.lb[5:8], 
  MR_OF_Trait_lnCVR_releveled[[5]]$ci.lb[6:8], 
  MR_OF_Trait_lnCVR_releveled[[6]]$ci.lb[7:8], 
  MR_OF_Trait_lnCVR_releveled[[7]]$ci.lb[8],
    MR_MG_Trait_lnRRi$ci.lb, 
  MR_MG_Trait_lnRR_releveled[[1]]$ci.lb[2:8],
  MR_MG_Trait_lnRR_releveled[[2]]$ci.lb[3:8], 
  MR_MG_Trait_lnRR_releveled[[3]]$ci.lb[4:8], 
  MR_MG_Trait_lnRR_releveled[[4]]$ci.lb[5:8], 
  MR_MG_Trait_lnRR_releveled[[5]]$ci.lb[6:8], 
  MR_MG_Trait_lnRR_releveled[[6]]$ci.lb[7:8], 
  MR_MG_Trait_lnRR_releveled[[7]]$ci.lb[8],
    MR_MG_Trait_lnCVRi$ci.lb, 
  MR_MG_Trait_lnCVR_releveled[[1]]$ci.lb[2:8],
  MR_MG_Trait_lnCVR_releveled[[2]]$ci.lb[3:8], 
  MR_MG_Trait_lnCVR_releveled[[3]]$ci.lb[4:8], 
  MR_MG_Trait_lnCVR_releveled[[4]]$ci.lb[5:8], 
  MR_MG_Trait_lnCVR_releveled[[5]]$ci.lb[6:8], 
  MR_MG_Trait_lnCVR_releveled[[6]]$ci.lb[7:8], 
  MR_MG_Trait_lnCVR_releveled[[7]]$ci.lb[8] ),3) 

t8$CI.ub[pos] <- round(c(
  MR_OF_Trait_lnRRi$ci.ub, 
  MR_OF_Trait_lnRR_releveled[[1]]$ci.ub[2:8],
  MR_OF_Trait_lnRR_releveled[[2]]$ci.ub[3:8], 
  MR_OF_Trait_lnRR_releveled[[3]]$ci.ub[4:8], 
  MR_OF_Trait_lnRR_releveled[[4]]$ci.ub[5:8], 
  MR_OF_Trait_lnRR_releveled[[5]]$ci.ub[6:8], 
  MR_OF_Trait_lnRR_releveled[[6]]$ci.ub[7:8], 
  MR_OF_Trait_lnRR_releveled[[7]]$ci.ub[8],
    MR_OF_Trait_lnCVRi$ci.ub, 
  MR_OF_Trait_lnCVR_releveled[[1]]$ci.ub[2:8],
  MR_OF_Trait_lnCVR_releveled[[2]]$ci.ub[3:8], 
  MR_OF_Trait_lnCVR_releveled[[3]]$ci.ub[4:8], 
  MR_OF_Trait_lnCVR_releveled[[4]]$ci.ub[5:8], 
  MR_OF_Trait_lnCVR_releveled[[5]]$ci.ub[6:8], 
  MR_OF_Trait_lnCVR_releveled[[6]]$ci.ub[7:8], 
  MR_OF_Trait_lnCVR_releveled[[7]]$ci.ub[8],
    MR_MG_Trait_lnRRi$ci.ub, 
  MR_MG_Trait_lnRR_releveled[[1]]$ci.ub[2:8],
  MR_MG_Trait_lnRR_releveled[[2]]$ci.ub[3:8], 
  MR_MG_Trait_lnRR_releveled[[3]]$ci.ub[4:8], 
  MR_MG_Trait_lnRR_releveled[[4]]$ci.ub[5:8], 
  MR_MG_Trait_lnRR_releveled[[5]]$ci.ub[6:8], 
  MR_MG_Trait_lnRR_releveled[[6]]$ci.ub[7:8], 
  MR_MG_Trait_lnRR_releveled[[7]]$ci.ub[8],
    MR_MG_Trait_lnCVRi$ci.ub, 
  MR_MG_Trait_lnCVR_releveled[[1]]$ci.ub[2:8],
  MR_MG_Trait_lnCVR_releveled[[2]]$ci.ub[3:8], 
  MR_MG_Trait_lnCVR_releveled[[3]]$ci.ub[4:8], 
  MR_MG_Trait_lnCVR_releveled[[4]]$ci.ub[5:8], 
  MR_MG_Trait_lnCVR_releveled[[5]]$ci.ub[6:8], 
  MR_MG_Trait_lnCVR_releveled[[6]]$ci.ub[7:8], 
  MR_MG_Trait_lnCVR_releveled[[7]]$ci.ub[8] ),3) 

t8$k[pos] <- c(
  table(data_OF$Trait), 
  rep(NA, 28),
  table(data_OF$Trait), 
  rep(NA, 28),
  table(data_MG$Trait), 
  rep(NA, 28),
  table(data_MG$Trait), 
  rep(NA, 28)) 

# adding model R2 estimates to the table
posR2 <- c(1,38,75,112) #row positions
t8$`R2`[posR2] <- round(c(R2(MR_OF_Trait_lnRRi)[1], R2(MR_OF_Trait_lnCVRi)[1], R2(MR_MG_Trait_lnRRi)[1], R2(MR_MG_Trait_lnCVRi)[1]),3)

write.csv(t8, file = "../Tables/Table_S8.csv", row.names = F, na = "")    
```


### Table S9    
Full MR models for lnRR and lnCVR on OF and MG datasets 

```{r Table MR univ Exposure Type}
#list.files("./Rdata/")
# load(file = "./Rdata/MR_OF_Full_lnRR.Rdata")
# load(file = "./Rdata/MR_OF_Full_lnCVR.Rdata")
# load(file = "./Rdata/MR_MG_Full_lnRR.Rdata")
# load(file = "./Rdata/MR_MG_Full_lnCVR.Rdata")

# loading empty table
t9 <- read_excel("../Tables/Results_Tables_templates.xlsx", sheet = 6)

# saving row position for estimates
pos <- c(2:13, 15:26, 28:38, 40:50)

t9$`Mean`[pos] <- round(c(
  MR_OF_Full_lnRR$b, 
  MR_OF_Full_lnCVR$b,
  MR_MG_Full_lnRR$b, 
  MR_MG_Full_lnCVR$b), 3) 
  
t9$CI.lb[pos] <- round(c(
  MR_OF_Full_lnRR$ci.lb, 
  MR_OF_Full_lnCVR$ci.lb,
  MR_MG_Full_lnRR$ci.lb, 
  MR_MG_Full_lnCVR$ci.lb), 3) 

t9$CI.ub[pos] <- round(c(
  MR_OF_Full_lnRR$ci.ub, 
  MR_OF_Full_lnCVR$ci.ub,
  MR_MG_Full_lnRR$ci.ub, 
  MR_MG_Full_lnCVR$ci.ub), 3) 

# adding model R2 estimates to the table
posR2 <- c(1, 14, 27, 39) #row positions
t9$`R2`[posR2] <- round(c(R2(MR_all_ExpT_lnRR)[1], R2(MR_all_ExpT_lnCVR)[1]),3)
# adding model k values to the table
t9$k[posR2] <- c( rep(dim(data_OF)[1],2), rep(dim(data_MG)[1],2) ) 

write.csv(t9, file = "../Tables/Table_S9.csv", row.names = F, na = "")    
```


### Table S10 
MR model selection analysis for lnRR and lnCVR on OF and MG datasets 

```{r Table model selection}
#list.files("./Rdata/")
#loading data
load(file = "../Rdata/MR_OF_Full_lnRR_ML_meta_AICc_seltable.Rdata") 
MR_OF_Full_lnRRst <- sel.table
load(file = "../Rdata/MR_OF_Full_lnCVR_ML_meta_AICc_seltable.Rdata")
MR_OF_Full_lnCVRst <- sel.table
load(file = "../Rdata/MR_MG_Full_lnRR_ML_meta_AICc_seltable.Rdata")
MR_MG_Full_lnRRst <- sel.table
load(file = "../Rdata/MR_MG_Full_lnCVR_ML_meta_AICc_seltable.Rdata")
MR_MG_Full_lnCVRst <- sel.table

# loading table template
t10 <- read_excel("../Tables/Results_Tables_templates.xlsx", sheet = 7)

# saving row position
pos <- c(2:9, 11:18, 20:27, 29:36)

t10$`Model`[pos] <- c(MR_OF_Full_lnRRst$Model, MR_OF_Full_lnCVRst$Model, MR_MG_Full_lnRRst$Model, MR_MG_Full_lnCVRst$Model)
t10$`K`[pos] <- c(MR_OF_Full_lnRRst$K, MR_OF_Full_lnCVRst$K, MR_MG_Full_lnRRst$K, MR_MG_Full_lnCVRst$K)
t10$`logLik`[pos] <- round(c(MR_OF_Full_lnRRst$logLik, MR_OF_Full_lnCVRst$logLik, MR_MG_Full_lnRRst$logLik, MR_MG_Full_lnCVRst$logLik),2)
t10$`AICc`[pos] <- round(c(MR_OF_Full_lnRRst$AICc, MR_OF_Full_lnCVRst$AICc, MR_MG_Full_lnRRst$AICc, MR_MG_Full_lnCVRst$AICc),2)
t10$`delta`[pos] <- round(c(MR_OF_Full_lnRRst$delta, MR_OF_Full_lnCVRst$delta, MR_MG_Full_lnRRst$delta, MR_MG_Full_lnCVRst$delta),2)
t10$`weight`[pos] <- round(c(MR_OF_Full_lnRRst$weight, MR_OF_Full_lnCVRst$weight, MR_MG_Full_lnRRst$weight, MR_MG_Full_lnCVRst$weight),2)

write.csv(t10, file = "../Tables/Table_S10_modelselection.csv", row.names = F, na = "")    
```


### Table S11 
Publication bias analysis for lnRR and lnCVR on OF and MG datasets - multivariate Egger's regression

```{r publiction bias, eval=FALSE, include=FALSE}
# load(file = "./Rdata/PB_OF_MG_Full.Rdata") #contains: PB_OF_Full_lnRR, PB_OF_Full_lnCVR, PB_MG_Full_lnRR, PB_MG_Full_lnCVR

# loading empty table
t11 <- read_excel("../Tables/Results_Tables_templates.xlsx", sheet = 8)

# saving row positions for estimates
pos <- c(2:14, 16:28, 30:41, 43:54)

t11$`Mean`[pos] <- round(c(
  PB_OF_Full_lnRR$b, 
  PB_OF_Full_lnCVR$b,
  PB_MG_Full_lnRR$b, 
  PB_MG_Full_lnCVR$b), 3) 
  
t11$CI.lb[pos] <- round(c(
  PB_OF_Full_lnRR$ci.lb, 
  PB_OF_Full_lnCVR$ci.lb,
  PB_MG_Full_lnRR$ci.lb, 
  PB_MG_Full_lnCVR$ci.lb), 3) 

t11$CI.ub[pos] <- round(c(
  PB_OF_Full_lnRR$ci.ub, 
  PB_OF_Full_lnCVR$ci.ub,
  PB_MG_Full_lnRR$ci.ub, 
  PB_MG_Full_lnCVR$ci.ub), 3) 

t11$p[pos] <- round(c(
  PB_OF_Full_lnRR$pval, 
  PB_OF_Full_lnCVR$pval,
  PB_MG_Full_lnRR$pval, 
  PB_MG_Full_lnCVR$pval), 3) 

# adding model R2 estimates to the table
posR2 <- c(1, 15, 29, 42) #row positions
t11$`R2`[posR2] <- round(c(R2(PB_OF_Full_lnRR)[1], R2(PB_OF_Full_lnCVR)[1], R2(PB_MG_Full_lnRR)[1], R2(PB_MG_Full_lnCVR)[1]),3)

write.csv(t11, file = "../Tables/Table_S11.csv", row.names = F, na = "")    
```


### Table S12 
lnRR and lnCVR MR models for OF and MG datasets, with study publication year as a moderator (part if pubication bias analyses)      
```{r publiction year, eval=FALSE, include=FALSE}
load(file = "../Rdata/MR_OF_Year_lnRR.Rdata")
load(file = "../Rdata/MR_OF_Year_lnCVR.Rdata")
load(file = "../Rdata/MR_MG_Year_lnRR.Rdata")
load(file = "../Rdata/MR_MG_Year_lnCVR.Rdata")

# loading empty table
t12 <- read_excel("../Tables/Results_Tables_templates.xlsx", sheet = 9)

# saving row positions for estimates
pos <- c(2:3, 5:6, 8:9, 11:12)

t12$`Mean`[pos] <- round(c(
  MR_OF_Year_lnRR$b, 
  MR_OF_Year_lnCVR$b,
  MR_MG_Year_lnRR$b, 
  MR_MG_Year_lnCVR$b), 3) 
  
t12$CI.lb[pos] <- round(c(
  MR_OF_Year_lnRR$ci.lb, 
  MR_OF_Year_lnCVR$ci.lb,
  MR_MG_Year_lnRR$ci.lb, 
  MR_MG_Year_lnCVR$ci.lb), 3) 

t12$CI.ub[pos] <- round(c(
  MR_OF_Year_lnRR$ci.ub, 
  MR_OF_Year_lnCVR$ci.ub,
  MR_MG_Year_lnRR$ci.ub, 
  MR_MG_Year_lnCVR$ci.ub), 3) 

t12$p[pos] <- round(c(
  MR_OF_Year_lnRR$pval, 
  MR_OF_Year_lnCVR$pval,
  MR_MG_Year_lnRR$pval, 
  MR_MG_Year_lnCVR$pval), 3) 

# adding model R2 estimates to the table
posR2 <- c(1, 4, 7, 10) #row positions
t12$`R2`[posR2] <- round(c(R2(MR_OF_Year_lnRR)[1], R2(MR_OF_Year_lnCVR)[1], R2(MR_MG_Year_lnRR)[1], R2(MR_MG_Year_lnCVR)[1]),3)

write.csv(t12, file = "../Tables/Table_S12.csv", row.names = F, na = "")    
```


### Table S13    
lnRR and lnCVR MR models for OF and MG datasets, with total energy content of obesogenic diet as a moderator    

```{r total energy content, eval=FALSE, include=FALSE}
load(file = "../Rdata/MR_OF_DietE_lnRR.Rdata")
load(file = "../Rdata/MR_OF_DietE_lnCVR.Rdata")
load(file = "../Rdata/MR_MG_DietE_lnRR.Rdata")
load(file = "../Rdata/MR_MG_DietE_lnCVR.Rdata")

# loading empty table
t13 <- read_excel("../Tables/Results_Tables_templates.xlsx", sheet = 10)

# saving row positions for estimates
pos <- c(2:3, 5:6, 8:9, 11:12)

t13$`Mean`[pos] <- round(c(
  MR_OF_DietE_lnRR$b, 
  MR_OF_DietE_lnCVR$b,
  MR_MG_DietE_lnRR$b, 
  MR_MG_DietE_lnCVR$b), 3) 
  
t13$CI.lb[pos] <- round(c(
  MR_OF_DietE_lnRR$ci.lb, 
  MR_OF_DietE_lnCVR$ci.lb,
  MR_MG_DietE_lnRR$ci.lb, 
  MR_MG_DietE_lnCVR$ci.lb), 3) 

t13$CI.ub[pos] <- round(c(
  MR_OF_DietE_lnRR$ci.ub, 
  MR_OF_DietE_lnCVR$ci.ub,
  MR_MG_DietE_lnRR$ci.ub, 
  MR_MG_DietE_lnCVR$ci.ub), 3) 

t13$p[pos] <- round(c(
  MR_OF_DietE_lnRR$pval, 
  MR_OF_DietE_lnCVR$pval,
  MR_MG_DietE_lnRR$pval, 
  MR_MG_DietE_lnCVR$pval), 3) 

# adding model R2 estimates to the table
posR2 <- c(1, 4, 7, 10) #row positions
t13$`R2`[posR2] <- round(c(R2(MR_OF_DietE_lnRR)[1], R2(MR_OF_DietE_lnCVR)[1], R2(MR_MG_DietE_lnRR)[1], R2(MR_MG_DietE_lnCVR)[1]),3)

write.csv(t13, file = "../Tables/Table_S13.csv", row.names = F, na = "")    
```


### Table S14    
lnRR and lnCVR MR models for OF and MG datasets, with relative protein content of the obesogenic diet as a moderator 

```{r relative protein content, eval=FALSE, include=FALSE}
load(file = "../Rdata/MR_OF_DietPNP_lnRR.Rdata")
load(file = "../Rdata/MR_OF_DietPNP_lnCVR.Rdata")
load(file = "../Rdata/MR_MG_DietPNP_lnRR.Rdata")
load(file = "../Rdata/MR_MG_DietPNP_lnCVR.Rdata")

# loading empty table
t14 <- read_excel("../Tables/Results_Tables_templates.xlsx", sheet = 11)

# saving row positions for estimates
pos <- c(2:3, 5:6, 8:9, 11:12)

t14$`Mean`[pos] <- round(c(
  MR_OF_DietPNP_lnRR$b, 
  MR_OF_DietPNP_lnCVR$b,
  MR_MG_DietPNP_lnRR$b, 
  MR_MG_DietPNP_lnCVR$b), 3) 
  
t14$CI.lb[pos] <- round(c(
  MR_OF_DietPNP_lnRR$ci.lb, 
  MR_OF_DietPNP_lnCVR$ci.lb,
  MR_MG_DietPNP_lnRR$ci.lb, 
  MR_MG_DietPNP_lnCVR$ci.lb), 3) 

t14$CI.ub[pos] <- round(c(
  MR_OF_DietPNP_lnRR$ci.ub, 
  MR_OF_DietPNP_lnCVR$ci.ub,
  MR_MG_DietPNP_lnRR$ci.ub, 
  MR_MG_DietPNP_lnCVR$ci.ub), 3) 

t14$p[pos] <- round(c(
  MR_OF_DietPNP_lnRR$pval, 
  MR_OF_DietPNP_lnCVR$pval,
  MR_MG_DietPNP_lnRR$pval, 
  MR_MG_DietPNP_lnCVR$pval), 3) 

# adding model R2 estimates to the table
posR2 <- c(1, 4, 7, 10) #row positions
t14$`R2`[posR2] <- round(c(R2(MR_OF_DietPNP_lnRR)[1], R2(MR_OF_DietPNP_lnCVR)[1], R2(MR_MG_DietPNP_lnRR)[1], R2(MR_MG_DietPNP_lnCVR)[1]),3)

write.csv(t14, file = "../Tables/Table_S14.csv", row.names = F, na = "")    
```


### Table S15     
lnRR and lnCVR MR models for OF and MG datasets, with duration of the exposure of the grandparents to obesogenic diet as a moderator    

```{r F0 exposure duration, eval=FALSE, include=FALSE}
load(file = "../Rdata/MR_OF_TDur_lnRR.Rdata")
load(file = "../Rdata/MR_OF_TDur_lnCVR.Rdata")
load(file = "../Rdata/MR_MG_TDur_lnRR.Rdata")
load(file = "../Rdata/MR_MG_TDur_lnCVR.Rdata")

# loading empty table
t15 <- read_excel("../Tables/Results_Tables_templates.xlsx", sheet = 12)

# saving row positions for estimates
pos <- c(2:3, 5:6, 8:9, 11:12)

t15$`Mean`[pos] <- round(c(
  MR_OF_TDur_lnRR$b, 
  MR_OF_TDur_lnCVR$b,
  MR_MG_TDur_lnRR$b, 
  MR_MG_TDur_lnCVR$b), 3) 
  
t15$CI.lb[pos] <- round(c(
  MR_OF_TDur_lnRR$ci.lb, 
  MR_OF_TDur_lnCVR$ci.lb,
  MR_MG_TDur_lnRR$ci.lb, 
  MR_MG_TDur_lnCVR$ci.lb), 3) 

t15$CI.ub[pos] <- round(c(
  MR_OF_TDur_lnRR$ci.ub, 
  MR_OF_TDur_lnCVR$ci.ub,
  MR_MG_TDur_lnRR$ci.ub, 
  MR_MG_TDur_lnCVR$ci.ub), 3) 

t15$p[pos] <- round(c(
  MR_OF_TDur_lnRR$pval, 
  MR_OF_TDur_lnCVR$pval,
  MR_MG_TDur_lnRR$pval, 
  MR_MG_TDur_lnCVR$pval), 3) 

# adding model R2 estimates to the table
posR2 <- c(1, 4, 7, 10) #row positions
t15$`R2`[posR2] <- round(c(R2(MR_OF_TDur_lnRR)[1], R2(MR_OF_TDur_lnCVR)[1], R2(MR_MG_TDur_lnRR)[1], R2(MR_MG_TDur_lnCVR)[1]),3)

write.csv(t15, file = "../Tables/Table_S15.csv", row.names = F, na = "")    
```

### Table S16    
lnRR and lnCVR MR models for OF and MG datasets, with grand-offspring generation as a moderator    

```{r MR Offspring_Generation, include = TRUE}
load(file = "../Rdata/MR_OF_OffGen_lnRR.Rdata")
load(file = "../Rdata/MR_OF_OffGen_lnRRi.Rdata")
load(file = "../Rdata/MR_OF_OffGen_lnCVR.Rdata")
load(file = "../Rdata/MR_OF_OffGen_lnCVRi.Rdata")
load(file = "../Rdata/MR_MG_OffGen_lnRR.Rdata")
load(file = "../Rdata/MR_MG_OffGen_lnRRi.Rdata")
load(file = "../Rdata/MR_MG_OffGen_lnRR.Rdata")
load(file = "../Rdata/MR_MG_OffGen_lnCVRi.Rdata")

# loading empty table
t16 <- read_excel("../Tables/Results_Tables_templates.xlsx", sheet = 13)

# saving row positions for estimates
pos <- c(2:4, 6:8, 10:12, 14:16)

t16$`Mean`[pos] <- round(c(
  MR_OF_OffGen_lnRRi$b, 
  MR_OF_OffGen_lnRR$b[2],
  MR_OF_OffGen_lnCVRi$b, 
  MR_OF_OffGen_lnCVR$b[2],
  MR_MG_OffGen_lnRRi$b, 
  MR_MG_OffGen_lnRR$b[2],
  MR_MG_OffGen_lnCVRi$b, 
  MR_MG_OffGen_lnCVR$b[2]), 3) 
  
t16$CI.lb[pos] <- round(c(
  MR_OF_OffGen_lnRRi$ci.lb, 
  MR_OF_OffGen_lnRR$ci.lb[2],
  MR_OF_OffGen_lnCVRi$ci.lb, 
  MR_OF_OffGen_lnCVR$ci.lb[2],
  MR_MG_OffGen_lnRRi$ci.lb, 
  MR_MG_OffGen_lnRR$ci.lb[2],
  MR_MG_OffGen_lnCVRi$ci.lb, 
  MR_MG_OffGen_lnCVR$ci.lb[2]), 3) 

t16$CI.ub[pos] <- round(c(
  MR_OF_OffGen_lnRRi$ci.ub, 
  MR_OF_OffGen_lnRR$ci.ub[2],
  MR_OF_OffGen_lnCVRi$ci.ub, 
  MR_OF_OffGen_lnCVR$ci.ub[2],
  MR_MG_OffGen_lnRRi$ci.ub, 
  MR_MG_OffGen_lnRR$ci.ub[2],
  MR_MG_OffGen_lnCVRi$ci.ub, 
  MR_MG_OffGen_lnCVR$ci.ub[2]), 3) 

t16$k[pos] <- c(
  rev(table(data_all$Offspring_Generation)), 
  rep(NA, 1),
  rev(table(data_all$Offspring_Generation)), 
  rep(NA, 1),
  rev(table(data_all$Offspring_Generation)), 
  rep(NA, 1),
  rev(table(data_all$Offspring_Generation)), 
  rep(NA, 1)
  ) 

# adding model R2 estimates to the table
posR2 <- c(1, 5, 9, 13) #row positions
t16$`R2`[posR2] <- round(c(R2(MR_OF_OffGen_lnRR)[1], R2(MR_OF_OffGen_lnCVR)[1], R2(MR_MG_OffGen_lnRR)[1], R2(MR_MG_OffGen_lnCVR)[1]),3)

write.csv(t16, file = "../Tables/Table_S16.csv", row.names = F, na = "")    
```


### Table S17    
lnRR MR models for body weights of F0, OF and MG datasets, with age at measurement as a moderator    

```{r MR Body_weight, include = TRUE}
load(file = "../Rdata/MR_F0_age.Rdata")
load(file = "../Rdata/MR_OF_age.Rdata")
load(file = "../Rdata/MR_MG_age.Rdata")

# loading empty table
t17 <- read_excel("../Tables/Results_Tables_templates.xlsx", sheet = 14)

# saving row positions for estimates
pos <- c(2:3, 5:6, 8:9)

t17$`Mean`[pos] <- round(c(
  MR_F0_age$b[1:2], 
  MR_OF_age$b[1:2], 
  MR_MG_age$b[1:2]), 3)
  
t17$CI.lb[pos] <- round(c(
  MR_F0_age$ci.lb, 
  MR_OF_age$ci.lb, 
  MR_MG_age$ci.lb), 3) 

t17$CI.ub[pos] <- round(c(
  MR_F0_age$ci.ub, 
  MR_OF_age$ci.ub, 
  MR_MG_age$ci.ub), 3) 

t17$p[pos] <- round(c(
  MR_F0_age$pval, 
  MR_OF_age$pval, 
  MR_MG_age$pval), 3) 

# adding model R2 estimates to the table
posR2 <- c(1, 4, 7) #row positions
t17$`R2`[posR2] <- round(c(R2(MR_F0_age)[1], R2(MR_OF_age)[1], R2(MR_MG_age)[1]),3)

write.csv(t17, file = "../Tables/Table_S17.csv", row.names = F, na = "")    
```


### Table S18    
Predict %difference in body weights of F0, OF and MG datasets at 100 days   

```{r predict Body_weight at 100 days, include = TRUE}
load(file = "../Rdata/prediction_F0.Rdata")
load(file = "../Rdata/prediction_OF.Rdata")
load(file = "../Rdata/prediction_MG.Rdata")

# loading empty table
t18 <- read_excel("../Tables/Results_Tables_templates.xlsx", sheet = 15)

# saving row positions for estimates
pos <- c(1:3)

t18$`Mean`[pos] <- round(c(
  prediction_F0$pred, 
  prediction_OF$pred, 
  prediction_MG$pred), 3)

t18$SE[pos] <- round(c(
  prediction_F0$se, 
  prediction_OF$se, 
  prediction_MG$se), 3)
  
t18$CI.lb[pos] <- round(c(
  prediction_F0$ci.lb, 
  prediction_OF$ci.lb, 
  prediction_MG$ci.lb), 3) 

t18$CI.ub[pos] <- round(c(
  prediction_F0$ci.ub, 
  prediction_OF$ci.ub, 
  prediction_MG$ci.ub), 3) 

t18$PI.lb[pos] <- round(c(
  prediction_F0$cr.lb, 
  prediction_OF$cr.lb, 
  prediction_MG$cr.lb), 3) 

t18$PI.ub[pos] <- round(c(
  prediction_F0$cr.ub, 
  prediction_OF$cr.ub, 
  prediction_MG$cr.ub), 3) 

write.csv(t18, file = "../Tables/Table_S18.csv", row.names = F, na = "")    
```

## Supplementary Figures    

```{r FigureS1, out.width = "400px"}
knitr::include_graphics("../Plots/SI_PRISMA_v2.pdf")
```
### Figure S1.    
PRISMA flow diagram summarising the literature search and screening process.        
[can be also inserted manually ufter updating the search]    


```{r FigureS2, out.width = "400px"}
knitr::include_graphics("../Plots/SI_Figure_DecisionTree_abstracts_v0.pdf")
```
### Figure S2.    
Decision tree used to screen titles and abstracts from bibliometric records of found studies.       


```{r FigureS3, out.width = "400px"}
knitr::include_graphics("../Plots/SI_Figure_DecisionTree_fulltexts_v0.pdf")
```
### Figure S3.     
Decision tree used to screen full-text papers.    


### Figure S4.     
insert Figure_diets_Rplot_v0.pdf


### Figure S5.     
insert Figure_exposure_Rplot_v0.pdf


### Figure S6.     
insert Figure_funnels_Rplot_v0.pdf
