---
title: "STEP4_PLOTS"
subtitle: "MA of transgenerational effects of obesogenic diets on rodents"
author: "ML"
date: "01/05/2020"
output: html_document
knit: (function(inputFile, encoding) {rmarkdown::render(inputFile, encoding = encoding, output_dir = "Knitted") })
---

Create plots - saved as pdf for the manuscript.   
[Note: run by chunks, do not knit]    

### Setup
```{r setup, include=FALSE, message=FALSE, warning=FALSE}


knitr::opts_chunk$set(
echo = FALSE,
message = FALSE,
warning = FALSE, # no warnings
cache = TRUE,# Cacheing to save time when kniting
tidy = TRUE
#fig.width = 9
)

options(scipen=100)

# Load packages
# devtools::install_github("thomasp85/patchwork")
pacman::p_load(tidyverse, # tidy family and related pacakges below
               metafor, # calculating effect sizes
               magrittr, # extending piping
               ggplot2,  # nice plots
               patchwork,  # arranging plots
               orchaRd #orchard plots, !!! actually using custom function - modified version with new argument k = FALSE !!!
)

# Load custom functions
#source("./Scripts/custom_functions.R") #load custom functions
```

<!-- ### Load data     -->
<!-- Processed data for analyses is stored in data_all_ES.csv and data_all_ES.RData fils.  -->
<!-- It needs to be split into One-off and Multigenerational data.       -->

<!-- ```{r load and subset data, include = FALSE} -->
<!-- # Load preprocessed data with effect sizes -->
<!-- data_all <- read.csv(file ="./Data/data_all_ES.csv") -->
<!-- #load(data_all, file = "../Rdata/data_all_ES.RData") #alternative -->
<!-- #str(data_all) -->

<!-- # Subset by One off and Multigenerational -->
<!-- data_MG <- filter(data_all, Exposure_Type == "Multigenerational") -->
<!-- data_OF <- filter(data_all, Exposure_Type == "One-off") -->
<!-- dim(data_MG) -->
<!-- dim(data_OF) -->
<!-- data_MG <- droplevels(data_MG) #adjust factor levels -->
<!-- data_OF <- droplevels(data_OF) #adjust factor levels -->
<!-- ``` -->

# ```{r load models, include = FALSE}
# 
# # for Figure2
# load(file = "../Rdata/MR_all_ExpT_lnRRi.Rdata")
# load(file = "../Rdata/MR_all_ExpT_lnCVRi.Rdata")
# 
# # for Figure3
# load(file = "../Rdata/MR_OF_ExpSex_lnRRi.Rdata")
# load(file = "../Rdata/MR_OF_ExpSex_lnCVRi.Rdata")
# load(file = "../Rdata/MR_MG_ExpSex_lnRRi.Rdata")
# load(file = "../Rdata/MR_MG_ExpSex_lnCVRi.Rdata")
# 
# # for Figure4
# load(file = "../Rdata/MR_OF_OffSex_lnRRi.Rdata")
# load(file = "../Rdata/MR_OF_OffSex_lnCVRi.Rdata")
# load(file = "../Rdata/MR_MG_OffSex_lnRRi.Rdata")
# load(file = "../Rdata/MR_MG_OffSex_lnCVRi.Rdata")
# 
# # for Figure5
# load(file = "../Rdata/MR_OF_Trait_lnRRi.Rdata")
# load(file = "../Rdata/MR_OF_Trait_lnCVRi.Rdata")
# load(file = "../Rdata/MR_MG_Trait_lnRRi.Rdata")
# load(file = "../Rdata/MR_MG_Trait_lnCVRi.Rdata")
# 
# # for funnel plots
# load(file = "../Rdata/PB_OF_Full_lnRR.Rdata")
# load(file = "../Rdata/PB_OF_Full_lnCVR.Rdata")
# load(file = "../Rdata/PB_MG_Full_lnRR.Rdata")
# load(file = "../Rdata/PB_MG_Full_lnCVR.Rdata")
# 
# ```


### Figure1 - summarise sample sizes for the 3 main moderators (F0_Parent_Exposed, Offspring_Sex, Trait) for ODF and MG data   

*Note:* manually marge with the experiment schematics picture.   

```{r Figure1 summary - categories sample sizes}

# plotting 3 plots in a single column with less labels

## F0_Parent_Exposed
# prepare data for plotting
plotting_df <- data_all %>% group_by(F0_Parent_Exposed, Exposure_Type) %>% summarise(Freq = n()) %>% mutate(Freq = if_else(Exposure_Type == "One-off", -Freq, Freq))
temp_df <- plotting_df %>% filter(Exposure_Type == "One-off") %>% arrange(Freq)
the_order <- rev(temp_df$F0_Parent_Exposed)
# plot
p_F0_Parent_Exposed <- 
  plotting_df %>% 
  ggplot(aes(x = F0_Parent_Exposed, y = Freq, group = Exposure_Type, fill = Exposure_Type)) +
  geom_bar(stat = "identity", width = 0.5) +
  coord_flip() +
  scale_x_discrete(limits = the_order, position = "top") + #used ordered F0_Parent_Exposeds - use for single axis
  scale_y_continuous(breaks = seq(-200, 100, 50), labels = abs(seq(-200, 100, 50)), limits = c(-210, 150)) +
  labs(x = "", y = "", title = "Number of effect sizes by exposed grand-parent sex") +
  theme(legend.position = "none",
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill =  "white"), 
        panel.grid.major.x = element_line("grey")) +
  scale_fill_manual(values=c("#56B4E9", "#E69F00"),   # change the default colors of bars
                    name="",
                    breaks=c("One-off", "Multigenerational"),
                    labels=c("One-off", "Multigenerational")) 
#print(p_F0_Parent_Exposed)

## Offspring_Sex
# prepare data for plotting
plotting_df <- data_all %>% group_by(Offspring_Sex, Exposure_Type) %>% summarise(Freq = n()) %>% mutate(Freq = if_else(Exposure_Type == "One-off", -Freq, Freq))
temp_df <- plotting_df %>%  filter(Exposure_Type == "One-off") %>%  arrange(Freq)
the_order <- rev(temp_df$Offspring_Sex)
# plot
p_Offspring_Sex <- 
  plotting_df %>% 
  ggplot(aes(x = Offspring_Sex, y = Freq, group = Exposure_Type, fill = Exposure_Type)) +
  geom_bar(stat = "identity", width = 0.5) +
  coord_flip() +
  scale_x_discrete(limits = the_order, position = "top") + #used ordered Offspring_Sexs - use for single axis
  scale_y_continuous(breaks = seq(-200, 100, 50), labels = abs(seq(-200, 100, 50)), limits = c(-210, 150)) +
  labs(x = "", y = "", title = "Number of effect sizes by grand-offspring sex") +
  theme(legend.position = "none",
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill =  "white"), 
        panel.grid.major.x = element_line("grey")) +
  scale_fill_manual(values=c("#56B4E9", "#E69F00"),   # change the default colors of bars
                    name="",
                    breaks=c("One-off", "Multigenerational"),
                    labels=c("One-off", "Multigenerational")) 
#print(p_Offspring_Sex)

## Trait
# prepare data for plotting
plotting_df <- data_all %>% group_by(Trait, Exposure_Type) %>% summarise(Freq = n()) %>% mutate(Freq = if_else(Exposure_Type == "One-off", -Freq, Freq))
temp_df <- plotting_df %>%  filter(Exposure_Type == "One-off") %>%  arrange(Freq)
the_order <- rev(temp_df$Trait)
# plot
p_Trait <- 
  plotting_df %>% 
  ggplot(aes(x = Trait, y = Freq, group = Exposure_Type, fill = Exposure_Type)) +
  geom_bar(stat = "identity", width = 0.5) +
  coord_flip() +
  scale_x_discrete(limits = the_order, position = "top") + #used ordered Traits - use for single axis
  scale_y_continuous(breaks = seq(-200, 100, 50), labels = abs(seq(-200, 100, 50)), limits = c(-210, 150)) +
  labs(x = "", y = "", title = "Number of effect sizes by grand-offspring trait") +
  theme(legend.position = "none",
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill =  "white"), 
        panel.grid.major.x = element_line("grey")) +
  scale_fill_manual(values=c("#56B4E9", "#E69F00"),   # change the default colors of bars
                    name="",
                    breaks=c("One-off", "Multigenerational"),
                    labels=c("One-off", "Multigenerational")) 
#print(p_Trait)

p_F0_Parent_Exposed / p_Offspring_Sex / p_Trait + plot_layout(ncol=1,heights=c(1,1,3))

ggsave(file = "../Plots/Figure1b_Rplot_v0.pdf", width = 8, height = 7, units = "cm", dpi = 300, scale=1.8)
```


### Figure2 - MR with Exposure Type as moderator (lnRR, lnCVR)

```{r Figure2 MR Exposure_Type}

## lnRR
p1 <- orchard_plot(MR_all_ExpT_lnRRi, mod = "Exposure_Type", xlab = "lnRR", transfm = "none", alpha = 0.3, angle = 45, cb = FALSE, k = FALSE) +
  scale_colour_manual(values=c("#E69F00", "#56B4E9")) + 
  scale_fill_manual(values=c("#E69F00", "#56B4E9")) +
  labs(title="a.", fontface = "bold") +
  scale_x_continuous(limits = c(-3, 4), n.breaks = 20) + 
  scale_y_discrete(labels = c("Multigenerational", "One-off")) +
  geom_text(x=3, y=2.2, label = paste("k =", colSums(MR_all_ExpT_lnRRi$X)["Exposure_TypeOne-off"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=1.2, label = paste("k =", colSums(MR_all_ExpT_lnRRi$X)["Exposure_TypeMultigenerational"]), fontface = "italic", size = 3) +
  theme(legend.position = "none", plot.margin = margin(30, 2, 2, 2, unit = "pt")) +
  labs(y = "Exposure type", angle = 90)+
  annotate('text', x = 4, y = 0.9, label="*", fontface="bold", size=6)

## lnCVR
p2 <- orchard_plot(MR_all_ExpT_lnCVRi, mod = "Exposure_Type", xlab = "lnCVR", transfm = "none", alpha = 0.3, angle = 45, cb = FALSE, k = FALSE) +
  scale_colour_manual(values=c("#E69F00", "#56B4E9")) + 
  scale_fill_manual(values=c("#E69F00", "#56B4E9")) +
  labs(title="b.", fontface = "bold") +
  scale_x_continuous(limits = c(-3, 4), n.breaks = 20) + 
  scale_y_discrete(labels = c("Multigenerational", "One-off")) +
  geom_text(x=3, y=2.2, label = paste("k =", colSums(MR_all_ExpT_lnRRi$X)["Exposure_TypeOne-off"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=1.2, label = paste("k =", colSums(MR_all_ExpT_lnRRi$X)["Exposure_TypeMultigenerational"]), fontface = "italic", size = 3) +
  theme(legend.position = "none", plot.margin = margin(30, 2, 2, 2, unit = "pt")) +
  labs(y = "Exposure type", angle = 90)

p1 + p2  + plot_layout(ncol = 1) #assemble plot panels
ggsave("../Plots/Figure2_Rplot_v0.pdf", width = 16, height = 8, units = "cm", dpi = 300, scale = 1.6)
```


### Figure 3 - MR with exposed F0 sex as moderator (lnRR, lnCVR)

```{r Figure3 MR FO_Parent_Exposed}
# "#56B4E9" - One-off, "#E69F00" - Multigenerational

## OF lnRR 
p1 <- orchard_plot(MR_OF_ExpSex_lnRRi, mod = "F0_Parent_Exposed", xlab = "lnRR", transfm = "none", alpha = 0.3, angle = 45, cb = FALSE, k = FALSE) +
  scale_colour_manual(values = rep("#56B4E9", 3)) + 
  scale_fill_manual(values = rep("#56B4E9", 3)) +
  labs(title="a. ") +
  scale_x_continuous(limits = c(-3, 4), n.breaks = 10) + 
  scale_y_discrete(labels = c("Both", "Female", "Male")) +
  geom_text(x=3, y=1.2, label = paste("k =", colSums(MR_OF_ExpSex_lnRRi$X)["F0_Parent_ExposedBoth"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=2.2, label = paste("k =", colSums(MR_OF_ExpSex_lnRRi$X)["F0_Parent_ExposedFemale"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=3.2, label = paste("k =", colSums(MR_OF_ExpSex_lnRRi$X)["F0_Parent_ExposedMale"]), fontface = "italic", size = 3) + 
  geom_text(x=-2, y=3.4, label = "One-off", fontface = "bold", size = 4, color = "#56B4E9") +
  theme(legend.position = "none", plot.margin = margin(30, 2, 2, 2, unit = "pt")) +
  labs(y = "Exposed F0 sex", angle = 90)

## OF lnCVR
p2 <- orchard_plot(MR_OF_ExpSex_lnCVRi, mod = "F0_Parent_Exposed", xlab = "lnCVR", transfm = "none", alpha = 0.3, angle = 45, cb = FALSE, k = FALSE) +
  scale_colour_manual(values = rep("#56B4E9", 3)) + 
  scale_fill_manual(values = rep("#56B4E9", 3)) +
  labs(title="c. ") +
  scale_x_continuous(limits = c(-3, 4), n.breaks = 10) + 
  scale_y_discrete(labels = c("Both", "Female", "Male")) +
  geom_text(x=3, y=1.2, label = paste("k =", colSums(MR_OF_ExpSex_lnCVRi$X)["F0_Parent_ExposedBoth"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=2.2, label = paste("k =", colSums(MR_OF_ExpSex_lnCVRi$X)["F0_Parent_ExposedFemale"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=3.2, label = paste("k =", colSums(MR_OF_ExpSex_lnCVRi$X)["F0_Parent_ExposedMale"]), fontface = "italic", size = 3) +
  geom_text(x=-2, y=3.4, label = "One-off", fontface = "bold", size = 4, color = "#56B4E9") +
  theme(legend.position = "none", plot.margin = margin(30, 2, 2, 2, unit = "pt")) +
  labs(y = "Exposed F0 sex", angle = 90)

## MG lnRR 
p3 <- orchard_plot(MR_MG_ExpSex_lnRRi, mod = "F0_Parent_Exposed", xlab = "lnRR", transfm = "none", alpha = 0.3, angle = 45, cb = FALSE, k = FALSE) +
  scale_colour_manual(values = rep("#E69F00", 2)) + 
  scale_fill_manual(values = rep("#E69F00", 2)) +
  labs(title="b. ") +
  scale_x_continuous(limits = c(-3, 4), n.breaks = 10) + 
  scale_y_discrete(labels = c("Female", "Male")) +
  geom_text(x=3, y=1.2, label = paste("k =", colSums(MR_MG_ExpSex_lnRRi$X)["F0_Parent_ExposedFemale"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=2.2, label = paste("k =", colSums(MR_MG_ExpSex_lnRRi$X)["F0_Parent_ExposedMale"]), fontface = "italic", size = 3) + 
  geom_text(x=-2, y=2.4, label = "Multigenerational", fontface = "bold", size = 4, color = "#E69F00") +
  theme(legend.position = "none", plot.margin = margin(30, 2, 2, 2, unit = "pt"))+
  annotate('text', x = 4, y = 0.9, label="*", fontface="bold", size=6)
  #+
  #labs(y = "Exposed F0 sex", angle = 90)

## MG lnCVR
p4 <- orchard_plot(MR_MG_ExpSex_lnCVRi, mod = "F0_Parent_Exposed", xlab = "lnCVR", transfm = "none", alpha = 0.3, angle = 45, cb = FALSE, k = FALSE) +
  scale_colour_manual(values = rep("#E69F00", 2)) + 
  scale_fill_manual(values = rep("#E69F00", 2)) +
  labs(title="d. ") +
  scale_x_continuous(limits = c(-3, 4), n.breaks = 10) + 
  scale_y_discrete(labels = c("Female", "Male")) +
  geom_text(x=3, y=1.2, label = paste("k =", colSums(MR_MG_ExpSex_lnCVRi$X)["F0_Parent_ExposedFemale"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=2.2, label = paste("k =", colSums(MR_MG_ExpSex_lnCVRi$X)["F0_Parent_ExposedMale"]), fontface = "italic", size = 3) +
  geom_text(x=-2, y=2.4, label = "Multigenerational", fontface = "bold", size = 4, color = "#E69F00") +
  theme(legend.position = "none", plot.margin = margin(30, 2, 2, 2, unit = "pt")) #+
  #labs(y = "Exposed F0 sex", angle = 90)

p1 + p3 + p2 + p4 + plot_layout(ncol = 2)  #assemble plot panels
ggsave("../Plots/Figure3_Rplot_v0.pdf", width = 16, height = 10, units = "cm", dpi = 300, scale = 1.6)
```


### Figure 4 - MR with measured grand-ofspring sex as moderator (lnRR, lnCVR)

```{r Figure4 MR Offspring_Sex}
# "#56B4E9" - One-off, "#E69F00" - Multigenerational

## OF lnRR 
p1 <- orchard_plot(MR_OF_OffSex_lnRRi, mod = "Offspring_Sex", xlab = "lnRR", transfm = "none", alpha = 0.3, angle = 45, cb = FALSE, k = FALSE) +
  scale_colour_manual(values = rep("#56B4E9", 3)) + 
  scale_fill_manual(values = rep("#56B4E9", 3)) +
  labs(title="a. ") +
  scale_x_continuous(limits = c(-3, 4), n.breaks = 10) + 
  scale_y_discrete(labels = c("Both", "Female", "Male")) +
  geom_text(x=3, y=1.2, label = paste("k =", colSums(MR_OF_OffSex_lnRRi$X)["Offspring_SexBoth"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=2.2, label = paste("k =", colSums(MR_OF_OffSex_lnRRi$X)["Offspring_SexFemale"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=3.2, label = paste("k =", colSums(MR_OF_OffSex_lnRRi$X)["Offspring_SexMale"]), fontface = "italic", size = 3) + 
  geom_text(x=-2, y=3.4, label = "One-off", fontface = "bold", size = 4, color = "#56B4E9") +
  theme(legend.position = "none", plot.margin = margin(30, 2, 2, 2, unit = "pt")) +
  labs(y = "Grand-offspring sex", angle = 90)

## OF lnCVR
p2 <- orchard_plot(MR_OF_ExpSex_lnCVRi, mod = "Offspring_Sex", xlab = "lnCVR", transfm = "none", alpha = 0.3, angle = 45, cb = FALSE, k = FALSE) +
  scale_colour_manual(values = rep("#56B4E9", 3)) + 
  scale_fill_manual(values = rep("#56B4E9", 3)) +
  labs(title="c. ") +
  scale_x_continuous(limits = c(-3, 4), n.breaks = 10) + 
  scale_y_discrete(labels = c("Both", "Female", "Male")) +
  geom_text(x=3, y=1.2, label = paste("k =", colSums(MR_OF_OffSex_lnCVRi$X)["Offspring_SexBoth"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=2.2, label = paste("k =", colSums(MR_OF_OffSex_lnCVRi$X)["Offspring_SexFemale"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=3.2, label = paste("k =", colSums(MR_OF_OffSex_lnCVRi$X)["Offspring_SexMale"]), fontface = "italic", size = 3) +
  geom_text(x=-2, y=3.4, label = "One-off", fontface = "bold", size = 4, color = "#56B4E9") +
  theme(legend.position = "none", plot.margin = margin(30, 2, 2, 2, unit = "pt")) +
  labs(y = "Grand-offspring sex", angle = 90)

## MG lnRR 
p3 <- orchard_plot(MR_MG_OffSex_lnRRi, mod = "Offspring_Sex", xlab = "lnRR", transfm = "none", alpha = 0.3, angle = 45, cb = FALSE, k = FALSE) +
  scale_colour_manual(values = rep("#E69F00", 3)) + 
  scale_fill_manual(values = rep("#E69F00", 3)) +
  labs(title="b. ") +
  scale_x_continuous(limits = c(-3, 4), n.breaks = 10) + 
  scale_y_discrete(labels = c("Both", "Female", "Male")) +
  geom_text(x=3, y=1.2, label = paste("k =", colSums(MR_MG_OffSex_lnRRi$X)["Offspring_SexBoth"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=2.2, label = paste("k =", colSums(MR_MG_OffSex_lnRRi$X)["Offspring_SexFemale"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=3.2, label = paste("k =", colSums(MR_MG_OffSex_lnRRi$X)["Offspring_SexMale"]), fontface = "italic", size = 3) + 
  geom_text(x=-2, y=3.4, label = "Multigenerational", fontface = "bold", size = 4, color = "#E69F00") +
  theme(legend.position = "none", plot.margin = margin(30, 2, 2, 2, unit = "pt"))+
    annotate('text', x = 4, y = 3, label="*", fontface="bold", size=6)+
    annotate('text', x = 4, y = 2, label="*", fontface="bold", size=6)#+
  #labs(y = "Grand-offspring sex", angle = 90)

## MG lnCVR
p4 <- orchard_plot(MR_MG_OffSex_lnCVRi, mod = "Offspring_Sex", xlab = "lnCVR", transfm = "none", alpha = 0.3, angle = 45, cb = FALSE, k = FALSE) +
  scale_colour_manual(values = rep("#E69F00", 3)) + 
  scale_fill_manual(values = rep("#E69F00", 3)) +
  labs(title="d. ") +
  scale_x_continuous(limits = c(-3, 4), n.breaks = 10) + 
  scale_y_discrete(labels = c("Both", "Female", "Male")) +
  geom_text(x=3, y=1.2, label = paste("k =", colSums(MR_MG_OffSex_lnCVRi$X)["Offspring_SexBoth"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=2.2, label = paste("k =", colSums(MR_MG_OffSex_lnCVRi$X)["Offspring_SexFemale"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=3.2, label = paste("k =", colSums(MR_MG_OffSex_lnCVRi$X)["Offspring_SexMale"]), fontface = "italic", size = 3) +
  geom_text(x=-2, y=3.4, label = "Multigenerational", fontface = "bold", size = 4, color = "#E69F00") +
  theme(legend.position = "none", plot.margin = margin(30, 2, 2, 2, unit = "pt")) #+
  #labs(y = "Grand-offspring sex", angle = 90)

p1 + p3 + p2 + p4 + plot_layout(ncol = 2)  #assemble plot panels
ggsave("../Plots/Figure4_Rplot_v0.pdf", width = 16, height = 10, units = "cm", dpi = 300, scale = 1.6)
```


### Figure5 - MR with measured grand-ofspring Trait as moderator (lnRR, lnCVR)

```{r Figure5 MR Trait}
# "#56B4E9" - One-off, "#E69F00" - Multigenerational

## OF lnRR 
p1 <- orchard_plot(MR_OF_Trait_lnRRi, mod = "Trait", xlab = "lnRR", transfm = "none", alpha = 0.3, angle = 0, cb = FALSE, k = FALSE) +
  scale_colour_manual(values = rep("#56B4E9", 8)) + 
  scale_fill_manual(values = rep("#56B4E9", 8)) +
  labs(title = "a. ") +
  scale_x_continuous(limits = c(-3, 4), n.breaks = 10) + 
  scale_y_discrete(labels = c("Adiposity", "Body weight", "Glucose Fasting", "Glucose Tolerance", "Insulin Fasting", "Insulin Tolerance", "Leptin", "Triglycerides")) +
  geom_text(x=3, y=1.2, label = paste("k =", colSums(MR_OF_Trait_lnRRi$X)["TraitAdiposity"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=2.2, label = paste("k =", colSums(MR_OF_Trait_lnRRi$X)["TraitBody_Weight"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=3.2, label = paste("k =", colSums(MR_OF_Trait_lnRRi$X)["TraitGlucose_FBG"]), fontface = "italic", size = 3) + 
  geom_text(x=3, y=4.2, label = paste("k =", colSums(MR_OF_Trait_lnRRi$X)["TraitGlucose_TT"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=5.2, label = paste("k =", colSums(MR_OF_Trait_lnRRi$X)["TraitInsulin_FI"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=6.2, label = paste("k =", colSums(MR_OF_Trait_lnRRi$X)["TraitInsulin_TT"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=7.2, label = paste("k =", colSums(MR_OF_Trait_lnRRi$X)["TraitLeptin"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=8.2, label = paste("k =", colSums(MR_OF_Trait_lnRRi$X)["TraitTriglycerides"]), fontface = "italic", size = 3) +  
  geom_text(x=-2, y=8.4, label = "One-off", fontface = "bold", size = 4, color = "#56B4E9") +
  theme(legend.position = "none", plot.margin = margin(30, 2, 2, 2, unit = "pt")) +
  labs(y = "Grand-offspring trait", angle = 90)+
  annotate('text', x = 4, y = 1, label="*", fontface="bold", size=6)

## OF lnCVR
p2 <- orchard_plot(MR_OF_Trait_lnCVRi, mod = "Trait", xlab = "lnCVR", transfm = "none", alpha = 0.3, angle = 0, cb = FALSE, k = FALSE) +
  scale_colour_manual(values = rep("#56B4E9", 8)) + 
  scale_fill_manual(values = rep("#56B4E9", 8)) +
  labs(title = "c. ") +
  scale_x_continuous(limits = c(-3, 4), n.breaks = 10) + 
    scale_y_discrete(labels = c("Adiposity", "Body weight", "Glucose Fasting", "Glucose Tolerance", "Insulin Fasting", "Insulin Tolerance", "Leptin", "Triglycerides")) +
  geom_text(x=3, y=1.2, label = paste("k =", colSums(MR_OF_Trait_lnCVRi$X)["TraitAdiposity"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=2.2, label = paste("k =", colSums(MR_OF_Trait_lnCVRi$X)["TraitBody_Weight"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=3.2, label = paste("k =", colSums(MR_OF_Trait_lnCVRi$X)["TraitGlucose_FBG"]), fontface = "italic", size = 3) + 
  geom_text(x=3, y=4.2, label = paste("k =", colSums(MR_OF_Trait_lnCVRi$X)["TraitGlucose_TT"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=5.2, label = paste("k =", colSums(MR_OF_Trait_lnCVRi$X)["TraitInsulin_FI"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=6.2, label = paste("k =", colSums(MR_OF_Trait_lnCVRi$X)["TraitInsulin_TT"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=7.2, label = paste("k =", colSums(MR_OF_Trait_lnCVRi$X)["TraitLeptin"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=8.2, label = paste("k =", colSums(MR_OF_Trait_lnCVRi$X)["TraitTriglycerides"]), fontface = "italic", size = 3) +  
  geom_text(x=-2, y=8.4, label = "One-off", fontface = "bold", size = 4, color = "#56B4E9") +
  theme(legend.position = "none", plot.margin = margin(30, 2, 2, 2, unit = "pt")) +
  labs(y = "Grand-offspring trait", angle = 90)

## MG lnRR 
p3 <- orchard_plot(MR_MG_Trait_lnRRi, mod = "Trait", xlab = "lnRR", transfm = "none", alpha = 0.3, angle = 0, cb = FALSE, k = FALSE) +
  scale_colour_manual(values = rep("#E69F00", 8)) + 
  scale_fill_manual(values = rep("#E69F00", 8)) +
  labs(title = "b. ") +
  scale_x_continuous(limits = c(-3, 4), n.breaks = 10) + 
  scale_y_discrete(labels = c("Adiposity", "Body weight", "Glucose Fasting", "Glucose Tolerance", "Insulin Fasting", "Insulin Tolerance", "Leptin", "Triglycerides")) +
  geom_text(x=3, y=1.2, label = paste("k =", colSums(MR_MG_Trait_lnRRi$X)["TraitAdiposity"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=2.2, label = paste("k =", colSums(MR_MG_Trait_lnRRi$X)["TraitBody_Weight"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=3.2, label = paste("k =", colSums(MR_MG_Trait_lnRRi$X)["TraitGlucose_FBG"]), fontface = "italic", size = 3) + 
  geom_text(x=3, y=4.2, label = paste("k =", colSums(MR_MG_Trait_lnRRi$X)["TraitGlucose_TT"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=5.2, label = paste("k =", colSums(MR_MG_Trait_lnRRi$X)["TraitInsulin_FI"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=6.2, label = paste("k =", colSums(MR_MG_Trait_lnRRi$X)["TraitInsulin_TT"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=7.2, label = paste("k =", colSums(MR_MG_Trait_lnRRi$X)["TraitLeptin"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=8.2, label = paste("k =", colSums(MR_MG_Trait_lnRRi$X)["TraitTriglycerides"]), fontface = "italic", size = 3) +  
  geom_text(x=-1.8, y=8.4, label = "Multigenerational", fontface = "bold", size = 4, color = "#E69F00") +
  theme(legend.position = "none", plot.margin = margin(30, 2, 2, 2, unit = "pt"))+
  annotate('text', x = 4, y = 1, label="*", fontface="bold", size=6)+
  annotate('text', x = 4, y = 7, label="*", fontface="bold", size=6)+
  annotate('text', x = 4, y = 8, label="*", fontface="bold", size=6)+
  annotate('text', x = 4, y = 5, label="*", fontface="bold", size=6)#+
  #labs(y = "Grand-offspring trait", angle = 90)

## MG lnCVR
p4 <- orchard_plot(MR_MG_Trait_lnCVRi, mod = "Trait", xlab = "lnCVR", transfm = "none", alpha = 0.3, angle = 0, cb = FALSE, k = FALSE) +
  scale_colour_manual(values = rep("#E69F00", 8)) + 
  scale_fill_manual(values = rep("#E69F00", 8)) +
  labs(title = "d. ") +
  scale_x_continuous(limits = c(-3, 4), n.breaks = 10) + 
  scale_y_discrete(labels = c("Adiposity", "Body weight", "Glucose Fasting", "Glucose Tolerance", "Insulin Fasting", "Insulin Tolerance", "Leptin", "Triglycerides")) +
  geom_text(x=3, y=1.2, label = paste("k =", colSums(MR_MG_Trait_lnCVRi$X)["TraitAdiposity"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=2.2, label = paste("k =", colSums(MR_MG_Trait_lnCVRi$X)["TraitBody_Weight"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=3.2, label = paste("k =", colSums(MR_MG_Trait_lnCVRi$X)["TraitGlucose_FBG"]), fontface = "italic", size = 3) + 
  geom_text(x=3, y=4.2, label = paste("k =", colSums(MR_MG_Trait_lnCVRi$X)["TraitGlucose_TT"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=5.2, label = paste("k =", colSums(MR_MG_Trait_lnCVRi$X)["TraitInsulin_FI"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=6.2, label = paste("k =", colSums(MR_MG_Trait_lnCVRi$X)["TraitInsulin_TT"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=7.2, label = paste("k =", colSums(MR_MG_Trait_lnCVRi$X)["TraitLeptin"]), fontface = "italic", size = 3) +
  geom_text(x=3, y=8.2, label = paste("k =", colSums(MR_MG_Trait_lnCVRi$X)["TraitTriglycerides"]), fontface = "italic", size = 3) +  
  geom_text(x=-1.8, y=8.4, label = "Multigenerational", fontface = "bold", size = 4, color = "#E69F00") +
  theme(legend.position = "none", plot.margin = margin(30, 2, 2, 2, unit = "pt"))+
  annotate('text', x = 4, y = 8, label="*", fontface="bold", size=6)#+
  #labs(y = "Grand-offspring trait", angle = 90)

p1 + p3 + p2 + p4 + plot_layout(ncol = 2)  #assemble plot panels
ggsave("../Plots/Figure5_Rplot_v0.pdf", width = 16, height = 14, units = "cm", dpi = 300, scale = 1.6)
```

### FigureS4 - F0 treatment start/end/duration plots (OF, MG)

```{r treatment timing plots, include = TRUE}

## OF dataset
p_OF_T_start <- data_OF %>%
  ggplot( aes(x=Treatment_Start_F0, fill=F0_Parent_Exposed)) +
    geom_histogram(color="#e9ecef", alpha=1, position = 'stack', breaks=seq(-150, 50, by=10)) +
    scale_fill_manual(values=c("#404080", "#CCFFE5", "#69b3a2")) +
    theme_bw() +
    theme(legend.position="none") +
    labs(x = "F0 treatment start [days]", y = "count ES", title = "a. One-off")

p_OF_T_end <- data_OF %>%
  ggplot( aes(x=Treatment_End_F0, fill=F0_Parent_Exposed)) +
    geom_histogram(color="#e9ecef", alpha=1, position = 'stack', breaks=seq(-150, 50, by=10)) +
    scale_fill_manual(values=c("#404080", "#CCFFE5", "#69b3a2")) +
    theme_bw() +
    theme(legend.position="top") +
    labs(fill="") +
    labs(x = "F0 treatment end [days]", y = "", title = "")


p_OF_T_duration <- data_OF %>%
  ggplot( aes(x=Treatment_Duration_F0, fill=F0_Parent_Exposed)) +
    geom_histogram(color="#e9ecef", alpha=1, position = 'stack', breaks=seq(0, 150, by=10)) +
    scale_fill_manual(values=c("#404080", "#CCFFE5", "#69b3a2")) +
    theme_bw() +
    theme(legend.position="none") +
    labs(x = "F0 treatment duration [days]", y = "", title = "")

## MG dataset
p_MG_T_start <- data_MG %>%
  ggplot( aes(x=Treatment_Start_F0, fill=F0_Parent_Exposed)) +
    geom_histogram(color="#e9ecef", alpha=1, position = 'stack', breaks=seq(-150, 50, by=10)) +
    scale_fill_manual(values=c("#CCFFE5", "#69b3a2")) +
    theme_bw() +
    theme(legend.position="none") +
    labs(x = "F0 treatment start [days]", y = "count ES", title = "b. Multigenerational")

p_MG_T_end <- data_MG %>%
  ggplot( aes(x=Treatment_End_F0, fill=F0_Parent_Exposed)) +
    geom_histogram(color="#e9ecef", alpha=1, position = 'stack', breaks=seq(-150, 50, by=10)) +
    scale_fill_manual(values=c("#CCFFE5", "#69b3a2")) +
    theme_bw() +
    theme(legend.position="top") +
    labs(fill="") +
    labs(x = "F0 treatment end [days]", y = "", title = "")

p_MG_T_duration <- data_MG %>%
  ggplot( aes(x=Treatment_Duration_F0, fill=F0_Parent_Exposed)) +
    geom_histogram(color="#e9ecef", alpha=1, position = 'stack', breaks=seq(0, 150, by=10)) +
    scale_fill_manual(values=c("#CCFFE5", "#69b3a2")) +
    theme_bw() +
    theme(legend.position="none") +
    labs(x = "F0 treatment duration [days]", y = "", title = "")

p_OF_T_start /p_OF_T_end / p_OF_T_duration / p_MG_T_start / p_MG_T_end /  p_MG_T_duration + plot_layout(ncol=3, nrow=2)

ggsave(file = "../Plots/Figure_exposure_Rplot_v0.pdf", width = 18, height = 16, units = "cm", dpi = 300, scale = 1.2)
```


### FigureS6 - funnel plots (lnRR, lnCVR)

```{r funnel plots, eval=FALSE, include=FALSE}
# funnels are based on residuals from full models in metafor
load(file = "../Rdata/RFP_OF_MG_Full.Rdata") #RFP_OF_Full_lnRR, RFP_OF_Full_lnCVR, RFP_MG_Full_lnRR, RFP_MG_Full_lnCVR

pdf(file="../Plots/Figure_funnels_Rplot_v0.pdf", width = 16, height = 10, pointsize = 20)
par(mfcol=c(2,2)) 
par(mar=c(4,4,2,1))

### OF lnRR
funnel(RFP_OF_Full_lnRR, yaxis = "seinv", level = c(90, 95, 99), shade = c("white", "gray55", "gray75"), refline = 0, legend = FALSE, xlab = "lnRR regressed residuals", xlim = c(-1.5,1.5), ylim = c(1,7), yaxt="n", col = "#56B4E9", hlines="lightgray")
axis(2, at = c(1, 2, 3, 4, 5, 6, 7), labels = c(1, 2, 3, 4, 5, 6, 7), las=2)
mtext("a. ", side = 3, adj = c(0,0), cex = 1.5)
text(-1.5, 6, "One-off", adj = c(0,0), col = "#56B4E9", cex = 1.5)

### OF lnCVR
funnel(RFP_OF_Full_lnCVR, yaxis = "seinv", level = c(90, 95, 99), shade = c("white", "gray55", "gray75"), refline = 0, legend = FALSE, xlab = "lnCVR regressed residuals", xlim = c(-3,3), ylim = c(1,4), yaxt="n", col = "#56B4E9", hlines="lightgray")
axis(2, at=c(1, 1.5, 2, 2.5, 3, 3.5, 4), labels = c(1, 1.5, 2, 2.5, 3, 3.5, 4), las=2)
mtext("c. ", side = 3, adj = c(0,0), cex = 1.5)
text(-3, 3.6, "One-off", adj = c(0,0), col = "#56B4E9", cex = 1.5)

### MG lnRR
funnel(RFP_MG_Full_lnRR, yaxis = "seinv", level = c(90, 95, 99), shade = c("white", "gray55", "gray75"), refline = 0, legend = FALSE, xlab = "lnRR regressed residuals", xlim = c(-1.5,1.5), ylim = c(1,4), yaxt="n", col = "#E69F00", hlines="lightgray") 
axis(2, at = c(1, 1.5, 2, 2.5, 3, 3.5, 4), labels = c(1, 1.5, 2, 2.5, 3, 3.5, 4), las=2)
mtext("b. ", side = 3, adj = c(0,0), cex = 1.5)
text(-1.5, 3.6, "Multigenerational", adj = c(0,0), col = "#E69F00", cex = 1.5)

### MG lnCVR
funnel(RFP_MG_Full_lnCVR, yaxis = "seinv", level = c(90, 95, 99), shade = c("white", "gray55", "gray75"), refline = 0, legend = FALSE, xlab = "lnCVR regressedresiduals", xlim = c(-3,3), ylim = c(1,4), yaxt="n", col = "#E69F00", hlines="lightgray")
axis(2, at=c(1, 1.5, 2, 2.5, 3, 3.5, 4), labels=c(1, 1.5, 2, 2.5, 3, 3.5, 4), las=2)
mtext("d. ", side = 3, adj = c(0,0), cex = 1.5)
text(-3, 3.6, "Multigenerational", adj = c(0,0), col = "#E69F00", cex = 1.5)

dev.off()
```



*NEXT: make tables for SI using STEP5_TABLES.Rmd script* 